---
title: "Untitled"
author: "Caitie"
date: "01/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(sf)
#library(startR)
library(here)
library(raster)
```

# Population raster

```{r}
pop_ras_proj<-raster(here("projected_data/Population/population_fji_proj.tif"))
```

# Connected populations

STP Watershed boundaries

Source - Water Authority Fiji

```{r}
stp<-st_read(here("raw_data/Sewage_plants/Fiji Waste Water Catchment.shp")) %>% 
  mutate(STP = ifelse(TREATMENT_ == "NATABUA WWTP", "Natabua WWTP",
                      ifelse(TREATMENT_ == "Navakai PS", "Navakai WWTP", as.character(TREATMENT_)))) %>% 
  mutate(area = st_area(.)) %>% 
  group_by(STP) %>% 
  summarise(area = sum(area, na.rm = T)) %>% 
  filter(!is.na(STP) == T) 
  
stp<-stp %>% 
  mutate(stp_pop = extract(pop_ras_proj, ., fun = sum, na.rm = T),
         ID = 1:nrow(stp))
```

# Compare our results population connected results to reported results

Source - Table 1 from Fiji national liquid waste management strategy and action plan 2007

```{r}
reported_conn<-read.csv(here("raw_data/Sewage_plants/STP_pop_connected.csv")) %>% 
  mutate(ID = ifelse(STP_name == "Adi_Cakobau School", 1,
                     ifelse(STP_name == "Pacific_Harbour", 2,
                            ifelse(STP_name == "Suva_Kinoya", 3,
                                   ifelse(STP_name == "Naboro Prison", 4,
                                          ifelse(STP_name == "Nausori", 5,
                                                 ifelse(STP_name ==  "Labasa", 6,
                                                        ifelse(STP_name == "Lautoka", 7,
                                                               ifelse(STP_name ==  "Nadi", 8,
                                                                      ifelse(STP_name == "Sigatoka", 9,
                                                                             ifelse(STP_name == "Ba", 10,
                                                                                    ifelse(STP_name == "Wailada", 11, NA))))))))))))
```

Join to estimates

```{r}
pop_check<- stp %>% 
  as.data.frame() %>% 
  dplyr::select(-geometry) %>% 
  full_join(., reported_conn, by = "ID") %>% 
  dplyr::select(STP, STP_name, stp_pop, Pop_connected) %>% 
  rename(estimated = stp_pop,
         reported = Pop_connected)

write.csv(here("output_data/Sewage_plants/STP_population_check.csv"))
```


# Compare our N/P estimates at STPs with reported estimates

Reported nutrients

Units are mg/L
```{r}
stp_nutri<-read.csv(here("raw_data/Sewage_plants/Nutrient_removal_STP.csv"))
```

Reported flow rates
Units are Mega litres
```{r}
flow<-read.csv(here("raw_data/Sewage_plants/WWTP_flow_data.csv")) %>% 
  filter(!WWTP == "") %>% 
  pivot_longer(., cols = c("X2010":"X2019"), values_to = "flow", names_to = "Year") %>% 
  filter(Year %in% c("X2015", "X2016", "X2017", "X2018","X2019")) %>% 
  mutate(flow = as.numeric(flow),
         res_flow = flow * 0.7) %>% 
  group_by(WWTP) %>% 
  summarise(avg_flow = mean(res_flow,na.rm = T)) %>% 
  mutate(STP = ifelse(WWTP == "Votua", "Ba",
                      ifelse(WWTP == "Natabua", "Lautoka", as.character(WWTP))),
         litres = avg_flow * 1000000)
```
70% of flow is residential - except Wailada, ACS and Naboro bc they are institutional/industrial areas

```{r}
res_ind<-read.csv(here("raw_data/Sewage_plants/WWTP_flow_residential_industrial.csv")) %>% 
  rename(residential = "Residential..70..",
         flow_2010 = "X2010..Megalitres.") %>% 
  mutate(STP = ifelse(STP == "Votua", "Ba",
                      ifelse(STP == "Natabua", "Lautoka", as.character(STP))),
         residential = replace_na(residential, 0),
         prop_res = residential/flow_2010) %>% 
  dplyr::select(STP, prop_res)
```

Join by STP
```{r}
stp_flow<-full_join(stp_nutri, flow, by = "STP") %>% 
  mutate(Total_nutri_mg = Final * litres,
         Total_nutri_kg = Total_nutri_mg*1e-6) %>% 
  pivot_wider(., names_from = "type", values_from= "Total_nutri_kg") %>% 
  dplyr::select(STP, N, P)

nflow<-stp_flow %>% 
  dplyr::select(STP, N) %>% 
  filter(!is.na(N) == T)

pflow<-stp_flow %>% 
  dplyr::select(STP, P) %>% 
  filter(!is.na(P) == T)

flow_final<-full_join(nflow, pflow, by = "STP") 
```

Estimated nutrients

```{r}
est_nutri<-st_read(here("output_data/Sewage_plants/Nutrients_at_STP.shp")) %>% 
  as.data.frame() %>% 
  dplyr::select(-geometry) %>% 
  mutate(STP = stringr::str_remove(STP, " WWTP"),
         STP = ifelse(STP == "Namara TP", "Namara", 
                  ifelse(STP == "Votua", "Ba",
                      ifelse(STP == "Natabua", "Lautoka", as.character(STP))))) %>% 
  dplyr::select(STP, N, P) %>% 
  rename(N_est = N,
         P_est = P)
```

```{r}
check_nutri<-full_join(flow_final, est_nutri, by = "STP") %>% 
  mutate(perc_diff_N = (N_est- N)/N,
         perc_diff_P = (P_est-P)/P)
```

```{r}
cor.test(check_nutri$N, check_nutri$N_est, method = "pearson") 

ggplot(check_nutri, aes(x = N_est/100000, y = N/100000, col = STP)) +
  geom_point() +
  ylab("Reported N (hundreds of thousands)") +
  xlab("Estimated N (hundreds of thousands)") +
  stat_smooth(method = "lm", col = "red") +
  theme_bw()
```

```{r}
cor.test(check_nutri$P, check_nutri$P_est, method = "pearson")

ggplot(check_nutri, aes(x = P_est/10000, y = P/10000, col = STP)) +
  geom_point() +
    ylab("Reported P (tens of thousands)") +
  xlab("Estimated P (tens of thousands)") +
  stat_smooth(method = "lm", col = "red") +
  theme_bw()
```
