---
title: "Untitled"
author: "Caitie"
date: "13/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(here)
library(tidyverse)
library(ggplot2)
library(sf)
library(pbmcapply)
library(raster)
library(tmap)
library(ggrepel)

source(here("scripts/plume_functions.R"))

t_crs<-"+proj=aea +lat_1=-9 +lat_2=-26 +lat_0=-17 +lon_0=180 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs"
```

# Connected

```{r}
stp_names<-list.files(here("output_data/Nutrients/plumes"), pattern = "fall_plume")
```

```{r}
nutri_removal<-read.csv(here("raw_data/Sewage_plants/Nutrient_removal_STP.csv")) %>% 
  mutate(ID = ifelse(STP == "ACS", NA,
                     ifelse(STP == "Deuba", 1,
                            ifelse(STP == "Kinoya", 2,
                                   ifelse(STP == "Naboro", NA,
                                          ifelse(STP == "Nadali", 3,
                                                 ifelse(STP ==  "Namara", 4,
                                                        ifelse(STP == "Lautoka", 5,
                                                               ifelse(STP ==  "Navakai", 6,
                                                                      ifelse(STP == "Olosara", 7,
                                                                             ifelse(STP == "Ba", 8,
                                                                                    ifelse(STP == "Wailada", NA, NA))))))))))),
         nutri_left = (1-rm_eff)) %>% 
  filter(type == "N")
```

```{r}
coral_shp<-list.files(here("output_data/Nutrients/plumes"), pattern = "fall_n_", full.names = T)
coral_shp2<-coral_shp[grep("shp", coral_shp)]

c_name<-c()
all_total<-c()
all_area<-c()

for(i in 1:length(coral_shp2)){
  print(i)
  sub_shp<-st_read(coral_shp2[[i]]) %>% 
    mutate(area = as.numeric(st_area(.)))
  name<-str_sub(stp_names[[i]], end=-11)
  total<-sum(sub_shp$Fj_c_N_,na.rm = T)
  sub_shp2<-sub_shp %>% 
    filter(Fj_c_N_>0)
  total_area<-sum(sub_shp2$area)
  c_name<-c(c_name, name)
  all_total<-c(all_total, total)
  all_area<-c(all_area, total_area)
}


stp_done<-data.frame(Name = c_name, N_reefs = all_total, area_m2 = all_area)

stp_done<-stp_done %>% 
  mutate(ID = case_when(Name == "Ba outfall"  ~ 8,
                        Name == "Labasa Outfall"~ 4,
                        Name =="Lautoka Natabua Sewage Outfall" ~ 5,
                        Name == "Nadi outfall" ~6,
                        Name == "Pacific Harbor Sewage Outfall"~1,
                        Name== "PWD (Kinoya) Sewage Outfall" ~2,
                        Name == "Rewa Outfall"~ 3,
                        Name == "Sigatoka Outfall"~7))

```


# Plot

Join data

```{r}
nutri_stp<-st_read(here("output_data/Sewage_plants/Nutrients_at_STP.shp")) %>% 
  as.data.frame() %>% 
  dplyr::select(-geometry) %>% 
  mutate(total = N+P)

nutri_stp<-nutri_stp %>% 
  mutate(ID = seq(1:nrow(nutri_stp)))
```



```{r}
connected_N_reefs<-full_join(nutri_stp, stp_done) %>% 
  mutate(stp_area_km2 = area*1e-6,
         reef_area_km2 = area_m2*1e-6,
         N_km2 = (N*0.001)/stp_area_km2,
         N_reef_km2 = (N_reefs*0.001)/reef_area_km2,
         label = case_when(STP== "Deuba WWTP" ~ "Deuba",
                           STP == "Kinoya WWTP" ~ "Kinoya",
                           STP =="Nadali WWTP" ~ "Nadali",
                           STP =="Namara TP" ~ "Namara",
                           STP == "Natabua WWTP" ~ "Natabua",
                           STP =="Navakai WWTP" ~ "Navakai",
                           STP =="Votua WWTP"  ~ "Votua",
                           STP == "Olosara" ~ "Olosara"))
```

Priorities for improving treatment
```{r}
ggplot(connected_N_reefs, aes(x = log10((N*0.001)+1), y = log10((N_reefs*0.001)+1), label = label, color = reef_area_km2)) + 
  geom_point(aes(size = stp_area_km2)) +
  geom_text_repel(force = 1, nudge_y = 0.1) +
  xlab("Nitrogen at pourpoint (tonnes, log+1)") +
  ylab("Nitrogen at coral reef (avg. tonnes, log+1)") +
  theme_bw()
```
```{r}
ggplot(connected_N_reefs, aes(x = log10((N*0.001)+1), y = log10((N_reefs*0.001)+1), label = label)) + 
  geom_point(aes(size = stp_area_km2)) +
  geom_text_repel(force = 1, nudge_y = 0.1) +
  xlab("Nitrogen at pourpoint (tonnes, log+1)") +
  ylab("Nitrogen at coral reef (avg. tonnes, log+1)") +
  theme_bw()
```

```{r}
conn_treat<-full_join(connected_N_reefs, nutri_removal, by = "ID") %>% 
  filter(!is.na(N) == T)
```

```{r}
ggplot(conn_treat, aes(x = N*0.001, y = rm_eff, label = label)) + 
  geom_point(aes(size = stp_pop)) +
  geom_text_repel(force = 1, nudge_x = 0.01)+
   xlab("Nitrogen at pourpoint\n (tonnes)") +
  ylab("Removal efficiency") +
  theme_bw()
```
```{r}
ggplot(conn_treat, aes(y = N_reefs*0.001, x = N*0.001, label = label, color = stp_pop)) + 
  geom_point(aes(size = rm_eff)) +
  geom_text_repel(force = 1, nudge_x = 0.01) +
  ylab("Nitrogen at coral reefs\n (tonnes)") +
  xlab("Nitrogen at pour point\n (tonnes") +
  theme_bw()
```
```{r}
ggplot(conn_treat, aes(y = N_reef_km2, x = N_km2, label = label, color = stp_pop)) + 
  geom_point(aes(size = rm_eff)) +
  geom_text_repel(force = 1, nudge_x = 0.01) +
  ylab("Nitrogen at coral reefs\n (tonnes/km2)") +
  xlab("Nitrogen at pour point\n (tonnes/km2)") +
  theme_bw()
```

# Unconnected nutrients

```{r}
un_basins_nutri<-st_read(here("output_data/InVEST/model_output/watershed_results_ndr.shp")) %>% 
  as.data.frame() %>% 
  dplyr::select(-geometry) %>% 
  mutate(rm_eff = (surf_n_ld - n_exp_tot)/surf_n_ld)
```

```{r}
bas_names<-list.files(here("output_data/Nutrients/plumes"), pattern = "MAIN_BAS_plume")

coral_shp<-list.files(here("output_data/Nutrients/plumes"), pattern = "n_coral", full.names = T)
coral_shp2<-coral_shp[grep("MAIN_BAS", coral_shp)]
coral_shp3<-coral_shp2[grep("shp", coral_shp2)]

c_name<-c()
all_total<-c()
all_area<-c()

for(i in 1:length(coral_shp3)){
  print(i)
  sub_shp<-st_read(coral_shp3[[i]]) %>% 
    mutate(area = as.numeric(st_area(.)))
  name<-substr(bas_names[[i]], start = 16, stop = 25)
  total<-sum(sub_shp$Fj_n_N_,na.rm = T)
  sub_shp2<-sub_shp %>% 
    filter(Fj_n_N_>0)
  total_area<-sum(sub_shp2$area)
  c_name<-c(c_name, name)
  all_total<-c(all_total, total)
  all_area<-c(all_area, total_area)
}


done<-data.frame(Name = c_name, N_reefs = all_total, area_m2 = all_area) %>% 
  rename(MAIN_BAS = Name) %>% 
  mutate(MAIN_BAS = as.numeric(MAIN_BAS))
```

# Plot

Join data

```{r}
unconnected_N_reefs<-full_join(un_basins_nutri, done) %>% 
  mutate(N_reefs = ifelse(is.na(N_reefs) == T, 0, as.numeric(N_reefs)),
         area_m2 = ifelse(is.na(area_m2) == T, 0, as.numeric(area_m2)),
         area_km2 = area*1e-6,
         reef_area_km2 = area_m2*1e-6,
         N_km2 = (n_exp_tot*0.001)/area_km2,
         N_reef_km2 = (N_reefs*0.001)/reef_area_km2,
         N_reef_km2 = ifelse(is.na(N_reef_km2) == T, 0, as.numeric(N_reef_km2)))
```
Calculate population in each basin

Priorities for improving treatment?
```{r}
ggplot(unconnected_N_reefs, aes(x = log10((n_exp_tot*0.001)+1), y = log10((N_reefs*0.001)+1), color = as.character(MAIN_BAS))) + 
  geom_point(aes(size = area_km2)) +
  xlab("Nitrogen at pourpoint (tonnes, log+1)") +
  ylab("Nitrogen at coral reef (avg. tonnes, log+1)") +
  theme_bw() +
  theme(legend.position = "none")
```

N/km2 at pourpoint vs. N reaching reefs/km2
```{r}
sub<-unconnected_N_reefs %>% 
  filter(N_reef_km2>0)

ggplot(sub, aes(x = log10(N_km2+1), y = log10(N_reef_km2+1), color = as.character(MAIN_BAS))) + 
  geom_point() +
   xlab("Nitrogen at pourpoint\n (tonnes/km^2, log+1)") +
  ylab("Nitrogen at coral reef\n (avg. tonnes/km^2, log+1)") +
  theme_bw() +
  theme(legend.position = "none")
```

Nitrogen produced in watershed vs. nitrogen exported in watershed

```{r}
ggplot(un_basins_nutri, aes(x = surf_n_ld*0.001, y = n_exp_tot*0.001, color = as.character(MAIN_BAS))) +
  geom_point(aes(size = area)) +
  theme_bw() +
  theme(legend.position = "none")
```
```{r}
all<-full_join(un_basins_nutri, unconnected_N_reefs)
ggplot(all, aes(x = surf_n_ld*0.001, y = N_reefs*0.001, color = as.character(MAIN_BAS))) +
  geom_point(aes(size = area)) +
  theme_bw() +
  theme(legend.position = "none")
```


```{r}
ggplot(un_basins_nutri, aes(x = surf_n_ld, y = area, color = as.character(MAIN_BAS))) +
  geom_point() +
  theme_bw() +
  theme(legend.position = "none")
```

# Maps

```{r}
basins<-st_read(here("output_data/InVEST/model_output/watershed_results_ndr.shp")) %>% 
  filter(!MAIN_BAS == 5120082250)

nutri_stp<-st_read(here("output_data/Sewage_plants/Nutrients_at_STP.shp"))
```

```{r}
#connected_produced<-tm_shape(basins) +
#  tm_borders() +
#  tm_fill(col = "linen")+ 
  
#connected_produced
```

```{r}
connected_exported<-tm_shape(basins) +
  tm_borders() +
  tm_fill(col = "linen")+ 
  tm_shape(nutri_stp) +
  tm_bubbles(size = "N",
             col = "STP",
             border.col = "red",
             border.lwd = 1.5) +
   tm_layout(legend.outside = TRUE, bg.color = "lightblue",
            legend.position=c("left", "top"))

connected_exported
```
```{r}
stp_reefs<-full_join(nutri_stp,connected_N_reefs)

connected_stp_reefs<-tm_shape(basins) +
  tm_borders() +
  tm_fill(col = "linen")+ 
  tm_shape(stp_reefs) +
  tm_bubbles(size = "N_reefs",
             col = "STP",
             border.col = "red",
             border.lwd = 1.5) +
   tm_layout(legend.outside = TRUE, bg.color = "lightblue",
            legend.position=c("left", "top"))

connected_stp_reefs
```
```{r}
nutri_reef<-st_read(here("output_data/Nutrients/Fiji_corals_nutrient_export.shp")) %>% 
  mutate(area = as.numeric(st_area(.)))

total_n<-nutri_reef%>% 
  mutate(Total_N=ifelse(Total_N<=0, NA, as.numeric(Total_N)))

total_nutrients<-tm_shape(basins) +
  tm_borders() +
  tm_fill(col="lightgrey") +
  tm_shape(total_n) +
  tm_fill(col = "Total_N", 
          title = "Total nitrogen (kg)", 
          style = "quantile",
          textNA = "Zero or NA") +
  tm_layout(legend.outside = TRUE, bg.color = "lightblue",
            legend.position=c("left", "top"))

total_nutrients
```
```{r}
conn_n<-nutri_reef%>% 
  mutate(conn_N=ifelse(conn_N<=0, NA, as.numeric(conn_N)))

conn_nutrients<-tm_shape(basins) +
  tm_borders() +
  tm_fill(col="lightgrey") +
  tm_shape(conn_n) +
  tm_fill(col = "conn_N", 
          title = "Connected nitrogen (kg)", 
          style = "quantile",
          textNA = "Zero or NA") +
  tm_layout(legend.outside = TRUE, bg.color = "lightblue",
            legend.position=c("left", "top"))

conn_nutrients
```

```{r}
unconnected_produced<-tm_shape(basins) +
  tm_borders() +
  tm_fill(col = "surf_n_ld",
          title = "Total nutrients (kg)", 
          style = "order",
          textNA = "Zero or NA")

unconnected_produced
```


```{r}
unconnected_exported<-tm_shape(basins) +
  tm_borders() +
  tm_fill(col = "n_exp_tot",
          title = "Total nutrients (kg)", 
          style = "order",
          textNA = "Zero or NA")

unconnected_exported
```

```{r}
unconn_n<-nutri_reef%>% 
  mutate(unconn_N=ifelse(unconn_N<=0, NA, as.numeric(unconn_N)))

unconn_nutrients<-tm_shape(basins) +
  tm_borders() +
  tm_fill(col="lightgrey") +
  tm_shape(unconn_n) +
  tm_fill(col = "unconn_N", 
          title = "Unconnected nitrogen (kg)", 
          style = "quantile",
          textNA = "Zero or NA") +
  tm_layout(legend.outside = TRUE, bg.color = "lightblue",
            legend.position=c("left", "top"))

unconn_nutrients
```

Plot connected N vs. unconnected N on reefs

```{r}
ggplot(nutri_reef, aes(x = conn_N, y = unconn_N)) +
  geom_point(aes(size = area))

cor.test(nutri_reef$conn_N, nutri_reef$unconn_N, method = "pearson")
```
```{r}
ggplot(nutri_reef, aes(x = conn_N, y = area)) +
  geom_point()
```
```{r}
ggplot(nutri_reef, aes(x = unconn_N, y = area)) +
  geom_point()
```

```{r}
conn_dat<-nutri_reef %>% 
  as.data.frame() %>% 
  filter(conn_N>0) %>% 
  dplyr::select(conn_N, area, -geometry) %>% 
  mutate(type = "connected") %>% 
  rename(N = conn_N)

unconn_dat<-nutri_reef %>% 
  as.data.frame() %>% 
  filter(unconn_N>0) %>% 
  dplyr::select(unconn_N, area, -geometry) %>% 
  mutate(type = "unconnected") %>% 
  rename(N = unconn_N)

bar_dat<- rbind(conn_dat, unconn_dat) %>% 
  group_by(type) %>% 
  summarise(area_all = sum(area, na.rm = T),
            N_all = sum(N, na.rm= T))

ggplot(bar_dat, aes(x = type, y = area_all)) +
  geom_bar(stat = "identity")
```

```{r}
ggplot(bar_dat, aes(x = type, y = N_all)) +
  geom_bar(stat = "identity")
```

Add plot with area on Y axis - do connected or unconnected pollution effect more area of reef?
Look into costs of improving to tertiary treatment
How do you decide when to improve STP?
Look at different land use maps for nature based solutions?? Mangrove layer?

1. Connected - increase treatment, expand treatment
2. Unconnected - nature-based solutions, direct to septic, improved septic treatment


```{r}
ggplot(nutri_reef, aes(x = conn_N, y = unconn_N)) +
  geom_point(aes(size = area))
```

