---
title: "Untitled"
author: "Caitie"
date: "16/09/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(sf)
library(here)
library(raster)
library(ggplot2)
```

# Improved wastewater treatment scenario

## N and P emissions within STP catchment areas without treatment

STP N and P values

```{r}
stp<-st_read(here("output_data/Sewage_plants/Nutrients_at_STP.shp")) %>% 
  as.data.frame() %>% 
  dplyr::select(-geometry)
```


## Nutrient removal

See how nutrients change with incremental 1% increase in nutrient removal efficiency for each STP (do from 0-100% and then can mark where current levels are)

Max treatment efficiency = 90% for N and 95% for P, equivalent to tertiary treatment

Current nutrient removal efficiencies

```{r}
seq_rm<-seq(0,1, 0.001)

S<-unique(stp$STP)

all<-c()

for(i in 1:length(S)){
  
  sub_stp<-stp %>% 
    filter(STP == S[[i]])
  
  name<-S[[i]]
  ID<-sub_stp$ID
  
  print(name)
  
  N_vals<-seq_rm * sub_stp$N_ntrtm
  P_vals<-seq_rm * sub_stp$P_ntrtm
  
  done<-data.frame(STP = name, ID = ID, rm_eff = seq_rm, N = N_vals, P = P_vals)
  
  all<-rbind(all, done)
  
}
```

# Plots

Plot contribution of each STP to total N and P values

```{r}
stp_plot<-stp %>% 
  dplyr::select(STP, N, P) 

stp_plot<-stp_plot %>% 
  mutate(prop_N = N/sum(stp_plot$N),
         prop_P = P/sum(stp_plot$P)) %>% 
  pivot_longer(., cols = c("prop_N", "prop_P"), names_to = "type", values_to = "prop")

ggplot(stp_plot, aes(fill=reorder(STP, prop, desc = T), y=prop, x=type)) + 
    geom_bar(position="stack", stat="identity") +
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black")) +
  xlab("Nutrient type") +
  ylab("Proportion of total nutrients")
```


Plot how final N and P values change with increased nutrient removal efficiency

Total

```{r}
total<-all %>% 
  group_by(rm_eff) %>% 
  summarise(N_all = sum(N, na.rm = T),
            P_all = sum(P, na.rm = T)) %>% 
  pivot_longer(., cols = c("N_all", "P_all"), names_to = "type", values_to = "value")
```
```{r}
ggplot(total, aes(x = rm_eff, y = value/100000, col = type)) +
  geom_line() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black")) +
  xlab("Removal Efficiency") +
  ylab("Nutrients (hundreds of thousands)")
```


By STP


```{r}

all_long<-all %>% 
  pivot_longer(., cols = c("N", "P"), names_to = "type", values_to = "value")

nutri_removal<-read.csv(here("raw_data/Sewage_plants/Nutrient_removal_STP.csv")) %>% 
  mutate(ID = ifelse(STP == "ACS", 1,
                     ifelse(STP == "Deuba", 2,
                            ifelse(STP == "Kinoya", 3,
                                   ifelse(STP == "Naboro", 4,
                                          ifelse(STP == "Nadali", 5,
                                                 ifelse(STP ==  "Namara", 6,
                                                        ifelse(STP == "Lautoka", 7,
                                                               ifelse(STP ==  "Navakai", 8,
                                                                      ifelse(STP == "Olosara", 9,
                                                                             ifelse(STP == "Ba", 10,
                                                                                    ifelse(STP == "Wailada", 11, NA)))))))))))) %>% 
  dplyr::select(ID, rm_eff, type) %>% 
  rename(actual_eff = rm_eff) %>% 
  mutate(actual_eff = round(actual_eff, 3)) %>% 
  full_join(., all_long, by = c("ID", "type")) %>% 
  mutate(rm_eff = round(rm_eff, 3)) 

```


N
```{r}
N_plot<-nutri_removal %>% 
  filter(type == "N") %>% 
  mutate(xpoints = ifelse(actual_eff == rm_eff, actual_eff, NA),
         ypoints = ifelse(actual_eff == rm_eff, value, NA))

ggplot(N_plot, aes(x = rm_eff, y = value/100000, col = STP)) +
  geom_line() +
  geom_point(aes(x = xpoints, y = ypoints/100000)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black")) +
  xlab("Nitrogen removal efficiency") +
  ylab("Nitrogen (hundreds of thousands)")
```
P
```{r}
P_plot<-nutri_removal %>% 
  filter(type == "P") %>% 
  mutate(xpoints = ifelse(actual_eff == rm_eff, actual_eff, NA),
         ypoints = ifelse(actual_eff == rm_eff, value, NA))

ggplot(P_plot, aes(x = rm_eff, y = value/100000, col = STP)) +
  geom_line() +
  geom_point(aes(x = xpoints, y = ypoints/100000)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black")) +
  xlab("Phosphorus removal efficiency") +
  ylab("Phosphorus (hundreds of thousands)")
```

