---
title: "Untitled"
author: "Caitie"
date: "01/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load packages

```{r}
library(tidyverse)
library(sf)
library(here)
library(tabularaster)
#devtools::install_github("rspatial/raster")
library(raster)
library(maptools)

t_crs<-"+proj=aea +lat_1=-9 +lat_2=-26 +lat_0=-17 +lon_0=180 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs"
```


# Select buffer size to use

We use 50 meters as this is the distance used for septic buffer

These layers are the 50 m buffer changed to N/P values, not including any treatment or leaching

```{r}
coast_septic_N<-raster(here("output_data/Nutrients/buffers/Coast_N_septic_per_basin_35_buff.tif"))

coast_septic_P<-raster(here("output_data/Nutrients/buffers/Coast_P_septic_per_basin_35_buff.tif"))
  
coast_direct_N<-raster(here("output_data/Nutrients/buffers/Coast_N_direct_per_basin_35_buff.tif"))

coast_direct_P<-raster(here("output_data/Nutrients/buffers/Coast_P_direct_per_basin_35_buff.tif"))
```


# Identify pourpoint locations

Center of raster cells are pourpoint locations

```{r}
#Get XY coordinates of cells
septic_N_xy<-as_tibble(coast_septic_N, values = TRUE, xy = TRUE)
septic_P_xy<-as_tibble(coast_septic_P, values = TRUE, xy = TRUE)
direct_N_xy<-as_tibble(coast_direct_N, values = TRUE, xy = TRUE)
direct_P_xy<-as_tibble(coast_direct_P, values = TRUE, xy = TRUE)
```

```{r}
#Subset to only include cells that have nutrient values
sub_septic_N<-septic_N_xy %>% 
  filter(!is.na(cellvalue) == T,
         cellvalue>0) %>% 
  rename(septic_N = cellvalue)

sub_septic_P<-septic_P_xy %>% 
  filter(!is.na(cellvalue) == T,
         cellvalue>0)%>% 
  rename(septic_P = cellvalue)

sub_direct_N<-direct_N_xy %>% 
  filter(!is.na(cellvalue) == T,
         cellvalue>0)%>% 
  rename(direct_N = cellvalue)

sub_direct_P<-direct_P_xy %>% 
  filter(!is.na(cellvalue) == T,
         cellvalue>0) %>% 
  rename(direct_P = cellvalue)
```

```{r}
#Join septic N and P and direct N and P

septic<-full_join(sub_septic_N, sub_septic_P)
direct<-full_join(sub_direct_N, sub_direct_P)
```

```{r}
#Create shapefile
septic_shp<-septic
coordinates(septic_shp)<-~x+y
crs(septic_shp)<-t_crs
septic_shp<-spTransform(septic_shp, t_crs)
septic_sf<-st_as_sf(septic_shp)
septic_sf<-st_transform(septic_sf, crs = t_crs)

```

```{r}
#Create shapefile
direct_shp<-direct
coordinates(direct_shp)<-~x+y
crs(direct_shp)<-t_crs
direct_shp<-spTransform(direct_shp, t_crs)
direct_sf<-st_as_sf(direct_shp)
direct_sf<-st_transform(direct_sf, crs = t_crs)
```

```{r}
#Snap pourpoints to coastline
#Don't do this for now - think it is done in the plume function
```
# Remove very small values?

Tuholske et al. remove pourpoints <1g N

Values are currently in kg so none meet this criteria

```{r}
test<-septic_sf[!septic_sf$septic_N == 0,]
test2<-direct_sf[!direct_sf$direct_N == 0,]
min(test$septic_N)
min(test$septic_P)
min(test2$direct_N)
min(test2$direct_P)
```
# Double check values

```{r}
# These should be equal
sum(septic_sf$septic_N, na.rm = T)
cellStats(coast_septic_N, sum, na.rm = T)

# These should be equal
sum(direct_sf$direct_N, na.rm = T)
cellStats(coast_direct_N, sum, na.rm = T)

```
# Apply treatment and leaching values

```{r}
septic_sf<-septic_sf %>% 
  mutate(
         septic_N_treat_leach = septic_N * 0.8, #20% lost treatment/soil
         septic_P_treat_leach = septic_P * 0.7) #30% lost treatment/soil
```

```{r}
direct_sf<-direct_sf %>% 
  mutate(#direct_N_treat = direct_N, #0% removal from direct disposal
         #direct_P_treat = direct_P,
         direct_N_treat_leach = direct_N * 0.2, #80% lost treatment/soils
         direct_P_treat_leach = direct_P * 0.01) #99% lost in treatment/soils
```


# Determine which basin pourpoints are in


```{r}
basin<-st_read(here("projected_data/Basins/Fiji_basins12.shp")) %>% 
  st_transform(., t_crs) %>% 
  group_by(MAIN_BAS) %>% 
  summarise(total_area = sum(area_m2, na.rm = T))
```
```{r}
septic_sf_basin<-st_intersection(septic_sf, basin)
direct_sf_basin<-st_intersection(direct_sf, basin)
```


# Save nutrients at pourpoints

Septic has much fewer pourpoints than direct.

```{r}
st_write(septic_sf_basin, here("output_data/Nutrients_at_pourpoints/Coastal_septic_pourpoints.shp"), delete_layer = TRUE)

st_write(direct_sf_basin, here("output_data/Nutrients_at_pourpoints/Coastal_direct_pourpoints.shp"), delete_layer = TRUE)
```

