---
title: "Plumes_by_treatment"
author: "Caitie"
date: "2022-08-29"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
gc()

library(tidyverse)
library(dplyr)
library(rgdal)
library(raster)
library(gdistance)
library(reshape2)
library(sf)
library(here)
#library(seegSDM)#discontinued

source(here("scripts/function_plume_diffusion_model_2.R"))

```




#READ OCEANS RASTER

```{r}
ocean_raster<-raster(here("raw_data/Plumes/ocean_raster_1km.tif"))
```


#read other plumes

```{r}
plu<-raster(here("raw_data/Plumes/ero_dep_tiff.tif"))
```


#READ POUR POINTS SHAPEFILE

```{r}
pour_points<-st_read(here("output_data/Nutrients_at_pourpoints/All_nutrients_at_pourpoints.shp")) %>% 
  st_transform(., st_crs(plu)) %>% 
  mutate(group = ifelse(type == "Connected", 1, 2))
```


```{r}
pour_points<-spTransform(as(pour_points,"Spatial"), crs(plu))
ocean_raster <- projectRaster(ocean_raster, crs = plu)

pour_points<-st_as_sf(pour_points)
```

#This code works well for a relatively small area.
#If you want to work at a global scale, you need to divide them
#by groups using something like this:

#convert to spatial object

```{r}
pour_points<-as(pour_points,"Spatial")
```


#create list by group
#point_list<-split(pour_points,as.character(pour_points@data$group))

```{r}
point_list<-split(pour_points,as.character(pour_points$group))
```



#The you can apply the function to each group in the
#list

#I used a loop because I wanted to keep track of some
#pour points. It is fairly quickly but you can also paralellize.

re[[2]] is not working properly

```{r}
pb <- txtProgressBar(min = 0, max = length(point_list), style = 3)


for(p in 1:length(point_list)){
  setTxtProgressBar(pb, p)
  focus_points<-point_list[[p]]
  type<-unique(focus_points$type)
  if(length(type)>1){
    type <- "Unconnected"
  }
tb <- txtProgressBar(min = 0, max = nrow(focus_points), style = 3)
re<-list()#to save your rasters
for (i in 1:nrow(focus_points)){#only the first 10 pour points
  setTxtProgressBar(tb, i) 
  re[[i]]<-  sed_flow(  
    pp_sf=focus_points[i,],#list of pour points (each element of the list should be a point)
    initial.value = focus_points[i,"N"][[1]],#value with nitrogen export value
    ocean_raster,
    buffer_value=60000,#buffer from pour point (in meters)-change value to make nutrients go farther 
    resolution_raster=1,#in km
    searchdistance=9000,#search distance to snap points to the coast,
    decay_percent=0.005,#5 % of sediment decay
    remaining_left=0.0005#stop when 99.5% of the sediment has spread from the coast
  )
  gc()
}

newextent<-extent(Reduce(extend,re))

re = lapply(re, function(r){extend(r,newextent)})

#set all rasters to same extent
for (i in 1:length(re)){
  r<-re[[i]]
  r<-extend(r,newextent)
  r[is.na(r[])] <- 0 
  re[[i]]<-r
  #print(i)
}

all_re<-Reduce("+", re)

writeRaster(all_re, here(paste0("output_data/Plumes/", type,"_plume.tif")), overwrite = TRUE)

rm(re)
}

```


