---
title: "Fiji_STP_watersheds"
author: "Caitie"
date: "09/09/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)
library(sf)
#library(startR)
library(here)
library(raster)
library(gdalUtils)
library(tabularaster)
library(units)
library(rgdal)
library(lwgeom)
library(fasterize)
library(exactextractr)

t_crs<-"+proj=aea +lat_1=-9 +lat_2=-26 +lat_0=-17 +lon_0=180 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs"
```

# Population density

Source:

https://pacificdata.org/data/dataset/fji_population_grid_2020

Settlement footprint generated by combining 2007 household listing locations and Facebook's High-Resolution Population Density Maps (https://data.humdata.org/dataset/fiji-high-resolution-population-density-maps-demographic-estimates).

Population allocated proportionally using 2017 census population counts at enumeration area level.

Year Population Growth Rate of 0.38% has been applied to update population up to 2020

The human settlement footprint with population allocated has been converted into a 100 m resolution raster.


```{r}
pop_ras<-raster(here("raw_data/Population/fji_population_grid_2020/FJI_Pop_Grid_2020.tif"))
```

```{r}
gdalwarp(srcfile ="/home/kuempel/Fiji_sewage/raw_data/Population/fji_population_grid_2020/FJI_Pop_Grid_2020.tif", dstfile = "/home/kuempel/Fiji_sewage/projected_data/Population/FJI_Pop_Grid_proj.tif", s_srs = "+proj=merc +lon_0=150 +k=1 +x_0=0 +y_0=0 +datum=WGS84 +units=m +no_defs", t_srs = t_crs, r = "bilinear", overwrite = T)
```

```{r}
pop_ras_proj<-raster(here("projected_data/Population/FJI_Pop_Grid_proj.tif"))

pop_ras_proj<-setMinMax(pop_ras_proj)
```


```{r}
fiji_pop_df<-cellStats(pop_ras_proj, "sum")

pop_df<-rasterToPoints(pop_ras_proj) %>% 
  as.data.frame()

fiji_pop_df
# Population is 887648
```


# Connected populations

STP Watershed boundaries

Source - Water Authority Fiji

```{r}
stp<-st_read(here("raw_data/Sewage_plants/Fiji Waste Water Catchment.shp")) %>% 
  st_transform(., crs = t_crs) %>% 
  mutate(STP = ifelse(TREATMENT_ == "NATABUA WWTP", "Natabua WWTP",
                      ifelse(TREATMENT_ == "Navakai PS", "Navakai WWTP", as.character(TREATMENT_)))) %>% 
  mutate(area = st_area(.)) %>% 
  group_by(STP) %>% 
  summarise(area = sum(area, na.rm = T)) %>% 
  filter(!is.na(STP) == T,
         !STP %in% c("ACS WWTP", "Naboro WWTP", "Wailada WWTP"))

#expand_stp<-st_buffer(stp, dist = (as.numeric(stp$area)*0.0001)) #expand by 0.01%
  
stp2<-stp %>% 
  mutate(stp_pop = exact_extract(pop_ras_proj, ., fun = "sum"),
         ID = 1:nrow(stp))


```

```{r}
stp_df<-stp2 %>% 
  as.data.frame() %>% 
  dplyr::select(-geometry)

write.csv(stp_df, here("output_data/Sewage_plants/Connected_population_by_STP.csv"))
```

```{r}
stp3<-st_cast(stp2, "MULTIPOLYGON")
stp_ID_ras<-fasterize(stp3, pop_ras_proj, field = "ID")

writeRaster(stp_ID_ras, here("output_data/Sewage_plants/STP_ID_raster.tif"), overwrite = T)
```

# Summarise population within each STP watershed

```{r}
stp_ras<-raster::mask(pop_ras_proj, stp)

cellStats(stp_ras, "sum")

writeRaster(stp_ras, here("output_data/Population/Connected_population.tif"), overwrite = T)
```

# Prop of population connected

```{r}
conn_pop<-sum(stp2$stp_pop)

prop_pop<-conn_pop/fiji_pop_df

conn_pop
fiji_pop_df
prop_pop

#~16% of population is connected based on these estimates with Felipe's population density layer
#~18.9% of population is connected based on the Facebook population density layer
#17.3% with the facebook layer corrected by Fiji 2017 census

#153242.4
```

# Compare our results to reported results

Source - Table 1 from Fiji national liquid waste management strategy and action plan 2007

```{r}
reported_conn<-read.csv(here("raw_data/Sewage_plants/STP_pop_connected.csv")) %>% 
  mutate(ID = ifelse(STP_name == "Adi_Cakobau School", NA,
                     ifelse(STP_name == "Pacific_Harbour", 1,
                            ifelse(STP_name == "Suva_Kinoya", 2,
                                   ifelse(STP_name == "Naboro Prison", NA,
                                          ifelse(STP_name == "Nausori", 3,
                                                 ifelse(STP_name ==  "Labasa", 4,
                                                        ifelse(STP_name == "Lautoka", 5,
                                                               ifelse(STP_name ==  "Nadi", 6,
                                                                      ifelse(STP_name == "Sigatoka", 7,
                                                                             ifelse(STP_name == "Ba", 8,
                                                                                    ifelse(STP_name == "Wailada", NA, NA))))))))))))

```

Join to estimates

```{r}
pop_check<- stp2 %>% 
  as.data.frame() %>% 
  dplyr::select(-geometry) %>% 
  full_join(., reported_conn, by = "ID") %>% 
  dplyr::select(STP, STP_name, stp_pop, Pop_connected) %>% 
  rename(estimated = stp_pop,
         reported = Pop_connected) %>% 
  mutate(diff = reported - estimated)

write.csv(pop_check,here("output_data/Sewage_plants/STP_population_check.csv"))
```

# Urban

GRUMP data

ATTRIBUTE FIELDS
VALUE	Integer, where 1 = rural and 2 = urban.
NB: Large water bodies have been masked and thus appear as "no data"

```{r}
#grump<-raster(here("raw_data/Population/fjiurextents.asc"))
#grump_prj<-projectRaster(grump, crs = crs(pop_ras))
#grump_fiji<-crop(grump_prj, pop_ras)
#grump_fiji_prj<-projectRaster(grump_fiji, crs = t_crs)
#grump_fiji_res<-resample(grump_fiji_prj, pop_ras_proj)
  
```

```{r}
#urban_ras<-grump_fiji_res
#urban_ras[urban_ras<2]<-0
#urban_ras[urban_ras >0]<-1
```


```{r}
#urban_pop_ras<-pop_ras_proj * urban_ras
#urban_pop<-cellStats(urban_pop_ras, stat = "sum", na.rm = T) #695055.5

#urban_pop/fiji_pop_df #26% of population is urban, reports state 59.1%
```

```{r}
#stp_urban_ras<-stp_ras * urban_pop_ras
#stp_urban_pop<-cellStats(stp_urban_ras, "sum", na.rm = T)

#stp_urban_pop/urban_pop #17.1%
```

These estimates are low - lets' look at Jung data.

From Jung et al. IUCN habitat classifications paper
https://www.nature.com/articles/s41597-020-00599-8.pdf

```{r}
urban<-raster(here("projected_data/Population/Fiji_urban.tif"))
urban<-projectRaster(urban, crs = t_crs)
#urban[urban>0]<-1
```


```{r}
urban<-resample(urban, pop_ras_proj)
urban_pts<-rasterToPoints(urban)
urban_df<-urban_pts %>% 
  as.data.frame() 

urban_ras<-urban
urban_ras[urban_ras>0]<-1
urban_ras[is.na(urban_ras)== T]<-0
```

Population that is urban

```{r}
urban_pop_ras<-pop_ras_proj * urban_ras
urban_pop<-cellStats(urban_pop_ras, stat = "sum", na.rm = T) #695055.5

urban_pop/fiji_pop_df #78% of population is urban, reports state 59.1%
```

Percent of urban population that is connected

```{r}
stp_urban_ras<-stp_ras * urban_pop_ras
stp_urban_pop<-cellStats(stp_urban_ras, "sum", na.rm = T)

stp_urban_pop/urban_pop #14%
```

These estimates are high for total population, but still low for urban.

Let's look at Fiji classified "Urban Areas"

```{r}
ua<-st_read(here("output_data/Population/Urban_area_buffers.shp")) %>% 
  st_transform(., t_crs)
```

```{r}
urban_pop_ua<-as.numeric(extract(pop_ras_proj, ua, fun = sum, na.rm = T))

urban_pop_ua/fiji_pop_df

#58.7% urban

rural_pop<-fiji_pop_df - urban_pop_ua

rural_pop/fiji_pop_df
```

```{r}
stp_ua<-extract(stp_ras, ua, fun = sum, na.rm = T)

stp_ua/urban_pop_ua

#29.1% of connected population is urban, should be ~35.4
```

```{r}
ua_ras<-fasterize(ua, pop_ras_proj)
ua_pts<-rasterToPoints(ua_ras)
ua_df<-ua_pts %>% 
  as.data.frame()  %>% 
  rename(urban_area = layer)
```


# Unconnected

Crop STP catchments from population raster

```{r}
unconnected_ras<-raster::mask(pop_ras_proj, stp, inverse = T)
```

# Septic population

Source: JMP/Fiji census data 2017/WISH Fiji survey (Nabeela data)

```{r}
non_stp<-rasterToPoints(unconnected_ras) %>% 
  as.data.frame() %>% 
  rename(unconnected = FJI_Pop_Grid_proj)

non_stp<-non_stp %>% 
  mutate(id = 1:nrow(non_stp))

pop_ua<-full_join(pop_df, ua_df, by = c("x", "y"))

pop_urban<-full_join(pop_ua, urban_df, by = c("x", "y")) %>% 
  full_join(., non_stp, by = c("x", "y")) 

```

# Conn urban

```{r}
stp_ua<-extract(stp_ras, ua, fun = sum, na.rm = T)

stp_perc_urban<-as.numeric(stp_ua)/urban_pop_ua

#29.1% of connected population is urban, should be ~35.4

# We could try to add in this amount of urban to STP treatment - for now we do not.
conn_urban_target<- 0.354 - stp_perc_urban #From Fiji 2017 census/JMP - percent of urban population with septic
conn_urban_pop_target<-as.numeric(urban_pop_ua*conn_urban_target)
conn_urban_pop_target

```

# Septic Urban

```{r}
septic_urban_perc<-0.59 #From Fiji 2017 census/JMP - percent of urban population with septic
septic_urban_pop_target<-as.numeric(urban_pop_ua*septic_urban_perc)
septic_urban_pop_target

#Septic urban

urban_cat<-pop_urban %>% 
  filter(!is.na(unconnected) == T,
         is.na(FJI_Pop_Grid_proj) == F) %>% 
  mutate(urban_bin = ifelse(Fiji_urban>0,1,0)) %>% 
  filter(urban_area == 1,
         urban_bin == 1) %>% 
  dplyr::arrange(desc(unconnected)) %>% 
  mutate(cumpop = cumsum(FJI_Pop_Grid_proj))

septic_urban<-urban_cat %>% 
  filter(cumpop<=septic_urban_pop_target) 

```


```{r}
# Other urban
other_urban_perc<-0.054 #From Fiji 2017 census/JMP - percent of urban population with septic
other_urban_pop_target<-as.numeric(urban_pop_ua*other_urban_perc)

other_urban<-urban_cat %>% 
  filter(cumpop>septic_urban_pop_target) %>% 
  mutate(cumpop2 = cumsum(FJI_Pop_Grid_proj)) %>% 
  filter(cumpop2<=other_urban_pop_target)
```

```{r}
# Connected rural

rural_non_stp<- non_stp %>% 
  filter(!id %in% septic_urban$id,
         !id %in% other_urban$id)

pop_rural<-full_join(pop_df, rural_non_stp, by = c("x", "y")) %>% 
  full_join(., urban_df, by = c("x", "y"))

conn_rural_perc<-0.014 #From Fiji 2017 census/JMP - percent of urban population with septic
#conn_rural_pop_target<-sum(pop_rural$unconnected, na.rm = T) * conn_rural_perc
conn_rural_pop_target<-rural_pop* conn_rural_perc
conn_rural_pop_target
```




```{r}
# Septic rural
rural_non_stp<- non_stp %>% 
  filter(!id %in% septic_urban$id,
         !id %in% other_urban$id)

pop_rural<-full_join(pop_df, rural_non_stp, by = c("x", "y")) %>% 
  full_join(., urban_df, by = c("x", "y"))

septic_rural_perc<-0.681 #From Fiji 2017 census/JMP - percent of urban population with septic
#septic_rural_pop_target<-sum(pop_rural$unconnected, na.rm = T) * septic_rural_perc
septic_rural_pop_target<-rural_pop * septic_rural_perc
septic_rural_pop_target

rural_cat<-pop_rural %>% 
  filter(!is.na(unconnected) == T,
         is.na(FJI_Pop_Grid_proj) == F) %>% 
  mutate(urban_bin = ifelse(Fiji_urban>0,1,0),
         urban_bin = ifelse(is.na(urban_bin) == T, 0, as.numeric(urban_bin))) %>% 
  dplyr::arrange(desc(unconnected)) %>% 
  dplyr::arrange(desc(urban_bin)) %>% 
  mutate(cumpop = cumsum(FJI_Pop_Grid_proj))

septic_rural<-rural_cat %>% 
  filter(cumpop<=septic_rural_pop_target) 
```

```{r}
# Other rural

other_rural_perc<-0.272 #From Fiji 2017 census/JMP - percent of urban population with septic
#other_rural_pop_target<-sum(pop_rural$unconnected, na.rm = T) * other_rural_perc
other_rural_pop_target<-rural_pop * other_rural_perc
other_rural_pop_target

other_rural<-rural_cat %>% 
  filter(cumpop>septic_rural_pop_target) %>% 
  mutate(cumpop2 = cumsum(unconnected)) %>% 
  filter(cumpop2<=other_rural_pop_target)
```

Check values

```{r}
# Connected urban check
conn_urban_check<-as.numeric(stp_ua/urban_pop_ua)

# Septic Urban
septic_urban_check<-sum(septic_urban$unconnected, na.rm = T)/urban_pop_ua #Should be ~58.9%
septic_urban_check
septic_urban_perc

# Septic Rural
septic_rural_check<-sum(septic_rural$unconnected,na.rm = T)/rural_pop #Should be ~68.1%
septic_rural_check
septic_rural_perc

# Other Urban
other_urban_check<-sum(other_urban$unconnected, na.rm = T)/urban_pop_ua #Should be ~5.4%
other_urban_check
other_urban_perc

# Other Rural
other_rural_check<-sum(other_rural$unconnected,na.rm = T)/rural_pop # Should be ~27.2%
other_rural_check
other_rural_perc
```

```{r}
septic_pop<-sum(septic_urban$unconnected, na.rm = T) + sum(septic_rural$unconnected,na.rm = T)
direct_pop<-sum(other_urban$unconnected, na.rm = T) + sum(other_rural$unconnected,na.rm = T)

national_septic_perc<-septic_pop/fiji_pop_df #Should be ~62.8
national_other_perc<-direct_pop/fiji_pop_df # Should be ~14.8
national_conn_perc<-conn_pop/fiji_pop_df

national_septic_perc
national_other_perc
national_conn_perc
```

```{r}
total_urban<-as.numeric(stp_ua) + sum(septic_urban$unconnected, na.rm = T) + sum(other_urban$unconnected, na.rm = T)
total_urban_perc<-total_urban/urban_pop_ua

total_urban_perc
```


```{r}
total_rural<-sum(septic_rural$unconnected,na.rm = T) + sum(other_rural$unconnected,na.rm = T)
total_rural_perc<-total_rural/rural_pop

total_rural_perc
```


```{r}
total_national<-(conn_pop + septic_pop + direct_pop)
total_national_perc<-(conn_pop + septic_pop + direct_pop)/fiji_pop_df #Should be ~98.4

total_national_perc
```

```{r}
check_treatment_df<-data.frame(improved = c("Sewer", "Septic", "Other", "Total"), urban = c(35.4, 58.9,5.4,99.6), rural = c(1.4, 68.1, 27.2,96.7), national = c(20.7, 62.8, 14.8,98.4))

check_treatment_df <- check_treatment_df %>% 
  mutate(urban_est = case_when(improved == "Sewer" ~ conn_urban_check*100,
                               improved == "Septic" ~ septic_urban_check*100,
                               improved == "Other" ~ other_urban_check*100,
                               improved == "Total" ~ total_urban_perc*100))

check_treatment_df<- check_treatment_df %>% 
         mutate(rural_est = case_when(improved == "Sewer" ~ 0,
                               improved == "Septic" ~ septic_rural_check*100,
                               improved == "Other" ~ other_rural_check*100,
                               improved == "Total" ~ total_rural_perc*100))

check_treatment_df<-check_treatment_df %>% 
         mutate(nation_est = case_when(improved == "Sewer" ~ national_conn_perc*100,
                                improved == "Septic" ~ national_septic_perc*100,
                                improved == "Other" ~ national_other_perc*100,
                                improved == "Total" ~ total_national_perc*100))

write.csv(check_treatment_df, here("tables/Compare_JMP_to_estimates.csv"))
```


```{r}
# Join and spatilise septic

septic_urban2<-septic_urban%>% 
  dplyr::select(x,y,FJI_Pop_Grid_proj)

septic_urban_sp<-st_as_sf(septic_urban2, coords = c("x", "y"), crs = t_crs)

septic_urban_ras<-rasterize(septic_urban_sp, pop_ras_proj, crs = t_crs)

septic_urban_ras_pop<-septic_urban_ras[[2]]

septic_urban_pop<-cellStats(septic_urban_ras_pop, "sum")

septic_urban_pop == sum(septic_urban$unconnected)
```

```{r}
# Join and spatilise septic

septic_rural2<-septic_rural%>% 
  dplyr::select(x,y,FJI_Pop_Grid_proj)

septic_rural_sp<-st_as_sf(septic_rural2, coords = c("x", "y"), crs = t_crs)

septic_rural_ras<-rasterize(septic_rural_sp, pop_ras_proj, crs = t_crs)

septic_rural_ras_pop<-septic_rural_ras[[2]]

septic_rural_pop<-cellStats(septic_rural_ras_pop, "sum")

septic_rural_pop == sum(septic_rural$unconnected)
```
```{r}
# Join and spatilise septic

other_urban2<-other_urban%>% 
  dplyr::select(x,y,FJI_Pop_Grid_proj)

other_urban_sp<-st_as_sf(other_urban2, coords = c("x", "y"), crs = t_crs)

other_urban_ras<-rasterize(other_urban_sp, pop_ras_proj, crs = t_crs)

other_urban_ras_pop<-other_urban_ras[[2]]

other_urban_pop<-cellStats(other_urban_ras_pop, "sum")

other_urban_pop == sum(other_urban$unconnected)
```

```{r}
# Join and spatilise septic

other_rural2<-other_rural%>% 
  dplyr::select(x,y,FJI_Pop_Grid_proj)

other_rural_sp<-st_as_sf(other_rural2, coords = c("x", "y"), crs = t_crs)

other_rural_ras<-rasterize(other_rural_sp, pop_ras_proj, crs = t_crs)

other_rural_ras_pop<-other_rural_ras[[2]]

other_rural_pop<-cellStats(other_rural_ras_pop, "sum")

other_rural_pop == sum(other_rural$unconnected)
```

# All septic raster

```{r}
septic_ras<-stack(septic_urban_ras_pop, septic_rural_ras_pop)

septic_ras_pop<-raster::calc(septic_ras, sum,na.rm = T)

writeRaster(septic_ras_pop,here("output_data/Population/Septic_population.tif"), overwrite = T)
```


# All other raster

```{r}
other_ras<-stack(other_urban_ras_pop,  other_rural_ras_pop)

other_ras_pop<-raster::calc(other_ras, sum,na.rm = T)

writeRaster(other_ras_pop,here("output_data/Population/Direct_population.tif"),overwrite = T)
```







