---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(lubridate)
library(stringr)
```

This code calculates the average N and P removal from each sewage treatment plant in Fiji based on data from Fiji Water Authority.
Advice from WAF is to remove values where the Final effluent > Raw values.

# Flow data 

Flow data is in ML which I assume means million litres

```{r}
wwtp_flow<-read.csv(here("raw_data/Sewage_plants/WWTP_flow_data.csv")) %>% 
  filter(!WWTP == "") %>% 
  pivot_longer(cols = X2010:X2019, names_to = "year", values_to = "flow_ML") %>% 
  mutate(flow_ML = as.numeric(flow_ML)) %>% 
  group_by(WWTP) %>% 
  summarise(avg_flow_ML = mean(flow_ML)) %>% 
  mutate(avg_flow_L = avg_flow_ML*1000000) 
```


# Kinoya

These estimates are in mg/L. Convert to tonnes

```{r}
kinoya<-read.csv(here("raw_data/Sewage_plants/Kinoya_Effluent.csv"), na.string = "N/A") %>% 
  mutate(Date = as.Date(Date, tryFormat = "%d/%m/%Y"),
         year = lubridate::year(Date), 
         month = lubridate::month(Date), 
         day = lubridate::day(Date),
         year = ifelse(year == 15, 2015,
                       ifelse(year == 16, 2016,
                              ifelse(year == 17, 2017,
                                     ifelse(year == 18, 2018,
                                            ifelse(year == 19, 2019,
                                                   ifelse(year ==20, 2020,
                                                          ifelse(year == 2001, 2015,as.numeric(year)))))))),
         Location = as.character(Location),
         Location = ifelse(Location == "Secondary Clarifier Effluent", "Final Effluent", as.character(Location))) %>% 
  filter(year <2020,
         grepl('Raw|Final', Location)) %>% 
  mutate_if(is.character, str_trim) %>% 
  mutate(Total.Reactive.Phosphates = as.numeric(as.character(Total.Reactive.Phosphates)))

```

```{r}

kinoya_flow<-wwtp_flow %>% 
  filter(WWTP == "Kinoya")

kinoya_N<-kinoya %>% 
  dplyr::select(STP, Date, year, month, day,Location, Total.Nitrogen) %>% 
  mutate(Location = ifelse(Location %in% c("Final Effluent 1","Final Effluent -2","Final Effluent [1]","Final Effluent [2]"), "Final Effluent", as.character(Location)),
         Location =ifelse(Location == "Raw Sewage", "Raw", "Final")) %>% 
  group_by(STP, Date, year, month, day, Location) %>% 
  summarise(Avg_N = mean(Total.Nitrogen, na.rm = T)) %>% 
  pivot_wider(., names_from = Location, values_from = Avg_N) %>% 
  #filter(!Final>Raw) %>% 
  mutate(Final_mg = Final * kinoya_flow$avg_flow_L,
         Raw_mg = Raw * kinoya_flow$avg_flow_L,
         Final_tonnes = Final_mg * 1e-9,
         Raw_tonnes = Raw_mg * 1e-9,
         remov_eff = (Raw_tonnes-Final_tonnes)/Raw_tonnes)

kinoya_N_month<- kinoya_N %>% 
  ungroup() %>% 
  group_by(STP, year, month) %>% 
  summarise(Raw_month = mean(Raw_tonnes, na.rm = T),
            Final_month = mean(Final_tonnes, na.rm = T))%>% 
  mutate(rm_eff = (Raw_month-Final_month)/Raw_month)

kinoya_N_year<-kinoya_N_month %>% 
  ungroup() %>% 
  group_by(STP, year) %>% 
  summarise(Raw_year = mean(Raw_month, na.rm = T),
            Final_year = mean(Final_month, na.rm = T)) %>% 
  mutate(rm_eff = (Raw_year-Final_year)/Raw_year)

kinoya_N_rm<-kinoya_N_year %>% 
  group_by(STP) %>% 
  summarise(Raw = mean(Raw_year, na.rm = T),
            Final = mean(Final_year, na.rm = T)) %>% 
  mutate(rm_eff = (Raw-Final)/Raw,
         type = "N")
```

```{r}
kinoya_P<-kinoya %>% 
  dplyr::select(STP, Date, year, month, day,Location, Total.Reactive.Phosphates) %>% 
  mutate(Location = ifelse(Location %in% c("Final Effluent 1","Final Effluent -2","Final Effluent [1]","Final Effluent [2]"), "Final Effluent", as.character(Location)),
         Location =ifelse(Location == "Raw Sewage", "Raw", "Final")) %>% 
  group_by(STP, Date, year, month, day, Location) %>% 
  summarise(Avg_N = mean(Total.Reactive.Phosphates, na.rm = T)) %>% 
  pivot_wider(., names_from = Location, values_from = Avg_N) %>% 
 # filter(!Final>Raw) %>% 
  mutate(Final_mg = Final * kinoya_flow$avg_flow_L,
         Raw_mg = Raw * kinoya_flow$avg_flow_L,
         Final_tonnes = Final_mg * 1e-9,
         Raw_tonnes = Raw_mg * 1e-9,
         remov_eff = (Raw_tonnes-Final_tonnes)/Raw_tonnes)

kinoya_P_month<- kinoya_P %>% 
  ungroup() %>% 
  group_by(STP, year, month) %>% 
  summarise(Raw_month = mean(Raw, na.rm = T),
            Final_month = mean(Final, na.rm = T)) %>% 
  mutate(rm_eff = (Raw_month-Final_month)/Raw_month)

kinoya_P_year<-kinoya_P_month %>% 
  ungroup() %>% 
  group_by(STP, year) %>% 
  summarise(Raw_year = mean(Raw_month, na.rm = T),
            Final_year = mean(Final_month, na.rm = T)) %>% 
  mutate(rm_eff = (Raw_year-Final_year)/Raw_year)

kinoya_P_rm<-kinoya_P_year %>% 
  group_by(STP) %>% 
  summarise(Raw = mean(Raw_year, na.rm = T),
            Final = mean(Final_year, na.rm = T)) %>% 
  mutate(rm_eff = (Raw-Final)/Raw,
         type = "P")
```

# Ba

```{r}
ba<-read.csv(here("raw_data/Sewage_plants/Ba_Effluent.csv"), na.string = "N/A") %>% 
  mutate(Date = as.Date(Date, tryFormat = "%d/%m/%Y"),
         year = lubridate::year(Date), 
         month = lubridate::month(Date), 
         day = lubridate::day(Date),
         year = ifelse(year == 15, 2015,
                       ifelse(year == 16, 2016,
                              ifelse(year == 17, 2017,
                                     ifelse(year == 18, 2018,
                                            ifelse(year == 19, 2019,
                                                   ifelse(year ==20, 2020,
                                                          ifelse(year == 2001, 2015,as.numeric(year)))))))),
         Location = as.character(Location),
         Location = ifelse(Location == "Secondary Clarifier Effluent", "Final Effluent", as.character(Location))) %>% 
  filter(year <2020,
         grepl('Raw|Maturation', Location)) %>% 
  mutate_if(is.character, str_trim) %>% 
  mutate(Location = ifelse(Location %in% c("Maturation Pond",  "Maturation", "Maturation [Final Effluent]"), "Final Effluent", as.character(Location))) %>% 
  mutate(Total.Reactive.Phosphates = as.numeric(as.character(Total.Reactive.Phosphates)))
```


```{r}
ba_N<-ba %>% 
  dplyr::select(STP, Date, year, month, day,Location, Total.Nitrogen) %>% 
  mutate(Location = ifelse(Location %in% c("Final Effluent 1","Final Effluent -2","Final Effluent [1]","Final Effluent [2]"), "Final Effluent", as.character(Location)),
         Location =ifelse(Location == "Raw Sewage", "Raw", "Final")) %>% 
  group_by(STP, Date, year, month, day, Location) %>% 
  summarise(Avg_N = mean(Total.Nitrogen, na.rm = T)) %>% 
  pivot_wider(., names_from = Location, values_from = Avg_N) %>% 
  #filter(!Final>Raw) %>% 
  mutate(rm_eff = (Raw-Final)/Raw)

ba_N_month<- ba_N %>% 
  ungroup() %>% 
  group_by(STP, year, month) %>% 
  summarise(Raw_month = mean(Raw, na.rm = T),
            Final_month = mean(Final, na.rm = T)) %>% 
  mutate(rm_eff = (Raw_month-Final_month)/Raw_month)

ba_N_year<-ba_N_month %>% 
  ungroup() %>% 
  group_by(STP, year) %>% 
  summarise(Raw_year = mean(Raw_month, na.rm = T),
            Final_year = mean(Final_month, na.rm = T)) %>% 
  mutate(rm_eff = (Raw_year-Final_year)/Raw_year)

ba_N_rm<-ba_N_year %>% 
  group_by(STP) %>% 
  summarise(Raw = mean(Raw_year, na.rm = T),
            Final = mean(Final_year, na.rm = T)) %>% 
  mutate(rm_eff = (Raw-Final)/Raw,
         type = "N")
```
```{r}
ba_P<-ba %>% 
  dplyr::select(STP, Date, year, month, day,Location, Total.Reactive.Phosphates) %>% 
  mutate(Location =ifelse(Location == "Raw Sewage", "Raw", "Final")) %>% 
  group_by(STP, Date, year, month, day, Location) %>% 
  summarise(Avg_N = mean(Total.Reactive.Phosphates, na.rm = T)) %>% 
  pivot_wider(., names_from = Location, values_from = Avg_N) %>% 
  #filter(!Final>Raw) %>% 
  mutate(rm_eff = (Raw-Final)/Raw)

ba_P_month<- ba_P %>% 
  ungroup() %>% 
  group_by(STP, year, month) %>% 
  summarise(Raw_month = mean(Raw, na.rm = T),
            Final_month = mean(Final, na.rm = T))%>% 
  mutate(rm_eff = (Raw_month-Final_month)/Raw_month)

ba_P_year<-ba_P_month %>% 
  ungroup() %>% 
  group_by(STP, year) %>% 
  summarise(Raw_year = mean(Raw_month, na.rm = T),
            Final_year = mean(Final_month, na.rm = T)) %>% 
  mutate(rm_eff = (Raw_year-Final_year)/Raw_year)

ba_P_rm<-ba_P_year %>% 
  group_by(STP) %>% 
  summarise(Raw = mean(Raw_year, na.rm = T),
            Final = mean(Final_year, na.rm = T)) %>% 
  mutate(rm_eff = (Raw-Final)/Raw,
         type = "P")
```
# Lautoka

```{r}
lautoka<-read.csv(here("raw_data/Sewage_plants/Lautoka_Effluent.csv"), na.string = "N/A") %>% 
  mutate(Date = as.Date(Date, tryFormat = "%d/%m/%Y"),
         year = lubridate::year(Date), 
         month = lubridate::month(Date), 
         day = lubridate::day(Date),
         year = ifelse(year == 15, 2015,
                       ifelse(year == 16, 2016,
                              ifelse(year == 17, 2017,
                                     ifelse(year == 18, 2018,
                                            ifelse(year == 19, 2019,
                                                   ifelse(year ==20, 2020,
                                                          ifelse(year == 2001, 2015,as.numeric(year)))))))),
         Location = as.character(Location)) %>% 
  filter(year <2020,
         grepl('Raw|Maturation', Location)) %>% 
  mutate_if(is.character, str_trim) %>% 
  mutate(Location = ifelse(Location %in% c("Maturation Pond [1]","Maturation Pond [2]", "Maturation Pond 1","Maturation Pond 2","Maturation Pond","Maturation Pond [2","Maturation 1","Maturation 2"), "Final Effluent", as.character(Location))) %>% 
  mutate(Total.Reactive.Phosphates = as.numeric(as.character(Total.Reactive.Phosphates)))
```


```{r}
lautoka_N<-lautoka %>% 
  dplyr::select(STP, Date, year, month, day,Location, Total.Nitrogen) %>% 
  mutate(Location =ifelse(Location == "Raw Sewage", "Raw", "Final")) %>% 
  group_by(STP, Date, year, month, day, Location) %>% 
  summarise(Avg_N = mean(Total.Nitrogen, na.rm = T)) %>% 
  pivot_wider(., names_from = Location, values_from = Avg_N) %>% 
  #filter(!Final>Raw) %>% 
  mutate(rm_eff = (Raw-Final)/Raw)

lautoka_N_month<- lautoka_N %>% 
  ungroup() %>% 
  group_by(STP, year, month) %>% 
  summarise(Raw_month = mean(Raw, na.rm = T),
            Final_month = mean(Final, na.rm = T)) %>% 
  mutate(rm_eff = (Raw_month-Final_month)/Raw_month)

lautoka_N_year<-lautoka_N_month %>% 
  ungroup() %>% 
  group_by(STP, year) %>% 
  summarise(Raw_year = mean(Raw_month, na.rm = T),
            Final_year = mean(Final_month, na.rm = T)) %>% 
  mutate(rm_eff = (Raw_year-Final_year)/Raw_year)

lautoka_N_rm<-lautoka_N_year %>% 
  group_by(STP) %>% 
  summarise(Raw = mean(Raw_year, na.rm = T),
            Final = mean(Final_year, na.rm = T)) %>% 
  mutate(rm_eff = (Raw-Final)/Raw,
         type = "N")
```
```{r}
lautoka_P<-lautoka %>% 
  dplyr::select(STP, Date, year, month, day,Location, Total.Reactive.Phosphates) %>% 
  mutate(Location = ifelse(Location %in% c("Final Effluent 1","Final Effluent -2","Final Effluent [1]","Final Effluent [2]"), "Final Effluent", as.character(Location)),
         Location =ifelse(Location == "Raw Sewage", "Raw", "Final")) %>% 
  group_by(STP, Date, year, month, day, Location) %>% 
  summarise(Avg_N = mean(Total.Reactive.Phosphates, na.rm = T)) %>% 
  pivot_wider(., names_from = Location, values_from = Avg_N) %>% 
  #filter(!Final>Raw) %>% 
  mutate(rm_eff = (Raw-Final)/Raw)

lautoka_P_month<- lautoka_P %>% 
  ungroup() %>% 
  group_by(STP, year, month) %>% 
  summarise(Raw_month = mean(Raw, na.rm = T),
            Final_month = mean(Final, na.rm = T)) %>% 
  mutate(rm_eff = (Raw_month-Final_month)/Raw_month)

lautoka_P_year<-lautoka_P_month %>% 
  ungroup() %>% 
  group_by(STP, year) %>% 
  summarise(Raw_year = mean(Raw_month, na.rm = T),
            Final_year = mean(Final_month, na.rm = T))  %>% 
  mutate(rm_eff = (Raw_year-Final_year)/Raw_year)

lautoka_P_rm<-lautoka_P_year %>% 
  group_by(STP) %>% 
  summarise(Raw = mean(Raw_year, na.rm = T),
            Final = mean(Final_year, na.rm = T)) %>% 
  mutate(rm_eff = (Raw-Final)/Raw,
         type = "P")
```
# Naboro

```{r}
naboro<-read.csv(here("raw_data/Sewage_plants/Naboro_Effluent.csv"), na.string = "N/A") %>% 
  mutate(Date = as.Date(Date, tryFormat = "%d/%m/%Y"),
         year = lubridate::year(Date), 
         month = lubridate::month(Date), 
         day = lubridate::day(Date),
         year = ifelse(year == 15, 2015,
                       ifelse(year == 16, 2016,
                              ifelse(year == 17, 2017,
                                     ifelse(year == 18, 2018,
                                            ifelse(year == 19, 2019,
                                                   ifelse(year ==20, 2020,
                                                          ifelse(year == 2001, 2015,as.numeric(year)))))))),
         Location = as.character(Location)) %>% 
  filter(year <2020,
         grepl('Raw|Final', Location)) %>% 
  mutate_if(is.character, str_trim)  %>% 
  mutate(Total.Reactive.Phosphates = as.numeric(as.character(Total.Reactive.Phosphates)))
```


```{r}
naboro_N<-naboro %>% 
  dplyr::select(STP, Date, year, month, day,Location, Total.Nitrogen) %>% 
  mutate(Location =ifelse(Location == "Raw Sewage", "Raw", "Final")) %>% 
  group_by(STP, Date, year, month, day, Location) %>% 
  summarise(Avg_N = mean(Total.Nitrogen, na.rm = T)) %>% 
  pivot_wider(., names_from = Location, values_from = Avg_N) %>% 
  #filter(!Final>Raw) %>% 
  mutate(rm_eff = (Raw-Final)/Raw)

naboro_N_month<- naboro_N %>% 
  ungroup() %>% 
  group_by(STP, year, month) %>% 
  summarise(Raw_month = mean(Raw, na.rm = T),
            Final_month = mean(Final, na.rm = T)) %>% 
  mutate(rm_eff = (Raw_month-Final_month)/Raw_month)

naboro_N_year<-naboro_N_month %>% 
  ungroup() %>% 
  group_by(STP, year) %>% 
  summarise(Raw_year = mean(Raw_month, na.rm = T),
            Final_year = mean(Final_month, na.rm = T)) %>% 
  mutate(rm_eff = (Raw_year-Final_year)/Raw_year)

naboro_N_rm<-naboro_N_year %>% 
  group_by(STP) %>% 
  summarise(Raw = mean(Raw_year, na.rm = T),
            Final = mean(Final_year, na.rm = T)) %>% 
  mutate(rm_eff = (Raw-Final)/Raw,
         type = "N")
```
```{r}
naboro_P<-naboro %>% 
  dplyr::select(STP, Date, year, month, day,Location, Total.Reactive.Phosphates) %>% 
  mutate(Location = ifelse(Location %in% c("Final Effluent 1","Final Effluent -2","Final Effluent [1]","Final Effluent [2]"), "Final Effluent", as.character(Location)),
         Location =ifelse(Location == "Raw Sewage", "Raw", "Final")) %>% 
  group_by(STP, Date, year, month, day, Location) %>% 
  summarise(Avg_N = mean(Total.Reactive.Phosphates, na.rm = T)) %>% 
  pivot_wider(., names_from = Location, values_from = Avg_N) %>% 
  #filter(!Final>Raw) %>% 
  mutate(rm_eff = (Raw-Final)/Raw)

naboro_P_month<- naboro_P %>% 
  ungroup() %>% 
  group_by(STP, year, month) %>% 
  summarise(Raw_month = mean(Raw, na.rm = T),
            Final_month = mean(Final, na.rm = T)) %>% 
  mutate(rm_eff = (Raw_month-Final_month)/Raw_month)

naboro_P_year<-naboro_P_month %>% 
  ungroup() %>% 
  group_by(STP, year) %>% 
  summarise(Raw_year = mean(Raw_month, na.rm = T),
            Final_year = mean(Final_month, na.rm = T))  %>% 
  mutate(rm_eff = (Raw_year-Final_year)/Raw_year)

naboro_P_rm<-naboro_P_year %>% 
  group_by(STP) %>% 
  summarise(Raw = mean(Raw_year, na.rm = T),
            Final = mean(Final_year, na.rm = T)) %>% 
  mutate(rm_eff = (Raw-Final)/Raw,
         type = "P")
```
# Nadali

```{r}
nadali<-read.csv(here("raw_data/Sewage_plants/Nadali_Effluent.csv"), na.string = "N/A") %>% 
  mutate(Date = as.Date(Date, tryFormat = "%d/%m/%Y"),
         year = lubridate::year(Date), 
         month = lubridate::month(Date), 
         day = lubridate::day(Date),
         year = ifelse(year == 15, 2015,
                       ifelse(year == 16, 2016,
                              ifelse(year == 17, 2017,
                                     ifelse(year == 18, 2018,
                                            ifelse(year == 19, 2019,
                                                   ifelse(year ==20, 2020,
                                                          ifelse(year == 2001, 2015,as.numeric(year)))))))),
         Location = as.character(Location)) %>% 
  filter(year <2020,
         grepl('Raw|Final', Location)) %>% 
  mutate_if(is.character, str_trim)  %>% 
  mutate(Total.Reactive.Phosphates = as.numeric(as.character(Total.Reactive.Phosphates)))
```


```{r}
nadali_N<-nadali %>% 
  dplyr::select(STP, Date, year, month, day,Location, Total.Nitrogen) %>% 
  mutate(Location =ifelse(Location == "Raw Sewage", "Raw", "Final")) %>% 
  group_by(STP, Date, year, month, day, Location) %>% 
  summarise(Avg_N = mean(Total.Nitrogen, na.rm = T)) %>% 
  pivot_wider(., names_from = Location, values_from = Avg_N) %>% 
  #filter(!Final>Raw) %>% 
  mutate(rm_eff = (Raw-Final)/Raw)

nadali_N_month<- nadali_N %>% 
  ungroup() %>% 
  group_by(STP, year, month) %>% 
  summarise(Raw_month = mean(Raw, na.rm = T),
            Final_month = mean(Final, na.rm = T)) %>% 
  mutate(rm_eff = (Raw_month-Final_month)/Raw_month)

nadali_N_year<-nadali_N_month %>% 
  ungroup() %>% 
  group_by(STP, year) %>% 
  summarise(Raw_year = mean(Raw_month, na.rm = T),
            Final_year = mean(Final_month, na.rm = T)) %>% 
  mutate(rm_eff = (Raw_year-Final_year)/Raw_year)

nadali_N_rm<-nadali_N_year %>% 
  group_by(STP) %>% 
  summarise(Raw = mean(Raw_year, na.rm = T),
            Final = mean(Final_year, na.rm = T)) %>% 
  mutate(rm_eff = (Raw-Final)/Raw,
         type = "N")
```
```{r}
nadali_P<-nadali %>% 
  dplyr::select(STP, Date, year, month, day,Location, Total.Reactive.Phosphates) %>% 
  mutate(Location = ifelse(Location %in% c("Final Effluent 1","Final Effluent -2","Final Effluent [1]","Final Effluent [2]"), "Final Effluent", as.character(Location)),
         Location =ifelse(Location == "Raw Sewage", "Raw", "Final")) %>% 
  group_by(STP, Date, year, month, day, Location) %>% 
  summarise(Avg_N = mean(Total.Reactive.Phosphates, na.rm = T)) %>% 
  pivot_wider(., names_from = Location, values_from = Avg_N) %>%
 # filter(!Final>Raw) %>% 
  mutate(rm_eff = (Raw-Final)/Raw)

nadali_P_month<- nadali_P %>% 
  ungroup() %>% 
  group_by(STP, year, month) %>% 
  summarise(Raw_month = mean(Raw, na.rm = T),
            Final_month = mean(Final, na.rm = T)) %>% 
  mutate(rm_eff = (Raw_month-Final_month)/Raw_month)

nadali_P_year<-nadali_P_month %>% 
  ungroup() %>% 
  group_by(STP, year) %>% 
  summarise(Raw_year = mean(Raw_month, na.rm = T),
            Final_year = mean(Final_month, na.rm = T)) %>% 
  mutate(rm_eff = (Raw_year-Final_year)/Raw_year)

nadali_P_rm<-nadali_P_year %>% 
  group_by(STP) %>% 
  summarise(Raw = mean(Raw_year, na.rm = T),
            Final = mean(Final_year, na.rm = T)) %>% 
  mutate(rm_eff = (Raw-Final)/Raw,
         type = "P")
```
# Namara

```{r}
namara<-read.csv(here("raw_data/Sewage_plants/Namara_Effluent.csv"), na.string = "N/A") %>% 
  mutate(Date = as.Date(Date, tryFormat = "%d/%m/%Y"),
         year = lubridate::year(Date), 
         month = lubridate::month(Date), 
         day = lubridate::day(Date),
         year = ifelse(year == 15, 2015,
                       ifelse(year == 16, 2016,
                              ifelse(year == 17, 2017,
                                     ifelse(year == 18, 2018,
                                            ifelse(year == 19, 2019,
                                                   ifelse(year ==20, 2020,
                                                          ifelse(year == 2001, 2015,as.numeric(year)))))))),
         Location = as.character(Location),
         Location = ifelse(Location == "Secondary Clarifier Effluent", "Final Effluent", as.character(Location))) %>% 
  filter(year <2020,
         grepl('Raw|Maturation', Location)) %>% 
  mutate_if(is.character, str_trim) %>% 
  mutate(Location = ifelse(Location %in% c("Maturation Pond",  "Maturation"), "Final Effluent", as.character(Location))) %>% 
  mutate(Total.Reactive.Phosphates = as.numeric(as.character(Total.Reactive.Phosphates)))
```


```{r}
namara_N<-namara %>% 
  dplyr::select(STP, Date, year, month, day,Location, Total.Nitrogen) %>% 
  mutate(Location =ifelse(Location == "Raw Sewage", "Raw", "Final")) %>% 
  group_by(STP, Date, year, month, day, Location) %>% 
  summarise(Avg_N = mean(Total.Nitrogen, na.rm = T)) %>% 
  pivot_wider(., names_from = Location, values_from = Avg_N) %>% 
  #filter(!Final>Raw) %>% 
  mutate(rm_eff = (Raw-Final)/Raw)

namara_N_month<- namara_N %>% 
  ungroup() %>% 
  group_by(STP, year, month) %>% 
  summarise(Raw_month = mean(Raw, na.rm = T),
            Final_month = mean(Final, na.rm = T)) %>% 
  mutate(rm_eff = (Raw_month-Final_month)/Raw_month)

namara_N_year<-namara_N_month %>% 
  ungroup() %>% 
  group_by(STP, year) %>% 
  summarise(Raw_year = mean(Raw_month, na.rm = T),
            Final_year = mean(Final_month, na.rm = T)) %>% 
  mutate(rm_eff = (Raw_year-Final_year)/Raw_year)

namara_N_rm<-namara_N_year %>% 
  group_by(STP) %>% 
  summarise(Raw = mean(Raw_year, na.rm = T),
            Final = mean(Final_year, na.rm = T)) %>% 
  mutate(rm_eff = (Raw-Final)/Raw,
         type = "N")
```
```{r}
namara_P<-namara %>% 
  dplyr::select(STP, Date, year, month, day,Location, Total.Reactive.Phosphates) %>% 
  mutate(Location = ifelse(Location %in% c("Final Effluent 1","Final Effluent -2","Final Effluent [1]","Final Effluent [2]"), "Final Effluent", as.character(Location)),
         Location =ifelse(Location == "Raw Sewage", "Raw", "Final")) %>% 
  group_by(STP, Date, year, month, day, Location) %>% 
  summarise(Avg_N = mean(Total.Reactive.Phosphates, na.rm = T)) %>% 
  pivot_wider(., names_from = Location, values_from = Avg_N) %>% 
  #filter(!Final>Raw) %>% 
  mutate(rm_eff = (Raw-Final)/Raw)

namara_P_month<- namara_P %>% 
  ungroup() %>% 
  group_by(STP, year, month) %>% 
  summarise(Raw_month = mean(Raw, na.rm = T),
            Final_month = mean(Final, na.rm = T)) %>% 
  mutate(rm_eff = (Raw_month-Final_month)/Raw_month)

namara_P_year<-namara_P_month %>% 
  ungroup() %>% 
  group_by(STP, year) %>% 
  summarise(Raw_year = mean(Raw_month, na.rm = T),
            Final_year = mean(Final_month, na.rm = T)) %>% 
  mutate(rm_eff = (Raw_year-Final_year)/Raw_year)

namara_P_rm<-namara_P_year %>% 
  group_by(STP) %>% 
  summarise(Raw = mean(Raw_year, na.rm = T),
            Final = mean(Final_year, na.rm = T)) %>% 
  mutate(rm_eff = (Raw-Final)/Raw,
         type = "P")
```
# Navakai

```{r}
navakai<-read.csv(here("raw_data/Sewage_plants/Navakai_Effluent.csv"), na.string = "N/A") %>% 
  mutate(Date = as.Date(Date, tryFormat = "%d/%m/%Y"),
         year = lubridate::year(Date), 
         month = lubridate::month(Date), 
         day = lubridate::day(Date),
         year = ifelse(year == 15, 2015,
                       ifelse(year == 16, 2016,
                              ifelse(year == 17, 2017,
                                     ifelse(year == 18, 2018,
                                            ifelse(year == 19, 2019,
                                                   ifelse(year ==20, 2020,
                                                          ifelse(year == 2001, 2015,as.numeric(year)))))))),
         Location = as.character(Location)) %>% 
  filter(year <2020,
         grepl('Raw|Decant|Final', Location)) %>% 
  mutate_if(is.character, str_trim) %>%
  mutate(Location = ifelse(Location %in% c("Decant",  "Decant", "Final Decand"), "Final Effluent", as.character("Raw Sewage"))) %>% 
  mutate(Total.Reactive.Phosphates = as.numeric(as.character(Total.Reactive.Phosphates)))
```


```{r}
navakai_N<-navakai %>% 
  dplyr::select(STP, Date, year, month, day,Location, Total.Nitrogen) %>% 
  mutate(Location =ifelse(Location == "Raw Sewage", "Raw", "Final")) %>% 
  group_by(STP, Date, year, month, day, Location) %>% 
  summarise(Avg_N = mean(Total.Nitrogen, na.rm = T)) %>% 
  pivot_wider(., names_from = Location, values_from = Avg_N) %>% 
 # filter(!Final>Raw) %>% 
  mutate(rm_eff = (Raw-Final)/Raw)

navakai_N_month<- navakai_N %>% 
  ungroup() %>% 
  group_by(STP, year, month) %>% 
  summarise(Raw_month = mean(Raw, na.rm = T),
            Final_month = mean(Final, na.rm = T)) %>% 
  mutate(rm_eff = (Raw_month-Final_month)/Raw_month)

navakai_N_year<-navakai_N_month %>% 
  ungroup() %>% 
  group_by(STP, year) %>% 
  summarise(Raw_year = mean(Raw_month, na.rm = T),
            Final_year = mean(Final_month, na.rm = T)) %>% 
  mutate(rm_eff = (Raw_year-Final_year)/Raw_year)

navakai_N_rm<-navakai_N_year %>% 
  group_by(STP) %>% 
  summarise(Raw = mean(Raw_year, na.rm = T),
            Final = mean(Final_year, na.rm = T)) %>% 
  mutate(rm_eff = (Raw-Final)/Raw,
         type = "N")
```
```{r}
navakai_P<-navakai %>% 
  dplyr::select(STP, Date, year, month, day,Location, Total.Reactive.Phosphates) %>% 
  mutate(Location = ifelse(Location %in% c("Final Effluent 1","Final Effluent -2","Final Effluent [1]","Final Effluent [2]"), "Final Effluent", as.character(Location)),
         Location =ifelse(Location == "Raw Sewage", "Raw", "Final")) %>% 
  group_by(STP, Date, year, month, day, Location) %>% 
  summarise(Avg_N = mean(Total.Reactive.Phosphates, na.rm = T)) %>% 
  pivot_wider(., names_from = Location, values_from = Avg_N) %>% 
  #filter(!Final>Raw) %>% 
  mutate(rm_eff = (Raw-Final)/Raw)

navakai_P_month<- navakai_P %>% 
  ungroup() %>% 
  group_by(STP, year, month) %>% 
  summarise(Raw_month = mean(Raw, na.rm = T),
            Final_month = mean(Final, na.rm = T)) %>% 
  mutate(rm_eff = (Raw_month-Final_month)/Raw_month)

navakai_P_year<-navakai_P_month %>% 
  ungroup() %>% 
  group_by(STP, year) %>% 
  summarise(Raw_year = mean(Raw_month, na.rm = T),
            Final_year = mean(Final_month, na.rm = T))%>% 
  mutate(rm_eff = (Raw_year-Final_year)/Raw_year)

navakai_P_rm<-navakai_P_year %>% 
  group_by(STP) %>% 
  summarise(Raw = mean(Raw_year, na.rm = T),
            Final = mean(Final_year, na.rm = T)) %>% 
  mutate(rm_eff = (Raw-Final)/Raw,
         type = "P")
```
# Olosara

```{r}
olosara<-read.csv(here("raw_data/Sewage_plants/Olosara_Effluent.csv"), na.string = "N/A") %>% 
  mutate(Date = as.Date(Date, tryFormat = "%d/%m/%Y"),
         year = lubridate::year(Date), 
         month = lubridate::month(Date), 
         day = lubridate::day(Date),
         year = ifelse(year == 15, 2015,
                       ifelse(year == 16, 2016,
                              ifelse(year == 17, 2017,
                                     ifelse(year == 18, 2018,
                                            ifelse(year == 19, 2019,
                                                   ifelse(year ==20, 2020,
                                                          ifelse(year == 2001, 2015,as.numeric(year)))))))),
         Location = as.character(Location),
         Location = ifelse(Location == "Secondary Clarifier Effluent", "Final Effluent", as.character(Location))) %>% 
  filter(year <2020,
         grepl('Raw|Maturation', Location)) %>% 
  mutate_if(is.character, str_trim) %>% 
  mutate(Location = ifelse(Location %in% c("Maturation Pond",  "Maturation"), "Final Effluent", as.character(Location))) %>% 
  mutate(Total.Reactive.Phosphates = as.numeric(as.character(Total.Reactive.Phosphates)))
```


```{r}
olosara_N<-olosara %>% 
  dplyr::select(STP, Date, year, month, day,Location, Total.Nitrogen) %>% 
  mutate(Location =ifelse(Location == "Raw Sewage", "Raw", "Final")) %>% 
  group_by(STP, Date, year, month, day, Location) %>% 
  summarise(Avg_N = mean(Total.Nitrogen, na.rm = T)) %>% 
  pivot_wider(., names_from = Location, values_from = Avg_N) %>% 
  #filter(!Final>Raw) %>% 
  mutate(rm_eff = (Raw-Final)/Raw)

olosara_N_month<- olosara_N %>% 
  ungroup() %>% 
  group_by(STP, year, month) %>% 
  summarise(Raw_month = mean(Raw, na.rm = T),
            Final_month = mean(Final, na.rm = T)) %>% 
  mutate(rm_eff = (Raw_month-Final_month)/Raw_month)

olosara_N_year<-olosara_N_month %>% 
  ungroup() %>% 
  group_by(STP, year) %>% 
  summarise(Raw_year = mean(Raw_month, na.rm = T),
            Final_year = mean(Final_month, na.rm = T)) %>% 
  mutate(rm_eff = (Raw_year-Final_year)/Raw_year)

olosara_N_rm<-olosara_N_year %>% 
  group_by(STP) %>% 
  summarise(Raw = mean(Raw_year, na.rm = T),
            Final = mean(Final_year, na.rm = T)) %>% 
  mutate(rm_eff = (Raw-Final)/Raw,
         type = "N")
```
```{r}
olosara_P<-olosara %>% 
  dplyr::select(STP, Date, year, month, day,Location, Total.Reactive.Phosphates) %>% 
  mutate(Location = ifelse(Location %in% c("Final Effluent 1","Final Effluent -2","Final Effluent [1]","Final Effluent [2]"), "Final Effluent", as.character(Location)),
         Location =ifelse(Location == "Raw Sewage", "Raw", "Final")) %>% 
  group_by(STP, Date, year, month, day, Location) %>% 
  summarise(Avg_N = mean(Total.Reactive.Phosphates, na.rm = T)) %>% 
  pivot_wider(., names_from = Location, values_from = Avg_N) %>% 
  #filter(!Final>Raw) %>% 
  mutate(rm_eff = (Raw-Final)/Raw)

olosara_P_month<- olosara_P %>% 
  ungroup() %>% 
  group_by(STP, year, month) %>% 
  summarise(Raw_month = mean(Raw, na.rm = T),
            Final_month = mean(Final, na.rm = T)) %>% 
  mutate(rm_eff = (Raw_month-Final_month)/Raw_month)

olosara_P_year<-olosara_P_month %>% 
  ungroup() %>% 
  group_by(STP, year) %>% 
  summarise(Raw_year = mean(Raw_month, na.rm = T),
            Final_year = mean(Final_month, na.rm = T))  %>% 
  mutate(rm_eff = (Raw_year-Final_year)/Raw_year)

olosara_P_rm<-olosara_P_year %>% 
  group_by(STP) %>% 
  summarise(Raw = mean(Raw_year, na.rm = T),
            Final = mean(Final_year, na.rm = T)) %>% 
  mutate(rm_eff = (Raw-Final)/Raw,
         type = "P")
```
# Wailada

```{r}
wailada<-read.csv(here("raw_data/Sewage_plants/Wailada_Effluent.csv"), na.string = "N/A") %>% 
  mutate(Date = as.Date(Date, tryFormat = "%d/%m/%Y"),
         year = lubridate::year(Date), 
         month = lubridate::month(Date), 
         day = lubridate::day(Date),
         year = ifelse(year == 15, 2015,
                       ifelse(year == 16, 2016,
                              ifelse(year == 17, 2017,
                                     ifelse(year == 18, 2018,
                                            ifelse(year == 19, 2019,
                                                   ifelse(year ==20, 2020,
                                                          ifelse(year == 2001, 2015,as.numeric(year)))))))),
         Location = as.character(Location),
         Location = ifelse(Location == "Secondary Clarifier Effluent", "Final Effluent", as.character(Location))) %>% 
  filter(year <2020,
         grepl('Raw|Final', Location)) %>% 
  mutate_if(is.character, str_trim)  %>% 
  mutate(Total.Reactive.Phosphates = as.numeric(as.character(Total.Reactive.Phosphates)))
```


```{r}
wailada_N<-wailada %>% 
  dplyr::select(STP, Date, year, month, day,Location, Total.Nitrogen) %>% 
  mutate(Location =ifelse(Location == "Raw Sewage", "Raw", "Final")) %>% 
  group_by(STP, Date, year, month, day, Location) %>% 
  summarise(Avg_N = mean(Total.Nitrogen, na.rm = T)) %>% 
  pivot_wider(., names_from = Location, values_from = Avg_N) %>%
  #filter(!Final>Raw) %>% 
  mutate(rm_eff = (Raw-Final)/Raw)

wailada_N_month<- wailada_N %>% 
  ungroup() %>% 
  group_by(STP, year, month) %>% 
  summarise(Raw_month = mean(Raw, na.rm = T),
            Final_month = mean(Final, na.rm = T)) %>% 
  mutate(rm_eff = (Raw_month-Final_month)/Raw_month)

wailada_N_year<-wailada_N_month %>% 
  ungroup() %>% 
  group_by(STP, year) %>% 
  summarise(Raw_year = mean(Raw_month, na.rm = T),
            Final_year = mean(Final_month, na.rm = T)) %>% 
  mutate(rm_eff = (Raw_year-Final_year)/Raw_year)

wailada_N_rm<-wailada_N_year %>% 
  group_by(STP) %>% 
  summarise(Raw = mean(Raw_year, na.rm = T),
            Final = mean(Final_year, na.rm = T)) %>% 
  mutate(rm_eff = (Raw-Final)/Raw,
         type = "N")
```
```{r}
wailada_P<-wailada %>% 
  dplyr::select(STP, Date, year, month, day,Location, Total.Reactive.Phosphates) %>% 
  mutate(Location = ifelse(Location %in% c("Final Effluent 1","Final Effluent -2","Final Effluent [1]","Final Effluent [2]"), "Final Effluent", as.character(Location)),
         Location =ifelse(Location == "Raw Sewage", "Raw", "Final")) %>% 
  group_by(STP, Date, year, month, day, Location) %>% 
  summarise(Avg_N = mean(Total.Reactive.Phosphates, na.rm = T)) %>% 
  pivot_wider(., names_from = Location, values_from = Avg_N) %>% 
 # filter(!Final>Raw) %>% 
  mutate(rm_eff = (Raw-Final)/Raw)

wailada_P_month<- wailada_P %>% 
  ungroup() %>% 
  group_by(STP, year, month) %>% 
  summarise(Raw_month = mean(Raw, na.rm = T),
            Final_month = mean(Final, na.rm = T)) %>% 
  mutate(rm_eff = (Raw_month-Final_month)/Raw_month)

wailada_P_year<-wailada_P_month %>% 
  ungroup() %>% 
  group_by(STP, year) %>% 
  summarise(Raw_year = mean(Raw_month, na.rm = T),
            Final_year = mean(Final_month, na.rm = T)) %>% 
  mutate(rm_eff = (Raw_year-Final_year)/Raw_year)

wailada_P_rm<-wailada_P_year %>% 
  group_by(STP) %>% 
  summarise(Raw = mean(Raw_year, na.rm = T),
            Final = mean(Final_year, na.rm = T)) %>% 
  mutate(rm_eff = (Raw-Final)/Raw,
         type = "P")
```
# Deuba

```{r}
deuba<-read.csv(here("raw_data/Sewage_plants/Deuba_Effluent.csv"), na.string = "N/A") %>% 
  mutate(Date = as.Date(Date, tryFormat = "%d/%m/%Y"),
         year = lubridate::year(Date), 
         month = lubridate::month(Date), 
         day = lubridate::day(Date),
         year = ifelse(year == 15, 2015,
                       ifelse(year == 16, 2016,
                              ifelse(year == 17, 2017,
                                     ifelse(year == 18, 2018,
                                            ifelse(year == 19, 2019,
                                                   ifelse(year ==20, 2020,
                                                          ifelse(year == 2001, 2015,as.numeric(year)))))))),
         Location = as.character(Location),
         Location = ifelse(Location == "Secondary Clarifier Effluent", "Final Effluent", as.character(Location))) %>% 
  filter(year <2020,
         grepl('Raw|Final', Location)) %>% 
  mutate_if(is.character, str_trim)  %>% 
  mutate(Total.Reactive.Phosphates = as.numeric(as.character(Total.Reactive.Phosphates)))
```


```{r}
deuba_N<-deuba %>% 
  dplyr::select(STP, Date, year, month, day,Location, Total.Nitrogen) %>% 
  mutate(Location =ifelse(Location == "Raw Sewage", "Raw", "Final")) %>% 
  group_by(STP, Date, year, month, day, Location) %>% 
  summarise(Avg_N = mean(Total.Nitrogen, na.rm = T)) %>% 
  pivot_wider(., names_from = Location, values_from = Avg_N) %>% 
  #filter(!Final>Raw) %>% 
  mutate(rm_eff = (Raw-Final)/Raw)

deuba_N_month<- deuba_N %>% 
  ungroup() %>% 
  group_by(STP, year, month) %>% 
  summarise(Raw_month = mean(Raw, na.rm = T),
            Final_month = mean(Final, na.rm = T)) %>% 
  mutate(rm_eff = (Raw_month-Final_month)/Raw_month)

deuba_N_year<-deuba_N_month %>% 
  ungroup() %>% 
  group_by(STP, year) %>% 
  summarise(Raw_year = mean(Raw_month, na.rm = T),
            Final_year = mean(Final_month, na.rm = T)) %>% 
  mutate(rm_eff = (Raw_year-Final_year)/Raw_year)

deuba_N_rm<-deuba_N_year %>% 
  group_by(STP) %>% 
  summarise(Raw = mean(Raw_year, na.rm = T),
            Final = mean(Final_year, na.rm = T)) %>% 
  mutate(rm_eff = (Raw-Final)/Raw,
         type = "N")
```
```{r}
deuba_P<-deuba %>% 
  dplyr::select(STP, Date, year, month, day,Location, Total.Reactive.Phosphates) %>% 
  mutate(Location = ifelse(Location %in% c("Final Effluent 1","Final Effluent -2","Final Effluent [1]","Final Effluent [2]"), "Final Effluent", as.character(Location)),
         Location =ifelse(Location == "Raw Sewage", "Raw", "Final")) %>% 
  group_by(STP, Date, year, month, day, Location) %>% 
  summarise(Avg_N = mean(Total.Reactive.Phosphates, na.rm = T)) %>% 
  pivot_wider(., names_from = Location, values_from = Avg_N) %>% 
  #filter(!Final>Raw) %>% 
  mutate(rm_eff = (Raw-Final)/Raw)

deuba_P_month<- deuba_P %>% 
  ungroup() %>% 
  group_by(STP, year, month) %>% 
  summarise(Raw_month = mean(Raw, na.rm = T),
            Final_month = mean(Final, na.rm = T)) %>% 
  mutate(rm_eff = (Raw_month-Final_month)/Raw_month)

deuba_P_year<-deuba_P_month %>% 
  ungroup() %>% 
  group_by(STP, year) %>% 
  summarise(Raw_year = mean(Raw_month, na.rm = T),
            Final_year = mean(Final_month, na.rm = T)) %>% 
  mutate(rm_eff = (Raw_year-Final_year)/Raw_year)

deuba_P_rm<-deuba_P_year %>% 
  group_by(STP) %>% 
  summarise(Raw = mean(Raw_year, na.rm = T),
            Final = mean(Final_year, na.rm = T)) %>% 
  mutate(rm_eff = (Raw-Final)/Raw,
         type = "P")
```
# ACS

```{r}
acs<-read.csv(here("raw_data/Sewage_plants/ACS_Effluent.csv"), na.string = "N/A") %>% 
  mutate(Date = as.Date(Date, tryFormat = "%d/%m/%Y"),
         year = lubridate::year(Date), 
         month = lubridate::month(Date), 
         day = lubridate::day(Date),
         year = ifelse(year == 15, 2015,
                       ifelse(year == 16, 2016,
                              ifelse(year == 17, 2017,
                                     ifelse(year == 18, 2018,
                                            ifelse(year == 19, 2019,
                                                   ifelse(year ==20, 2020,
                                                          ifelse(year == 2001, 2015,as.numeric(year)))))))),
         Location = as.character(Location)) %>% 
  filter(year <2020,
         grepl('Raw|Final', Location)) %>% 
  mutate_if(is.character, str_trim) %>% 
  filter(!Location == "Raw Effluent") %>% 
  mutate(Total.Nitrogen = as.numeric(as.character(Total.Nitrogen))) %>% 
  mutate(Total.Reactive.Phosphates = as.numeric(as.character(Total.Reactive.Phosphates)))
```


```{r}
acs_N<-acs %>% 
  dplyr::select(STP, Date, year, month, day,Location, Total.Nitrogen) %>% 
  mutate(Location =ifelse(Location == "Raw Sewage", "Raw", "Final")) %>% 
  group_by(STP, Date, year, month, day, Location) %>% 
  summarise(Avg_N = mean(Total.Nitrogen, na.rm = T)) %>% 
  pivot_wider(., names_from = Location, values_from = Avg_N) %>% 
 # filter(!Final>Raw) %>% 
  mutate(rm_eff = (Raw-Final)/Raw)

acs_N_month<- acs_N %>% 
  ungroup() %>% 
  group_by(STP, year, month) %>% 
  summarise(Raw_month = mean(Raw, na.rm = T),
            Final_month = mean(Final, na.rm = T)) %>% 
  mutate(rm_eff = (Raw_month-Final_month)/Raw_month)

acs_N_year<-acs_N_month %>% 
  ungroup() %>% 
  group_by(STP, year) %>% 
  summarise(Raw_year = mean(Raw_month, na.rm = T),
            Final_year = mean(Final_month, na.rm = T)) %>% 
  mutate(rm_eff = (Raw_year-Final_year)/Raw_year)

acs_N_rm<-acs_N_year %>% 
  group_by(STP) %>% 
  summarise(Raw = mean(Raw_year, na.rm = T),
            Final = mean(Final_year, na.rm = T)) %>% 
  mutate(rm_eff = (Raw-Final)/Raw,
         type = "N")
```
```{r}
acs_P<-acs %>% 
  dplyr::select(STP, Date, year, month, day,Location, Total.Reactive.Phosphates) %>% 
  mutate(Location = ifelse(Location %in% c("Final Effluent 1","Final Effluent -2","Final Effluent [1]","Final Effluent [2]"), "Final Effluent", as.character(Location)),
         Location =ifelse(Location == "Raw Sewage", "Raw", "Final")) %>% 
  group_by(STP, Date, year, month, day, Location) %>% 
  summarise(Avg_N = mean(Total.Reactive.Phosphates, na.rm = T)) %>% 
  pivot_wider(., names_from = Location, values_from = Avg_N) %>% 
  #filter(!Final>Raw) %>% 
  mutate(rm_eff = (Raw-Final)/Raw)

acs_P_month<- acs_P %>% 
  ungroup() %>% 
  group_by(STP, year, month) %>% 
  summarise(Raw_month = mean(Raw, na.rm = T),
            Final_month = mean(Final, na.rm = T)) %>% 
  mutate(rm_eff = (Raw_month-Final_month)/Raw_month)

acs_P_year<-acs_P_month %>% 
  ungroup() %>% 
  group_by(STP, year) %>% 
  summarise(Raw_year = mean(Raw_month, na.rm = T),
            Final_year = mean(Final_month, na.rm = T))  %>% 
  mutate(rm_eff = (Raw_year-Final_year)/Raw_year)

acs_P_rm<-acs_P_year %>% 
  group_by(STP) %>% 
  summarise(Raw = mean(Raw_year, na.rm = T),
            Final = mean(Final_year, na.rm = T)) %>% 
  mutate(rm_eff = (Raw-Final)/Raw,
         type = "P")
```

# Combine

```{r}
all<-rbind(kinoya_N_rm,
           kinoya_P_rm,
           ba_N_rm,
           ba_P_rm,
           lautoka_N_rm,
           lautoka_P_rm,
           naboro_N_rm,
           naboro_P_rm,
           nadali_N_rm,
           nadali_P_rm,
           namara_N_rm,
           namara_P_rm,
           navakai_N_rm,
           navakai_P_rm,
           olosara_N_rm,
           olosara_P_rm,
           wailada_N_rm,
           wailada_P_rm,
           deuba_N_rm,
           deuba_P_rm,
           acs_N_rm,
           acs_P_rm)
```

```{r}
all_year<-rbind(kinoya_N_year,
           kinoya_P_year,
           ba_N_year,
           ba_P_year,
           lautoka_N_year,
           lautoka_P_year,
           naboro_N_year,
           naboro_P_year,
           nadali_N_year,
           nadali_P_year,
           namara_N_year,
           namara_P_year,
           navakai_N_year,
           navakai_P_year,
           olosara_N_year,
           olosara_P_year,
           wailada_N_year,
           wailada_P_year,
           deuba_N_year,
           deuba_P_year,
           acs_N_year,
           acs_P_year)

all_year2<-all_year %>% 
  group_by(STP) %>% 
  summarise(avg_raw_year = mean(Raw_year),
            avg_final_year = mean(Final_year),
            avg_rm_eff = mean(rm_eff))
```

```{r}
write.csv(all, here("output_data/Sewage_plants/Nutrient_removal_STP_allvalues.csv"))
```