---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(lubridate)
library(stringr)
library(here)
```

This code calculates the average N and P removal from each sewage treatment plant in Fiji based on data from Fiji Water Authority.
Advice from WAF is to remove values where the Final effluent > Raw values.However, we kept them as it is common for systems to overload.

# Flow data 

Flow data is in ML = million litres

```{r}
wwtp_flow<-read.csv(here("raw_data/Sewage_plants/WWTP_flow_data.csv")) %>% 
  filter(!WWTP == "") %>% 
  pivot_longer(cols = X2010:X2019, names_to = "year", values_to = "flow_ML") %>% 
  mutate(flow_ML = as.numeric(flow_ML),
         year = as.numeric(str_remove(year, "X"))) %>% 
  mutate(flow_L = flow_ML*1000000) %>% 
  filter(year>=2015) %>% 
  mutate(WWTP2 = ifelse(WWTP == "Votua", "Ba",
                        ifelse(WWTP == "Natabua", "Lautoka",
                               WWTP)))
```

# Loop to calculate nutrients

```{r}
stp_files<-list.files(here("raw_data/Sewage_plants/"), pattern = "Effluent", full.names = T)

stp_files<-stp_files[-c(1,6,11)]
```

WWTP values are in mg/L. Convert to tonnes by multiplying by flow rate and multiplying by 1e-9

```{r}

all<-c()
all_year<-c()
all_samples<-c()

for(i in 1:length(stp_files)){
  stp<-read.csv(stp_files[[i]])
  name<-unique(stp$STP)
  
  print(name)
  
  if(name =="Lautoka"){
     stp<- stp %>% 
      mutate(Date = as.Date(Date, tryFormat = "%d/%m/%Y"),
         year = lubridate::year(Date), 
         month = lubridate::month(Date), 
         day = lubridate::day(Date),
         Location = as.character(Location)) %>% 
  filter(year <2020,
         grepl('Raw|Maturation', Location)) %>% 
  mutate_if(is.character, str_trim) %>% 
  mutate(Location = ifelse(Location %in% c("Maturation Pond [2]", "Maturation Pond 2","Maturation Pond"," Maturation Pond [2","Maturation 2", "Maturation", "Maturation [Final Effluent]", " Maturation Pond"), "Final Effluent", as.character(Location))) %>% 
  mutate(Total.Reactive.Phosphates = as.numeric(as.character(Total.Reactive.Phosphates))) %>% 
      filter(Location %in% c("Raw Sewage", "Raw Sewerage", "Final Effluent"))
  }else if(name %in% c("Namara", "Olosara", "Ba")){
    stp<- stp %>% 
      mutate(Date = as.Date(Date, tryFormat = "%d/%m/%Y"),
         year = lubridate::year(Date), 
         month = lubridate::month(Date), 
         day = lubridate::day(Date),
         year = ifelse(year == 15, 2015,
                       ifelse(year == 16, 2016,
                              ifelse(year == 17, 2017,
                                     ifelse(year == 18, 2018,
                                            ifelse(year == 19, 2019,
                                                   ifelse(year ==20, 2020,NA)))))),
         Location = as.character(Location)) %>% 
  filter(year <2020,
         grepl('Raw|Maturation', Location)) %>% 
  mutate_if(is.character, str_trim) %>% 
  mutate(Location = ifelse(Location %in% c("Maturation Pond [2]", "Maturation Pond 2","Maturation Pond"," Maturation Pond [2","Maturation 2", "Maturation", "Maturation [Final Effluent]", " Maturation Pond"), "Final Effluent", as.character(Location))) %>% 
  mutate(Total.Reactive.Phosphates = as.numeric(as.character(Total.Reactive.Phosphates))) %>% 
      filter(Location %in% c("Raw Sewage", "Raw Sewerage", "Final Effluent"))
    }else if(name == "Deuba"){
     stp<-stp %>% 
     mutate(Date = as.Date(Date, tryFormat = "%d/%m/%Y"),
         year = lubridate::year(Date), 
         month = lubridate::month(Date), 
         day = lubridate::day(Date),
         Location = as.character(Location),
         Location = ifelse(Location == "Secondary Clarifier Effluent", "Final Effluent", as.character(Location))) %>% 
  filter(year <2020,
         grepl('Raw|Final|Decant', Location)) %>% 
  mutate_if(is.character, str_trim) %>% 
  mutate(Total.Reactive.Phosphates = as.numeric(as.character(Total.Reactive.Phosphates)))
    
     }else{
       stp<-stp %>% 
     mutate(Date = as.Date(Date, tryFormat = "%d/%m/%Y"),
         year = lubridate::year(Date), 
         month = lubridate::month(Date), 
         day = lubridate::day(Date),
         year = ifelse(year == 15, 2015,
                       ifelse(year == 16, 2016,
                              ifelse(year == 17, 2017,
                                     ifelse(year == 18, 2018,
                                            ifelse(year == 19, 2019,
                                                   ifelse(year ==20, 2020,NA)))))),
         Location = as.character(Location),
         Location = ifelse(Location == "Secondary Clarifier Effluent", "Final Effluent", as.character(Location))) %>% 
  filter(year <2020,
         grepl('Raw|Final|Decant', Location)) %>% 
  mutate_if(is.character, str_trim) %>% 
  mutate(Total.Reactive.Phosphates = as.numeric(as.character(Total.Reactive.Phosphates)))
  }
  
  stp_flow<-wwtp_flow %>% 
  filter(WWTP2 == name)

  stp_N<-stp %>% 
  dplyr::select(STP, Date, year, month, day,Location, Total.Nitrogen) %>% 
  mutate(Total.Nitrogen = ifelse(Total.Nitrogen == "N/A", NA, as.numeric(Total.Nitrogen)),
         Location =ifelse(Location %in% c("Raw Sewage", "Raw Sewerage"), "Raw", "Final")) %>% 
  group_by(STP, Date, year, month, day, Location) %>% 
  summarise(Avg_N = mean(Total.Nitrogen, na.rm = T)) %>% 
  pivot_wider(., names_from = Location, values_from = Avg_N) %>% 
  mutate(Final2 = ifelse(Final>Raw, Raw, Final)) %>% #Deal with values when Final>Raw
  full_join(., stp_flow, by = "year") %>% 
  mutate(Final_mg = Final2 * flow_L,
         Raw_mg = Raw * flow_L,
         Final_tonnes = Final_mg * 1e-9,
         Raw_tonnes = Raw_mg * 1e-9,
         remov_eff = (Raw_tonnes-Final_tonnes)/Raw_tonnes) 
  
  stp_N<-stp_N %>% 
      filter(!is.na(Raw) == T,
         !is.na(Final) == T) # Remove pairs that don't have both values

stp_N_month<- stp_N %>% 
  ungroup() %>% 
  group_by(STP, year, month) %>% 
  summarise(Raw_month = mean(Raw_tonnes, na.rm = T),
            Final_month = mean(Final_tonnes, na.rm = T)) %>% 
  mutate(rm_eff = (Raw_month-Final_month)/Raw_month)

samples_N<-stp_N %>% 
  filter(!is.na(Raw_tonnes) == T) %>% 
   group_by(STP, year) %>% 
  summarise(n_samples = length(unique(Date))) %>% 
     mutate(type = "N")

stp_N_year<-stp_N_month %>% 
  ungroup() %>% 
  group_by(STP, year) %>% 
  summarise(Raw_year = mean(Raw_month, na.rm = T),
            Final_year = mean(Final_month, na.rm = T)) %>% 
  mutate(rm_eff = (Raw_year-Final_year)/Raw_year)

stp_N_rm<-stp_N_year %>% 
  group_by(STP) %>% 
  summarise(Raw = mean(Raw_year, na.rm = T),
            Final = mean(Final_year, na.rm = T)) %>% 
  mutate(rm_eff = (Raw-Final)/Raw,
         type = "N")

 stp_P<-stp %>% 
  dplyr::select(STP, Date, year, month, day,Location, Total.Reactive.Phosphates) %>% 
  mutate(Location = ifelse(Location %in% c("Final Effluent 1","Final Effluent -2","Final Effluent [1]","Final Effluent [2]"), "Final Effluent", as.character(Location)),
         Location =ifelse(Location %in% c("Raw Sewage", "Raw Sewerage"), "Raw", "Final")) %>% 
  group_by(STP, Date, year, month, day, Location) %>% 
  summarise(Avg_N = mean(Total.Reactive.Phosphates, na.rm = T)) %>% 
  pivot_wider(., names_from = Location, values_from = Avg_N) %>% 
 # filter(!Final>Raw) %>% 
 mutate(Final2 = ifelse(Final>Raw, Raw, Final)) %>% #Deal with values when Final>Raw
  full_join(., stp_flow, by = "year") %>% 
  mutate(Final_mg = Final2 * flow_L,
         Raw_mg = Raw * flow_L,
         Final_tonnes = Final_mg * 1e-9,
         Raw_tonnes = Raw_mg * 1e-9,
         remov_eff = (Raw_tonnes-Final_tonnes)/Raw_tonnes) 
 
   stp_P<-stp_P %>% 
      filter(!is.na(Raw) == T,
         !is.na(Final) == T) # Remove pairs that don't have both values
   
   samples_P<-stp_P %>% 
  filter(!is.na(Raw_tonnes) == T) %>% 
   group_by(STP, year) %>% 
  summarise(n_samples = length(unique(Date))) %>% 
     mutate(type = "P")

all_samples<-rbind(all_samples, samples_N) %>% 
  rbind(., samples_P)
 
stp_P_month<- stp_P %>% 
  ungroup() %>% 
  group_by(STP, year, month) %>% 
  summarise(Raw_month = mean(Raw, na.rm = T),
            Final_month = mean(Final, na.rm = T)) %>% 
  mutate(rm_eff = (Raw_month-Final_month)/Raw_month)

stp_P_year<-stp_P_month %>% 
  ungroup() %>% 
  group_by(STP, year) %>% 
  summarise(Raw_year = mean(Raw_month, na.rm = T),
            Final_year = mean(Final_month, na.rm = T)) %>% 
  mutate(rm_eff = (Raw_year-Final_year)/Raw_year)

stp_P_rm<-stp_P_year %>% 
  group_by(STP) %>% 
  summarise(Raw = mean(Raw_year, na.rm = T),
            Final = mean(Final_year, na.rm = T)) %>% 
  mutate(rm_eff = (Raw-Final)/Raw,
         type = "P")

all<-rbind(all, stp_N_rm) %>% 
  rbind(., stp_P_rm)

all_year<-rbind(all_year, stp_N_year) %>% 
  rbind(., stp_P_year)
}
```

```{r}
all_year2<-all_year %>% 
  group_by(STP) %>% 
  summarise(avg_raw_year = mean(Raw_year),
            avg_final_year = mean(Final_year),
            avg_rm_eff = mean(rm_eff))

all_samples2 <-all_samples %>% 
  group_by(STP, type) %>% 
  summarise(total_samples = sum(n_samples, na.rm = T))

write.csv(all, here("output_data/Sewage_plants/Nutrient_removal_STP_allvalues.csv"))

```


