---
title: "Untitled"
author: "Caitie"
date: "24/09/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(sf)
library(here)
library(gdalUtils)
library(tabularaster)
library(units)
library(rgdal)
library(lwgeom)
library(pbmcapply)
library(fasterize)
#devtools::install_github("rspatial/raster")
library(raster)

t_crs<-"+proj=aea +lat_1=-9 +lat_2=-26 +lat_0=-17 +lon_0=180 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs"
```

# Basins

```{r}
fiji_basins12<-st_read(here("projected_data/Basins/Fiji_basins12.shp")) %>% 
  group_by(MAIN_BAS) %>% 
  summarise(area_km2 = sum(area_km2, na.rm = T))

fiji_basins12<-fiji_basins12 %>% 
  mutate(ID = seq(from = 1, to =nrow(fiji_basins12), 1)) %>% 
  st_transform(., crs = t_crs)
```

# Fiji Coast

```{r}
coast<-fiji_basins12 %>% 
  mutate(ID = as.numeric(1)) %>% 
  group_by(ID) %>% 
  summarise(area_km2 = sum(area_km2, na.rm = T))

st_write(coast, here("output_data/Coast/Basin_coast.shp"), delete_layer = T)
```

# N and P pollution

These values are without any nutrient removal

```{r}
N_cell_septic<-raster(here("output_data/Nutrients/Septic_N.tif"))

P_cell_septic<-raster(here("output_data/Nutrients/Septic_P.tif"))

N_cell_direct<-raster(here("output_data/Nutrients/Direct_N.tif"))

P_cell_direct<-raster(here("output_data/Nutrients/Direct_P.tif"))

```


# Create buffers

Think of whether I've made these buffers correct....

Another option?
https://gis.stackexchange.com/questions/327788/addressing-just-the-outermost-cells-in-a-raster

```{r}
#buff<-seq(from = -10, to = -50, by = -10) %>% as.list()
buff<-seq(from = -5, to = -55, by = -10) %>% as.list()

create_buff<-function(x){

# buffer size, here 10 units of shpA coordinates inward
# (better if projected coordinate system)
buffer_size <- x

# compute buffered polygons
shpA_buffered <- st_buffer(coast, buffer_size) 

# remove degenerate polygons
shpA_remaining <- shpA_buffered[!st_is_empty(shpA_buffered),]

diff<-st_difference(coast, shpA_remaining)

diff_ras<-fasterize(diff, N_cell_direct)

st_write(diff, paste0("/home/kuempel/Fiji_sewage/output_data/Coast/buffers/buffer_coast_",x,".shp"), delete_layer = T)

writeRaster(diff_ras, paste0("/home/kuempel/Fiji_sewage/output_data/Coast/buffers/buffer_coast_",x,".tif"), overwrite = T)

}
```

```{r}
pbmclapply(buff, create_buff, mc.cores = 5, mc.style = "ETA")
```


```{r}
#library(tmap)

#test<-st_read(here("output_data/Coast/buffers/buffer_coast_-100.shp"))

#test2<-st_read(here("output_data/Coast/buffers/buffer_coast_-20.shp"))

#tmap_mode("view")

#tm_shape(test2) +
#  tm_polygons() 
```

```{r}
buff2<-seq(from = -100, to = -500, by = -100) %>% as.list()


pbmclapply(buff2, create_buff, mc.cores = 5, mc.style = "ETA")
```

# Clear memory
```{r}
gc()
```

# Change buffer area to N/P values

```{r}
buffer_list<-list.files(path = here("output_data/Coast/buffers"), pattern = ".tif$", full.names = T)

river_list<-list.files(path = here("output_data/Rivers/buffers"), pattern = ".tif$", full.names = T)

buffer_N_P<-function(x){
  
  #buffer_shp<-st_read(x)
  
  # Read in raster
  buffer_ras<-raster(x)
  
  # Get buffer size
  num<-as.numeric(regmatches(x, gregexpr("[[:digit:]]+", x)))
  
  # Search value for river raster
  num_search<-paste0(num, ".tif")
  
  # Load river raster
  river_ras<-raster(river_list[grep(pattern = num_search, x = river_list)])
  
  # Change NAs to 0 in river raster
  river_ras2<-river_ras
  river_ras2[is.na(river_ras2) == T]<- 0
  
  # Add together coast and river raster to find overlaps to avoid double counting
  coast_only<-buffer_ras + river_ras2
  
  # If value ==2 then we know there is overlap so we remove that cell so we do not double count population. 
  coast_only2<-coast_only
  coast_only2[coast_only2 == 2]<-NA

  
  # Subset septic values to only coastal cells (excluding river overlap)
  N<-N_ras * coast_only2
  P<-P_ras * coast_only2
  
  #basin_N<-raster::extract(N_ras, buffer_basin, fun=sum, na.rm=TRUE, df=TRUE)
  #basin_P<-raster::extract(P_ras, buffer_basin, fun=sum, na.rm=TRUE, df=TRUE)
  
  basin_N<-raster::extract(N, fiji_basins12, fun=sum, na.rm=TRUE, df=TRUE)
  basin_P<-raster::extract(P, fiji_basins12, fun=sum, na.rm=TRUE, df=TRUE)
  

  #basins_nutri_df<-full_join(basin_N, fiji_basins12, by = "ID") %>% 
  #  rename(N = Septic_N) %>% 
  #  full_join(., basin_P, by = "ID") %>% 
  #  rename(P = Septic_P) %>% 
  #  dplyr::select(ID, N, P, MAIN_BAS)
  
   basins_nutri_df<-full_join(basin_N, fiji_basins12, by = "ID") %>% 
    rename(N = layer) %>% 
    full_join(., basin_P, by = "ID") %>% 
    rename(P = layer) %>% 
    dplyr::select(ID, N, P, MAIN_BAS)
  
  
  write.csv(basins_nutri_df, paste0("/home/kuempel/Fiji_sewage/output_data/Nutrients/buffers/Coast_N_P_", name,"_per_basin_",num,"_buff.csv"))
  
  writeRaster(N, paste0("/home/kuempel/Fiji_sewage/output_data/Nutrients/buffers/Coast_N_", name,"_per_basin_",num,"_buff.tif"), overwrite = T)
  
  writeRaster(P, paste0("/home/kuempel/Fiji_sewage/output_data/Nutrients/buffers/Coast_P_", name,"_per_basin_",num,"_buff.tif"), overwrite = T)

  }

```

```{r}
N_ras<-N_cell_septic
P_ras<-P_cell_septic
name<-"septic"

pbmclapply(buffer_list, buffer_N_P, mc.cores = 10, mc.style = "ETA")
```


```{r}
N_ras<-N_cell_direct
P_ras<-P_cell_direct
name<-"direct"

pbmclapply(buffer_list, buffer_N_P, mc.cores = 2, mc.style = "ETA")
```

# Calculate N and P for different buffer distances and leaching rates

Treatment rate of 0.1 means that 10% of nutrients is removed through treatment

Leach rate of 0.1 means that 10% of nutrients leaches (90% lost), a value of 90% would be 10% of nutrients is lost through leaching
```{r}
N_P_buffers<-list.files(here("output_data/Nutrients/buffers"), pattern = "Coast", full.names = T)

sub_N_P_buffers<-N_P_buffers[grep(pattern = ".csv", N_P_buffers)]

sub_N_P_buffers_septic<-sub_N_P_buffers[grep(pattern = "septic", sub_N_P_buffers)]

leach<-seq(0.1,1,by = 0.1)
treatment<-seq(0.1,1, by = 0.1)
df2<-c()
df3<-c()

for(i in 1:length(sub_N_P_buffers_septic)){
  name<-sub_N_P_buffers_septic[i]
  buff<-parse_number(name)
  c<-read.csv(sub_N_P_buffers_septic[i])
  n<-sum(c$N, na.rm = T)
  p<-sum(c$P, na.rm = T)
  
  for(z in 1:length(treatment)){
    rm(df)
    print(treatment[z])
    n_treat<-n*(1-treatment[z])
    p_treat<-p*(1-treatment[z])
    
    for(k in 1:length(leach)){
    
    n_leach<-n_treat*leach[k]
    p_leach<-p_treat*leach[k]
    
    df<-data.frame(buffer = buff, treatment_rate = treatment[z], N = n, P = p, N_treat = n_treat, P_treat = p_treat, leach_rate = leach[k], N_leach = n_leach, P_leach = p_leach)
    
    df2<-rbind(df2, df)
    
    }
    
    df3<-rbind(df3,df2)
    
  }
  
  
}

df3<-df3 %>% 
  mutate(type = "septic")

```

```{r}
sub_N_P_buffers_direct<-sub_N_P_buffers[grep(pattern = "direct", sub_N_P_buffers)]

df4<-c()
df5<-c()

for(i in 1:length(sub_N_P_buffers_direct)){
  name<-sub_N_P_buffers_direct[i]
  buff<-parse_number(name)
  c<-read.csv(sub_N_P_buffers_direct[i])
  n<-sum(c$N, na.rm = T)
  p<-sum(c$P, na.rm = T)
  
  for(z in 1:length(treatment)){
    rm(df)
    print(treatment[z])
    n_treat<-n*(1-treatment[z])
    p_treat<-p*(1-treatment[z])
  
  for(k in 1:length(leach)){
    rm(df)
    print(leach[k])
    n_leach<-n*leach[k]
    p_leach<-p*leach[k]
    
    df<-data.frame(buffer = buff, treatment_rate = treatment[z], N= n, P = p, N_treat = n_treat, P_treat = p_treat, leach_rate = leach[k], N_leach = n_leach, P_leach = p_leach)
    
    df4<-rbind(df4, df)
  }
     df5<-rbind(df5,df4)
  }
}

df5<- df5 %>% 
  mutate(type = "direct")

```

```{r}

write.csv(df3, here("output_data/Sensitivity/Coastal_septic_treatment_leach_buffer_analysis.csv"))

write.csv(df5, here("output_data/Sensitivity/Coastal_direct_treatment_leach_buffer_analysis.csv"))
```

