---
title: "Untitled"
author: "Caitie"
date: "25/09/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(sf)
library(here)
library(raster)
library(gdalUtils)
library(tabularaster)
library(rgdal)
library(countrycode)
```

In this code we estimate the contribution of tourists to sewage pollution in Fiji.

# Visitor Arrivals by country 2018

Data is from Fiji's Bureau of Statistics: https://www.statsfiji.gov.fj/index.php/statistics/tourism-and-migration-statistics/visitor-arrivals-statistics

Potentially use a different year?

```{r}
visit_arrivals<-read_csv(here("raw_data/Tourism/Fiji_Visitor_Arrivals_by_Country.csv")) %>% 
  dplyr::select(-X5, -X6, -X7, -X8, -X9, -X10, -X11) %>% 
  filter(!Country == "Total") %>% 
  group_by(Country) %>% 
  summarise(Total_vistors = sum(Visitor_arrivals, na.rm = T)) %>% 
  mutate(Country = ifelse(Country == "Korea", "South Korea", as.character(Country)))

```

# Visitors from each country by region

```{r}
visitors_region<-read_csv(here("raw_data/Tourism/Fiji_tourists_by_region.csv"))

prop_visitors_region<- visitors_region %>% 
  group_by(Country) %>% 
  summarise(Total_visitors = sum(Num_visitors, na.rm = T)) %>% 
  left_join(., visitors_region, by = "Country") %>% 
  mutate(prop_visitors = Num_visitors/Total_visitors)
```

# Rooms and beds occupied in each region

Data source: https://fhta.com.fj/wp-content/uploads/2019/01/Qtr.-3-2018.pdf

```{r}
beds_sold<-read_csv(here("raw_data/Tourism/Fiji_room_bed_sold_by_region.csv")) %>% 
  group_by(Area) %>% 
  summarise(Total_beds_sold = sum(Beds_sold, na.rm = T),
            Total_rooms_sold = sum(Rooms_sold, na.rm = T)) %>% 
  mutate(Prop_beds_sold = Total_beds_sold/sum(Total_beds_sold, na.rm = T),
         Prop_rooms_sold= Total_rooms_sold/sum(Total_rooms_sold, na.rm = T))
```

# Protein supply by country

```{r}
protein_supply<-read_csv(here("raw_data/Protein_supply/protein-supply-by-region.csv")) %>% 
  filter(Year == 2013) %>% 
  rename(Protein_g_capita_day = `Food Balance Sheets: Grand Total - Protein supply quantity (g/capita/day) (FAO (2017)) (g/capita/day)`)
```

```{r}
plant_protein_supply<-read_csv(here("raw_data/Protein_supply/FAOSTAT_vegetable_protein_consumption.csv")) %>% 
  filter(Year == 2013,
         Item == "Vegetal Products") %>% 
  dplyr::select(Country, Year, Item, Value) %>% #unit is g/capita/day
  mutate(Code = countrycode(Country, "country.name", "iso3c")) %>%
  rename(plant_protein = Value)
```

```{r}
protein_supply<-full_join(protein_supply, plant_protein_supply, by = c("Code", "Year"))
```

# Join Visitors and protein supply

Visitor data has groups of countries-for this we take the mean protein for the group of countries

```{r}
# Countries by continent

continent<-read_csv(here("raw_data/Tourism/Countries_by_continent.csv"))

# Taiwan included in rest of Asia

# Countries in "Rest_of_Asia" = 
# Countries in "Continental Europe" = 
# Countries in "Pacific Islands" =
# Countries in "Others" = 

#> unique(visit_arrivals$Country)
# [1] "Australia"       "Canada"          "China"           "Europe"          "Hong Kong"       "India"           "Japan"           "South Korea"    
# [9] "New Zealand"     "Others"          "Pacific_Islands" "Rest_of_Asia"    "United Kingdom"  "United States"  

rest_of_asia<-continent %>% 
  filter(Continent == "Asia",
         !ISO3 %in% c("CHN", "HKG", "IND", "JPN", "KOR"))

cont_europe<-continent %>% 
  filter(Continent == "Europe",
         !ISO3 %in% c("ALA", "ISL", "IRL", "GGY", "IMN", "MLT", "GBR", "FRO", "SJM", "HRV", "GIB", "JEY"),
         !is.na(ISO3) == T)
  
pi<-continent %>% 
  filter(Continent == "Oceania",
         !ISO3 %in% c("NZL", "AUS", "FJI"),
         !Region1 == "Australia and New Zealand")

  
# For now we do not include Others with accounts for 4974 or 0.5% of visitors
```


```{r}
rest_of_asia_protein<-left_join(rest_of_asia, protein_supply, by = c("ISO3" = "Code")) %>% 
  summarise(Protein_g_capita_day = mean(Protein_g_capita_day, na.rm = T),
            Plant_protein = mean(plant_protein, na.rm = T))

cont_europe_protein<-left_join(cont_europe, protein_supply, by = c("ISO3" = "Code")) %>% 
  summarise(Protein_g_capita_day = mean(Protein_g_capita_day, na.rm = T),
            Plant_protein = mean(plant_protein, na.rm = T))

pi_protein<-left_join(pi, protein_supply, by = c("ISO3" = "Code")) %>% 
  summarise(Protein_g_capita_day = mean(Protein_g_capita_day, na.rm = T),
            Plant_protein = mean(plant_protein, na.rm = T))


```


# Calculate Nutrients from visitors

```{r}
avg_stay = 11.4 #days - reference is from https://pic.or.jp/ja/wp-content/uploads/2019/07/2018-Annual-Visitor-Arrivals-ReportF.pdf


visitor_nutrients<-visit_arrivals %>% 
  filter(!Country == "Others") %>% 
  left_join(., protein_supply, by = c("Country" = "Entity")) %>% 
  mutate(Protein_g_capita_day = as.numeric(Protein_g_capita_day),
         Protein_g_capita_day = ifelse(Country == "Rest_of_Asia", as.numeric(round(rest_of_asia_protein$Protein_g_capita_day,2)),
                                       ifelse(Country == "Europe", as.numeric(round(cont_europe_protein$Protein_g_capita_day,2)),
                                              ifelse(Country == "Pacific_Islands", as.numeric(round(pi_protein$Protein_g_capita_day,2)),
                                                     ifelse(Country == "Hong Kong", 129.18, as.numeric(Protein_g_capita_day))))),
         Plant_protein = as.numeric(plant_protein),
         Plant_protein= ifelse(Country == "Rest_of_Asia", as.numeric(round(rest_of_asia_protein$Plant_protein,2)),
                                       ifelse(Country == "Europe", as.numeric(round(cont_europe_protein$Plant_protein,2)),
                                              ifelse(Country == "Pacific_Islands", as.numeric(round(pi_protein$Plant_protein,2)),
                                                     ifelse(Country == "Hong Kong", 34.77, as.numeric(Plant_protein))))),
         Protein_N_intake = Protein_g_capita_day * 0.13,
         #Protein_P_intake = Protein_g_capita_day *(1/6),
         #N_excretion_human = Protein_N_intake * (0.8+0.17),
         P_excretion_human = 0.011 * (Protein_g_capita_day + Plant_protein), 
         N_emissions_human = Protein_N_intake * avg_stay/1000, #kg/person/year
         P_emissions_human = P_excretion_human* avg_stay/1000,#kg/person/year
         N_emissions_visitors = N_emissions_human * Total_vistors, #kg/country tourists total/year
         P_emissions_visitors = P_emissions_human * Total_vistors) 

```


# Join to visitor by region data

```{r}
visitor_nutrients_region<-visitor_nutrients %>% 
  mutate(Country2 = ifelse(Country == "Europe", "Cont. Europe",
                           ifelse(Country == "United States", "USA",
                           ifelse(Country %in% c("Hong Kong", "India", "Japan", "South Korea", "Rest_of_Asia", "Pacific_Islands", "United Kingdom", "China"), "Others", as.character(Country))))) %>% 
  left_join(., prop_visitors_region, by = c("Country2" = "Country")) %>% 
  mutate(N_visitors_region = N_emissions_visitors * prop_visitors,
         P_visitors_region = P_emissions_visitors * prop_visitors)
```

# Surface water transport

Determine what watersheds each STP is in

```{r}
stp_shp<-readOGR("/home/kuempel/Waste_water_data/Fiji/Sewage_plants/Fiji Wastewater Treatment plants.kml") %>% 
  st_as_sf()

stp_shp<-st_transform(stp_shp, "+proj=tmerc +lat_0=-17 +lon_0=178.75 +k=0.9998548 +x_0=2000000 +y_0=4000000 +ellps=WGS72 +towgs84=35.1728,-136.5713,36.9643,-1.371019,0.841969,4.718006,1.53700236005 +units=m +no_defs ")

basins12<-st_read(here("projected_data/Basins/Fiji_basins12.shp"))

```



# Spatial distribute connections

We assume that resorts in Mamanuca are not connected to municipal STP (islands) so we do not include them.
Northern Division = Labasa STP
Suva = Kinoya STP
Nadi = Navakai Nadi STP
Lautoka = Natabua Lautoka STP
Coral Coast = Olosara Sigatoka and Pacific Harbor STP (stretch of coastline between Sigatoka and Suva, on the island of Viti Levu, in Fiji.)
Others = Votua Ba STP and Nadali Nausori???

```{r}
stp<-read_csv("/home/kuempel/Waste_water_data/Fiji/Sewage_plants/Fiji_Sewer_Treatment_Plants.csv") %>% 
  filter(!Plant_Name %in% c("ACS", "Wailada", "Naboro"))%>% 
  mutate(Tikina = ifelse(Plant_Name == "Olosara", "Nasigatoka",
                         ifelse(Plant_Name == "Natabua", "Vuda", 
                                ifelse(Tikina == "Nausori", "Naitasiri", 
                                       ifelse(Tikina == "Nasinu", "Naitasiri", 
                                              ifelse(Tikina == "Pacific Harbor", "Serua", as.character(Tikina)))))),
         Area = ifelse(Tikina == "Vuda", "Lautoka",
                       ifelse(Tikina %in% c("Nasigatoka", "Serua"), "Coral Coast",
                              ifelse(Tikina == "Labasa", "Northern Division",
                                     ifelse(Tikina %in% c("Ba", "Naitasiri"), "Others", as.character(Tikina))))))

```

From IAS 2004 it is estimated that 26.7% of surveyed resorts were connected to municipal STP. We use that figure here.

```{r}
prop_con = 0.267

visitor_nutrients_stp<-visitor_nutrients_region %>% 
  filter(!Area == "Mamanuca") %>% 
  mutate(N_visitors_connected = N_visitors_region * prop_con,
         P_visitors_connected = P_visitors_region * prop_con) %>% 
  dplyr::select(Country, Area, Total_visitors, N_visitors_connected, P_visitors_connected) %>% 
  left_join(., stp, by = "Area") %>% 
  mutate(Prop_non_res2= ifelse(Tikina == "Ba" & Area == "Others", 1,
                               ifelse(is.na(Prop_non_res) == T & Area == "Others",1 - 0.08695652,
                                      ifelse(Area == "Coral Coast", 0.5,
                                             ifelse(Area %in% c("Nadi", "Lautoka", "Northern Division"),1,as.numeric(Prop_non_res))))),
         Total_N_stp = N_visitors_connected * Prop_non_res2,
         Total_P_stp = P_visitors_connected * Prop_non_res2) %>% 
  group_by(Plant_Name) %>% 
  summarise(Total_N = sum(Total_N_stp, na.rm = T),
            Total_P = sum(Total_P_stp, na.rm = T))


```

```{r}
write.csv(visitor_nutrients_stp, here("output_data/Sewage_plants/Connected_tourist_nutrients.csv"))
```




# Determine connections????

https://www.tourismfiji.com/fiji-map-resorts.html

There were a total of 870,309 visitors to Fiji in 2018 from this data. This is nearly the same as the reported population of Fiji (reported as 883,483 in 2017).

Fiji liquid wastewater management strategy:

~15 large (>100 rooms) and 25 medium sized resorts (30-100 rooms)
Smaller resorts/backpacker accomodations usually have septic tanks (~65 such facilities)

Greenpeace 1997:
66% of resorts carry out primary treatment of effluent
7% had secondary treatment

IAS 2004
40% of resorts have on-site sewage treatment plants
40% had septic tanks
20% connected to sewer system


50% of resorts had primary treatment
23% secondary treatment

50% test effluent quality

26.7% of resorts connected?



