---
title: "Untitled"
author: "Caitie"
date: "16/09/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(sf)
#library(startR)
library(here)
library(raster)
library(gdalUtils)
library(tabularaster)
library(units)
library(rgdal)
library(lwgeom)
```

# Population raster

```{r}
pop_ras_proj<-raster(here("projected_data/Population/population_fji_proj.tif"))
```

# Calculate N and P from human population

N emission (kg/person/year) are estimated based on dietary per capita protein consumption from FAO

```{r}
Protein_intake<- 73.6 #FAO protein supply g/capita/day 
plant_protein_intake<-42.23 # FAO 2013 Protein Supply Vegetable products g/capita/day
```

The human N emissions (kg/person/year) are thus

```{r}
N_excretion_human<- Protein_intake*0.13

#g/person/day assuming 13% nitrogen content of protein- This estimate is slightly lower than using the GDP_ppp estimate. Value from Wang et al. 2019 and Jönsson H., Richert Stintzing A., Vinnerås B. & Salomon E. Guidelines on use of urine and faeces in crop production (Stockholm Environment Institute, SE-103 14 Stockholm, Sweden, 2004).

N_emissions_human<- 0.365*N_excretion_human #kg/person/year
```

```{r}
P_excretion_human<- 0.011 * (Protein_intake + plant_protein_intake) 

# units are total protein in urine and feces g/person/day - Equation from Mihelic et al. 2011 https://reader.elsevier.com/reader/sd/pii/S0045653511001925?token=37B898436A78191398F270991D46AED05EF0C364F3BF68D80B1FFC4C1C334575343378A0F7DAD55F258716F0EDDB1D42

P_emissions_human<-0.365*P_excretion_human #kg/person/year
```

# N and P emissions per grid cell

```{r}
N_cell<-pop_ras_proj * N_emissions_human #kg/year/cell
P_cell<-pop_ras_proj * P_emissions_human #kg/year/cell
```

```{r}
writeRaster(N_cell, here("output_data/Nutrients/Fiji_N_per_cell.tif"),overwrite = T)
writeRaster(P_cell, here("output_data/Nutrients/Fiji_P_per_cell.tif"), overwrite = T)
```


If there was no sewage treatment - we estimate the N and P emissions are thus

```{r}
N_notreatment<-cellStats(N_cell, sum)
P_notreatment<-cellStats(P_cell, sum)
```


# Wastewater treatment

But there is wastewater treatment

Sewage treatment plant catchment shapefile

```{r}
stp<-st_read(here("raw_data/Sewage_plants/Fiji Waste Water Catchment.shp")) %>% 
  mutate(STP = ifelse(TREATMENT_ == "NATABUA WWTP", "Natabua WWTP",
                      ifelse(TREATMENT_ == "Navakai PS", "Navakai WWTP", as.character(TREATMENT_)))) %>% 
  mutate(area = st_area(.)) %>% 
  group_by(STP) %>% 
  summarise(area = sum(area, na.rm = T)) %>% 
  filter(!is.na(STP) == T) 

  
stp<-stp %>% 
  mutate(stp_pop = extract(pop_ras_proj, ., fun = sum, na.rm = T),
         ID = 1:nrow(stp))
```


Sewage treatment plant catchment raster

```{r}
stp_ras<-raster(here("output_data/Sewage_plants/stp_raster.tif"))
```

Sewage treatment plant nutrient removal rates

```{r}
nutri_removal<-read.csv(here("raw_data/Sewage_plants/Nutrient_removal_STP.csv")) %>% 
  mutate(ID = ifelse(STP == "ACS", 1,
                     ifelse(STP == "Deuba", 2,
                            ifelse(STP == "Kinoya", 3,
                                   ifelse(STP == "Naboro", 4,
                                          ifelse(STP == "Nadali", 5,
                                                 ifelse(STP ==  "Namara", 6,
                                                        ifelse(STP == "Lautoka", 7,
                                                               ifelse(STP ==  "Navakai", 8,
                                                                      ifelse(STP == "Olosara", 9,
                                                                             ifelse(STP == "Ba", 10,
                                                                                    ifelse(STP == "Wailada", 11, NA))))))))))))

N_removal<-nutri_removal %>% 
  filter(type == "N")

P_removal<-nutri_removal %>% 
  filter(type == "P")
```

Make sewage treatment into a raster

This takes awhile - avoid if possible

```{r}
#N_stp_removal<-subs(stp_ras, N_removal, by= "ID", which="rm_eff")
#P_stp_removal<-subs(stp_ras, P_removal, by= "ID", which="rm_eff")
```

```{r}
#writeRaster(N_stp_removal, here("output_data/Sewage_plants/N_stp_removal.tif"))
#writeRaster(P_stp_removal, here("output_data/Sewage_plants/P_stp_removal.tif"))
```

```{r}
N_stp_removal<-raster(here("output_data/Sewage_plants/N_stp_removal.tif"), overwrite = T)
P_stp_removal<-raster(here("output_data/Sewage_plants/P_stp_removal.tif"), overwrite = T)
```


Account for treatment

```{r}
test<-N_stp_removal
test[is.na(test) == T]<-1

N_rm_stp<-N_cell * N_stp_removal

P_rm_stp<-P_cell * P_stp_removal

N_rm_all<- N_cell * test
  
P_rm_all<- P_cell * test
```

```{r}
writeRaster(N_rm_stp, here("output_data/Sewage_plants/N_total_stp_rm.tif"), overwrite = T)
writeRaster(P_rm_stp, here("output_data/Sewage_plants/P_total_stp_rm.tif"), overwrite = T)
writeRaster(N_rm_all, here("output_data/Sewage_plants/N_total_stp_rm_all.tif"), overwrite = T)
writeRaster(P_rm_all, here("output_data/Sewage_plants/P_total_stp_rm_all.tif"), overwrite = T)
```


# Nutrients at each STP

```{r}
stp<- stp %>% 
  mutate(N = extract(N_rm_stp, stp, fun = sum, na.rm = T),
         P = extract(P_rm_stp, stp, fun = sum, na.rm = T))
```
Current nutrients based on removal efficiency
```{r}
sum(stp$N) * 0.001 #Tonnes/year
sum(stp$P) * 0.001 #Tonnes/year
```

Nutrients if no treatment occurred
```{r}
stp<- stp %>% 
  mutate(N_notreatment = extract(N_cell, stp, fun = sum, na.rm = T),
         P_notreatment = extract(P_cell, stp, fun = sum, na.rm = T))

st_write(stp, here("output_data/Sewage_plants/Nutrients_at_STP.shp"))
```

