---
title: "GSR_Survey_data"
author: "Caitie"
date: "30/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(here)
library(raster)
library(sp)
library(sf)
library(rgeos)

t_crs<-"+proj=aea +lat_1=-9 +lat_2=-26 +lat_0=-17 +lon_0=180 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs"

```

Surveys conducted in 2019 across 71 sites

# Fish biomass at each site

Sum by site and transect then take mean (might be some sites that don't have the same # of transects)

```{r}
fish<-read.csv(here("raw_data/GSR_surveys/beltfish-Great_Sea_Reef_2019-20201130.csv")) %>% 
  group_by(Site, Transect.number, Functional.group) %>% 
  summarise(total_biomass_kgha = sum(Biomass_kgha, na.rm = T),
            total_count = sum(Count,na.rm = T)) %>% 
  group_by(Site, Functional.group) %>% 
  summarise(avg_biomass_kgha = mean(total_biomass_kgha, na.rm = T),
            avg_count = mean(total_count, na.rm = T))

write.csv(fish, here("output_data/GSR_Surveys/Fish_biomass_count.csv"))
```


# Benthic at each site

Point intersect transect
3 x 50 meter transects with a point every .5 meter (100 points per transect)

Aggregate by transect and by site
Count frequency of hard corals

By growth form for hard corals

If interesting - loop in Fiji team for publication


"We derived twelve categories of coral communities based on benthic surveys, including total cover of scleractinian corals, total cover of branching scleractinian corals, total cover of foliose scleractinian corals, genera richness, turf algae, macroalgae, and rubble. Different coral cover metrics were estimated as the average percent of living hard coral or with a specific growth form at each site, and genera richness was estimated as the average number of coral genera on replicate transects."

1. Macroalgae
2. Turf algae
3. General richness
4. Crustose coralline algae
5. Rubble
6. Soft coral

```{r}
benthic<-read.csv(here("raw_data/GSR_surveys/benthicpit-Great_Sea_Reef_2019-20201130.csv"))

perc_cover<-benthic %>% 
  mutate(frequency = 1) %>% 
  group_by(Site, Transect.number, Benthic.category) %>% 
  summarise(Freq = sum(frequency, na.rm = T)) %>% 
  mutate(prop_cover = Freq/100)

avg_perc_cover<-perc_cover %>% 
  group_by(Site, Benthic.category) %>% 
  summarise(avg_prop_cover = mean(prop_cover, na.rm = T))

write.csv(avg_perc_cover, here("output_data/GSR_Surveys/Avg_percent_benthic_cover.csv"))
```

# Distance from shore at each site

```{r}
sites<-read.csv(here("raw_data/GSR_surveys/sites.csv"))

xy<-sites %>% 
  dplyr::select(Longitude, Latitude) %>% 
  rename(Y = Latitude, 
         X= Longitude) 

spdf <- SpatialPointsDataFrame(coords = xy, data = sites,
                               proj4string = CRS("+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0")) %>% 
  spTransform(., t_crs)

fiji<-st_read(here("projected_data/Tikina/fji_proj.shp")) %>% 
  st_transform(., t_crs)

fiji<-as(fiji, "Spatial") 

# Distance in meters
distance_shore<-apply(gDistance(spdf, fiji,byid=TRUE),2,min)

dist_shp<-as(spdf, "sf") %>% 
  cbind(distance_shore)
```


# Distance from STP at each site

```{r}
stp<-st_read(here("output_data/Sewage_plants/Nutrients_at_STP.shp")) %>% 
  st_transform(., t_crs)

stp<-as(stp, "Spatial") 

# Distance in meters
distance_stp<-apply(gDistance(spdf, stp,byid=TRUE),2,min)

dist_shp<-dist_shp%>% 
  cbind(distance_stp)
```

# Nutrients at each site

```{r}
unconn_N<-raster(here("output_data/Nutrients/Fiji_unconnected_N_plumes.tif"))
conn_N<-raster(here("output_data/Nutrients/Fiji_connected_N_plumes.tif"))

unconn_site<-extract(unconn_N, spdf, na.rm = T)
  
conn_site<-extract(conn_N, spdf, na.rm = T)

nutri<-cbind(unconn_site, conn_site)

all_vars<-dist_shp %>% 
  cbind(nutri) %>% 
  mutate(unconn_site = ifelse(is.na(unconn_site) == T, 0, as.numeric(unconn_site)),
         conn_site = ifelse(is.na(conn_site) == T, 0, as.numeric(conn_site)))
```


# Bathymetry at each site

```{r}
south_bath<-raster(here("raw_data/Allen_Coral_Atlas/gsr_south_bathymetry.tif")) %>% 
  projectRaster(., crs = t_crs)

writeRaster(south_bath,here("projected_data/Allen_Coral_Atlas/gsr_south_pathymetry_proj.tif"))

south_bath_sites<-extract(south_bath, spdf)
```

# All data

```{r}
all_vars<-full_join(all_vars, fish, by = c("Name" = "Site")) %>% 
  full_join(., avg_perc_cover, by = c("Name" = "Site")) %>% 
  mutate(Total_N = unconn_site + conn_site) %>% 
  rename(fish_biomass_kgha = avg_biomass_kgha,
         fish_count = avg_count) %>% 
  as.data.frame() %>% 
  dplyr::select(-geometry) 

write.csv(all_vars, here("output_data/GSR_Surveys/GSR_variables.csv"))
```

