---
title: "Untitled"
author: "Caitie"
date: "04/03/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(raster)
library(here)
library(sf)

t_crs<-"+proj=aea +lat_1=-9 +lat_2=-26 +lat_0=-17 +lon_0=180 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs"
```


# Nutrients by treatment types

Nutrients without treatment

```{r}
n_fiji<-raster(here("output_data/Nutrients/Fiji_N_per_cell.tif"))
p_fiji<-raster(here("output_data/Nutrients/Fiji_P_per_cell.tif"))
```

```{r}
fiji_n<-cellStats(n_fiji, sum, na.rm = T) * 0.001
fiji_p<-cellStats(p_fiji, sum , na.rm = T) * 0.001

fiji_n
fiji_p
```


## Connected

```{r}
nutri_connected<-st_read(here("output_data/Sewage_plants/Nutrients_at_STP.shp"))
```

The below values are in kg/year
```{r}

# Total N and P human emissions
connected_n<-sum(nutri_connected$N) * 0.001
connected_p<-sum(nutri_connected$P) * 0.001

connected_n
connected_p


```

```{r}
# N and P after WWTP treatment
connected_n_treat<-sum(nutri_connected$N_final) * 0.001
connected_p_treat<-sum(nutri_connected$P_final) * 0.001

connected_n_treat
connected_p_treat

```

```{r}
# Percent of N and P emissions released into environment
sum(nutri_connected$N_final)/sum(nutri_connected$N)
sum(nutri_connected$P_final)/sum(nutri_connected$P)


sum(nutri_connected$P_final)/sum(nutri_connected$N_final)
```

Correlation between Fiji Water Authoriy estimates and our estimates

```{r}
nutri_removal<-read.csv(here("raw_data/Sewage_plants/Nutrient_removal_STP.csv")) %>% 
  mutate(ID = ifelse(STP == "ACS", NA,
                     ifelse(STP == "Deuba", 1,
                            ifelse(STP == "Kinoya", 2,
                                   ifelse(STP == "Naboro", NA,
                                          ifelse(STP == "Nadali", 3,
                                                 ifelse(STP ==  "Namara", 4,
                                                        ifelse(STP == "Lautoka", 5,
                                                               ifelse(STP ==  "Navakai", 6,
                                                                      ifelse(STP == "Olosara", 7,
                                                                             ifelse(STP == "Ba", 8,
                                                                                    ifelse(STP == "Wailada", NA, NA))))))))))),
         nutri_left = (1-rm_eff)) %>% 
  filter(!STP == "ACS",
         !STP == "Naboro") 

N_removal<-nutri_removal %>% 
  filter(type == "N",
        !is.na(ID) == T) %>% 
  rename(N_left = nutri_left) %>% 
  dplyr::select(STP, ID, Raw, Final)%>% 
  rename(N_raw = Raw,
         N_eff_actual = Final)

P_removal<-nutri_removal %>% 
  filter(type == "P",
         !is.na(ID) == T) %>% 
  rename(P_left = nutri_left) %>% 
  dplyr::select(STP, ID, Raw, Final) %>% 
  rename(P_raw = Raw,
         P_eff_actual = Final)
  
```

```{r}
wwtp_compare<-full_join(nutri_connected, N_removal, by = c("ID", "STP")) %>% 
  full_join(., P_removal)
```

```{r}
cor.test(wwtp_compare$N_final, wwtp_compare$N_eff_actual, method = "pearson")
cor.test(wwtp_compare$P_final, wwtp_compare$P_eff_actual, method = "pearson")
```

## Septic

```{r}
test<-st_read(here("output_data/Nutrients_at_pourpoints/All_nutrients_at_pourpoints.shp"))

test_septic<-test %>% 
  filter(type == "Septic")

sum(test_septic$N) * 0.001
```


```{r}
N_cell_septic<-raster(here("output_data/Nutrients/Septic_N.tif"))

P_cell_septic<-raster(here("output_data/Nutrients/Septic_P.tif"))

```

Coastal septic/direct

```{r}
coastal_septic<-st_read(here("output_data/Nutrients_at_pourpoints/Coastal_septic_pourpoints.shp"))

coastal_direct<-st_read(here("output_data/Nutrients_at_pourpoints/Coastal_direct_pourpoints.shp"))
```

This is the amount of N/P through septic systems assuming 10% nutrient removal in tonnes/year

```{r}
septic_n<-cellStats(N_cell_septic, sum, na.rm = T) * 0.001
septic_p<-cellStats(P_cell_septic, sum , na.rm = T) * 0.001
```

# final amount in environment

This is the amount that makes it into surface waters considering a 50 m lateral travel distance and 10% leaching from rivers and coasts

```{r}
septic_leach<-st_read(here("output_data/Nutrients_at_pourpoints/Fiji_septic_pourpoints.shp"))

septic_leach_n<-sum(septic_leach$N_leach) * 0.001
septic_leach_p<-sum(septic_leach$P_leach) * 0.001
```

```{r}
coast_septic_n<-sum(coastal_septic$septic_N*0.1)* 0.001
coast_septic_p<-sum(coastal_septic$septic_P*0.1)* 0.001
```

```{r}
total_septic_n<-septic_leach_n + coast_septic_n

total_septic_p<-septic_leach_p + coast_septic_p

total_septic_n
total_septic_p
```

```{r}
(total_septic_n)/(cellStats(N_cell_septic, sum, na.rm = T) * 0.001)
(total_septic_p)/(cellStats(P_cell_septic, sum , na.rm = T) * 0.001)

```

## Direct

```{r}
N_cell_direct<-raster(here("output_data/Nutrients/Direct_N.tif"))

P_cell_direct<-raster(here("output_data/Nutrients/Direct_P.tif"))
```


```{r}
cellStats(N_cell_direct, sum, na.rm = T) * 0.001
cellStats(P_cell_direct, sum , na.rm = T) * 0.001
```

```{r}
nutri_direct<-read.csv(here("output_data/Nutrients/buffers/N_P_direct_per_basin_50_buff.csv"))

direct_n_surface<-sum(nutri_direct$N,na.rm = T) * 0.1 * 0.001
direct_p_surface<-sum(nutri_direct$P,na.rm = T) * 0.1 * 0.001


```

```{r}
coastal_direct<-st_read(here("output_data/Nutrients_at_pourpoints/Coastal_direct_pourpoints.shp")) 

coastal_direct_n<-sum(coastal_direct$direct_N)*0.1*0.001
coastal_direct_p<-sum(coastal_direct$direct_P)*0.1*0.001
```

```{r}
total_direct_n<-direct_n_surface+coastal_direct_n
total_direct_p<-direct_p_surface+coastal_direct_p

total_direct_n
total_direct_p
```

```{r}
(total_direct_n)/(cellStats(N_cell_direct, sum, na.rm = T) * 0.001)
(total_direct_p)/(cellStats(P_cell_direct, sum , na.rm = T) * 0.001)
```

# Residential nutrients

Total residential nutrients at pourpoints

```{r}
total_n_surface<-connected_n_treat+total_septic_n + total_direct_n

total_p_surface<-connected_p_treat+total_septic_p + total_direct_p

total_n_surface
total_p_surface
```

```{r}
connected_n_treat/total_n_surface
connected_p_treat/total_p_surface
```

```{r}
(coast_septic_n+coastal_direct_n)/(total_septic_n+total_direct_n)

(coast_septic_p+coastal_direct_p)/(total_septic_p+total_direct_p)
```

# Max septic/direct with buffers

```{r}
coastal_buff<-read.csv(here("output_data/Sensitivity/Coastal_leaching_buffer_sensitivity.csv"))

river_buff<-read.csv(here("output_data/Sensitivity/Leaching_buffer_sensitivity.csv"))
```

Max septic
```{r}
coast_max<-coastal_buff %>% 
  filter(leach_rate == 1.0,
         buffer == 500)

river_max<-river_buff %>% 
  filter(leach_rate == 1.0,
         buffer == 500)

all<-full_join(coast_max, river_max)
```

```{r}
septic_max<-all %>% 
  filter(type == "septic")

sum(septic_max$N)*0.001
sum(septic_max$P)*0.001
```

```{r}
direct_max<-all %>% 
  filter(type == "direct")

sum(direct_max$N)*0.001
sum(direct_max$P)*0.001
```
