---
title: "Untitled"
author: "Caitie"
date: "16/09/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(sf)
#library(startR)
library(here)
library(raster)
library(gdalUtils)
library(tabularaster)
library(units)
library(rgdal)
library(lwgeom)

source(here("scripts/plume_functions.R"))

t_crs<-"+proj=aea +lat_1=-9 +lat_2=-26 +lat_0=-17 +lon_0=180 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs"
```

# Population raster

```{r}
pop_ras_proj<-raster(here("projected_data/Population/population_fji_albers.tif"))
```

# Calculate N and P from human population

N emission (kg/person/year) are estimated based on dietary per capita protein consumption from FAO

```{r}
Protein_intake<- 73.6 #FAO protein supply g/capita/day 
plant_protein_intake<-42.23 # FAO 2013 Protein Supply Vegetable products g/capita/day
```

The human N emissions (kg/person/year) are thus

```{r}
N_excretion_human<- Protein_intake*0.13

#g/person/day assuming 13% nitrogen content of protein- This estimate is slightly lower than using the GDP_ppp estimate. Value from Wang et al. 2019 and Jönsson H., Richert Stintzing A., Vinnerås B. & Salomon E. Guidelines on use of urine and faeces in crop production (Stockholm Environment Institute, SE-103 14 Stockholm, Sweden, 2004).

N_emissions_human<- 0.365*N_excretion_human #kg/person/year
```

```{r}
P_excretion_human<- 0.011 * (Protein_intake + plant_protein_intake) 

# units are total protein in urine and feces g/person/day - Equation from Mihelic et al. 2011 https://reader.elsevier.com/reader/sd/pii/S0045653511001925?token=37B898436A78191398F270991D46AED05EF0C364F3BF68D80B1FFC4C1C334575343378A0F7DAD55F258716F0EDDB1D42

P_emissions_human<-0.365*P_excretion_human #kg/person/year
```

# N and P emissions per grid cell

```{r}
N_cell<-pop_ras_proj * N_emissions_human #kg/year/cell
P_cell<-pop_ras_proj * P_emissions_human #kg/year/cell
```

```{r}
writeRaster(N_cell, here("output_data/Nutrients/Fiji_N_per_cell.tif"),overwrite = T)
writeRaster(P_cell, here("output_data/Nutrients/Fiji_P_per_cell.tif"), overwrite = T)
```

```{r}
N_cell<-raster(here("output_data/Nutrients/Fiji_N_per_cell.tif"))
P_cell<-raster(here("output_data/Nutrients/Fiji_P_per_cell.tif"))
```



If there was no sewage treatment - we estimate the N and P emissions are thus

```{r}
#N_notreatment<-cellStats(N_cell, sum)
#P_notreatment<-cellStats(P_cell, sum)
```


# Connected populations

But there is wastewater treatment

Sewage treatment plant catchment shapefile

```{r}
stp<-st_read(here("raw_data/Sewage_plants/Fiji Waste Water Catchment.shp")) %>% 
  mutate(STP = ifelse(TREATMENT_ == "NATABUA WWTP", "Natabua WWTP",
                      ifelse(TREATMENT_ == "Navakai PS", "Navakai WWTP", as.character(TREATMENT_)))) %>% 
  mutate(area = st_area(.)) %>% 
  group_by(STP) %>% 
  summarise(area = sum(area, na.rm = T)) %>% 
  filter(!is.na(STP) == T,
         !STP %in% c("ACS WWTP", "Naboro WWTP", "Wailada WWTP")) 

  
stp<-stp %>% 
  mutate(stp_pop = extract(pop_ras_proj, ., fun = sum, na.rm = T),
         ID = 1:nrow(stp))
```


Sewage treatment plant catchment raster

```{r}
stp_ras<-raster(here("output_data/Sewage_plants/stp_raster_residential.tif"))
```

Sewage treatment plant nutrient removal rates

```{r}
nutri_removal<-read.csv(here("raw_data/Sewage_plants/Nutrient_removal_STP.csv")) %>% 
  mutate(ID = ifelse(STP == "ACS", NA,
                     ifelse(STP == "Deuba", 1,
                            ifelse(STP == "Kinoya", 2,
                                   ifelse(STP == "Naboro", NA,
                                          ifelse(STP == "Nadali", 3,
                                                 ifelse(STP ==  "Namara", 4,
                                                        ifelse(STP == "Lautoka", 5,
                                                               ifelse(STP ==  "Navakai", 6,
                                                                      ifelse(STP == "Olosara", 7,
                                                                             ifelse(STP == "Ba", 8,
                                                                                    ifelse(STP == "Wailada", NA, NA))))))))))),
         nutri_left = (1-rm_eff))

N_removal<-nutri_removal %>% 
  filter(type == "N",
        !is.na(ID) == T)

P_removal<-nutri_removal %>% 
  filter(type == "P",
         !is.na(ID) == T)
```

Make sewage treatment into a raster

This takes awhile - avoid if possible

```{r}
N_stp_removal<-subs(stp_ras, N_removal, by= "ID", which="nutri_left")
P_stp_removal<-subs(stp_ras, P_removal, by= "ID", which="nutri_left")
```

```{r}
writeRaster(N_stp_removal, here("output_data/Sewage_plants/N_stp_removal.tif"), overwrite = T)
writeRaster(P_stp_removal, here("output_data/Sewage_plants/P_stp_removal.tif"), overwrite = T)
```

```{r}
N_stp_removal<-raster(here("output_data/Sewage_plants/N_stp_removal.tif"), overwrite = T)
P_stp_removal<-raster(here("output_data/Sewage_plants/P_stp_removal.tif"), overwrite = T)
```


Account for treatment

```{r}
test<-N_stp_removal
test[is.na(test) == T]<-1
test[test<1]<-0

test2<-P_stp_removal
test2[is.na(test2) == T]<-1
test2[test2<1]<-0

N_connected<-N_cell * N_stp_removal

P_connected<-P_cell * P_stp_removal

N_unconnected<- N_cell * test
  
P_unconnected<- P_cell * test2
```

```{r}
writeRaster(N_connected, here("output_data/Nutrients/N_connected.tif"), overwrite = T)
writeRaster(P_connected, here("output_data/Nutrients/P_connected.tif"), overwrite = T)
writeRaster(N_unconnected, here("output_data/Nutrients/N_unconnected.tif"), overwrite = T)
writeRaster(P_unconnected, here("output_data/Nutrients/P_unconnected.tif"), overwrite = T)
```


# Nutrients at each STP

```{r}
stp<- stp %>% 
  mutate(N = extract(N_connected, stp, fun = sum, na.rm = T),
         P = extract(P_connected, stp, fun = sum, na.rm = T))
```
Current nutrients based on removal efficiency
```{r}
sum(stp$N) * 0.001 #Tonnes/year
sum(stp$P) * 0.001 #Tonnes/year
```

```{r}
st_write(stp, here("output_data/Sewage_plants/Nutrients_at_STP.shp"), append = F)
```

# Unconnected

# River data

```{r}
rivers<-st_read(here("raw_data/Rivers/Fiji_RiverATLAS.shp"))

rivers_proj<-st_transform(rivers, st_crs(stp)) %>% st_zm()

st_write(rivers_proj, here("projected_data/Rivers/Fiji_rivers.shp"), append = F)
```

```{r}
buffer_rivers<-st_buffer(rivers_proj, dist = 500) %>% 
  mutate(ID = 1)
```

# Remove STP area

```{r}
#diff_buffer<-st_difference(buffer_rivers, st_union(stp))

#st_write(diff_buffer, here("output_data/Rivers/River_buffer_stprm.shp"), append = F)
```

# Septic population
```{r}
septic<-raster(here("output_data/Population/Septic_population.tif"))

septic[septic>0]<-1
```

```{r}
direct<-raster(here("output_data/Population/Direct_population.tif"))

direct[direct>0]<-1
```

```{r}
septic_N<-N_unconnected * septic
septic_P<-P_unconnected * septic

septic_N_rm<-septic_N * 0.9 # Assume 10% removal efficiency from Wang et al. primary treatment
septic_P_rm<-septic_P * 0.9 # Assume 10% removal efficiency from Wang et al. primary treatment

direct_N<-N_unconnected * direct
direct_P<-P_unconnected * direct
```

```{r}
writeRaster(septic_N_rm,here("output_data/Nutrients/Septic_N.tif"),overwrite = T)
writeRaster(septic_P_rm,here("output_data/Nutrients/Septic_P.tif"),overwrite = T)
writeRaster(direct_N,here("output_data/Nutrients/Direct_N.tif"),overwrite = T)
writeRaster(direct_P,here("output_data/Nutrients/Direct_P.tif"),overwrite = T)
```

# Rasterize buffer

```{r}
buffer_rivers<-st_cast(buffer_rivers, "POLYGON")
buffer_ras<-fasterize::fasterize(buffer_rivers, N_unconnected)

writeRaster(buffer_ras, here("output_data/Nutrients/buffer_rivers.tif"),overwrite = T)

buffer_ras<-raster(here("output_data/Rivers/buffer_rivers.tif"))
```


# Change Buffer area to N and P pollution values

```{r}
direct_N_buff<-direct_N * buffer_ras

direct_P_buff<-direct_P * buffer_ras

septic_N_buff<- septic_N_rm * buffer_ras

septic_P_buff<- septic_P_rm * buffer_ras
```


```{r}
#cellStats(direct_N, stat = sum, na.rm = T) #1695542 kg/year
#cellStats(direct_N_buff, stat = sum, na.rm = T) #738091.8 kg/year

#cellStats(septic_N, stat = sum, na.rm = T) #1525970 kg/year
#cellStats(septic_N_buff, stat = sum, na.rm = T) #649384.4 kg/year
```

# Nutrients within watersheds

Wateshed boundaries

Level 12 basins

Look to see if any of the basins are endorrheic - they are not (column ENDO)
```{r}
# Read in data and calculate area
fiji_basins12<-st_read(here("projected_data/Basins/Fiji_basins12.shp")) %>% 
  group_by(MAIN_BAS) %>% 
  summarise(area_km2 = sum(area_km2, na.rm = T))

fiji_basins12<-fiji_basins12 %>% 
  mutate(ID = seq(from = 1, to =nrow(fiji_basins12), 1))

#fiji_basins_df<-fiji_basins12 %>% 
#  as.data.frame() %>% 
#  dplyr::select(HYBAS_ID, NEXT_DOWN,area_km2, ID, dis_m3_pyr)

```


Sum cells within watersheds

```{r}
septic_basin_N<-raster::extract(septic_N_buff, fiji_basins12, fun=sum, na.rm=TRUE, df=TRUE)
septic_basin_P<-raster::extract(septic_P_buff, fiji_basins12, fun=sum, na.rm=TRUE, df=TRUE)

direct_basin_N<-raster::extract(direct_N_buff, fiji_basins12, fun=sum, na.rm=TRUE, df=TRUE)
direct_basin_P<-raster::extract(direct_P_buff, fiji_basins12, fun=sum, na.rm=TRUE, df=TRUE)
```

```{r}
septic_basins_nutri_df<-full_join(septic_basin_N, fiji_basins12, by = "ID") %>% 
  full_join(., septic_basin_P, by = "ID") %>% 
  rename(N = layer.x,
         P = layer.y) %>% 
  dplyr::select(ID, N, P, MAIN_BAS)

direct_basins_nutri_df<-full_join(direct_basin_N, fiji_basins12, by = "ID") %>% 
  full_join(., direct_basin_P, by = "ID") %>% 
  rename(N = layer.x,
         P = layer.y) %>% 
  dplyr::select(ID, N, P, MAIN_BAS)

```

```{r}
write.csv(septic_basins_nutri_df, here("output_data/Nutrients/N_P_septic_per_basin.csv"))
write.csv(direct_basins_nutri_df, here("output_data/Nutrients/N_P_direct_per_basin.csv"))
```

