---
title: "Fiji_STP_watersheds"
author: "Caitie"
date: "09/09/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)
library(sf)
#library(startR)
library(here)
library(raster)
library(gdalUtils)
library(tabularaster)
library(units)
library(rgdal)
library(lwgeom)
library(fasterize)
library(exactextractr)

t_crs<-"+proj=aea +lat_1=-9 +lat_2=-26 +lat_0=-17 +lon_0=180 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs"
```

# Population density

Source:

https://pacificdata.org/data/dataset/fji_population_grid_2020

Settlement footprint generated by combining 2007 household listing locations and Facebook's High-Resolution Population Density Maps (https://data.humdata.org/dataset/fiji-high-resolution-population-density-maps-demographic-estimates).

Population allocated proportionally using 2017 census population counts at enumeration area level.

Year Population Growth Rate of 0.38% has been applied to update population up to 2020

The human settlement footprint with population allocated has been converted into a 100 m resolution raster.


```{r}
pop_ras<-raster(here("raw_data/Population/fji_population_grid_2020/FJI_Pop_Grid_2020.tif"))
```

```{r}
gdalwarp(srcfile ="/home/kuempel/Fiji_sewage/raw_data/Population/fji_population_grid_2020/FJI_Pop_Grid_2020.tif", dstfile = "/home/kuempel/Fiji_sewage/projected_data/Population/FJI_Pop_Grid_proj.tif", s_srs = "+proj=merc +lon_0=150 +k=1 +x_0=0 +y_0=0 +datum=WGS84 +units=m +no_defs", t_srs = t_crs, r = "bilinear", overwrite = T)
```

```{r}
pop_ras_proj<-raster(here("projected_data/Population/FJI_Pop_Grid_proj.tif"))

pop_ras_proj<-setMinMax(pop_ras_proj)
```


# Connected populations

STP Watershed boundaries

Source - Water Authority Fiji

```{r}
stp<-st_read(here("raw_data/Sewage_plants/Fiji Waste Water Catchment.shp")) %>% 
  st_transform(., crs = t_crs) %>% 
  mutate(STP = ifelse(TREATMENT_ == "NATABUA WWTP", "Natabua WWTP",
                      ifelse(TREATMENT_ == "Navakai PS", "Navakai WWTP", as.character(TREATMENT_)))) %>% 
  mutate(area = st_area(.)) %>% 
  group_by(STP) %>% 
  summarise(area = sum(area, na.rm = T)) %>% 
  filter(!is.na(STP) == T,
         !STP %in% c("ACS WWTP", "Naboro WWTP", "Wailada WWTP"))
  
stp2<-stp %>% 
  mutate(stp_pop = exact_extract(pop_ras_proj, ., fun = "sum"),
         ID = 1:nrow(stp))
```
```{r}
stp_df<-stp2 %>% 
  as.data.frame() %>% 
  dplyr::select(-geometry)

write.csv(stp_df, here("output_data/Sewage_plants/Connected_population_by_STP.csv"))
```

```{r}
stp3<-st_cast(stp2, "MULTIPOLYGON")
stp_ID_ras<-fasterize(stp3, pop_ras_proj, field = "ID")

writeRaster(stp_ID_ras, here("output_data/Sewage_plants/STP_ID_raster.tif"), overwrite = T)
```

# Summarise population within each STP watershed

```{r}
fiji_pop_df<-cellStats(pop_ras_proj, "sum")

pop_df<-rasterToPoints(pop_ras_proj) %>% 
  as.data.frame()

 # Population is 887648
```

```{r}
stp_ras<-mask(pop_ras_proj, stp)

cellStats(stp_ras, "sum")

writeRaster(stp_ras, here("output_data/Population/Connected_population.tif"), overwrite = T)
```

# Prop of population connected

```{r}
conn_pop<-sum(stp2$stp_pop)

prop_pop<-conn_pop/fiji_pop_df

conn_pop
fiji_pop_df
prop_pop

#~16% of population is connected based on these estimates with Felipe's population density layer
#~18.9% of population is connected based on the Facebook population density layer
#17.3% with the facebook layer corrected by Fiji 2017 census

#153242.4
```

# Compare our results to reported results

Source - Table 1 from Fiji national liquid waste management strategy and action plan 2007

```{r}
reported_conn<-read.csv(here("raw_data/Sewage_plants/STP_pop_connected.csv")) %>% 
  mutate(ID = ifelse(STP_name == "Adi_Cakobau School", NA,
                     ifelse(STP_name == "Pacific_Harbour", 1,
                            ifelse(STP_name == "Suva_Kinoya", 2,
                                   ifelse(STP_name == "Naboro Prison", NA,
                                          ifelse(STP_name == "Nausori", 3,
                                                 ifelse(STP_name ==  "Labasa", 4,
                                                        ifelse(STP_name == "Lautoka", 5,
                                                               ifelse(STP_name ==  "Nadi", 6,
                                                                      ifelse(STP_name == "Sigatoka", 7,
                                                                             ifelse(STP_name == "Ba", 8,
                                                                                    ifelse(STP_name == "Wailada", NA, NA))))))))))))

```

Join to estimates

```{r}
pop_check<- stp2 %>% 
  as.data.frame() %>% 
  dplyr::select(-geometry) %>% 
  full_join(., reported_conn, by = "ID") %>% 
  dplyr::select(STP, STP_name, stp_pop, Pop_connected) %>% 
  rename(estimated = stp_pop,
         reported = Pop_connected) %>% 
  mutate(diff = reported - estimated)

write.csv(pop_check,here("output_data/Sewage_plants/STP_population_check.csv"))
```


# Unconnected

Crop STP cathcments from population raster

```{r}
unconnected_ras<-mask(pop_ras_proj, stp, inverse = T)
```

# Septic population

Source: Fiji liquid waste management strategy and action plan 2007

40% of the population uses septic systems

From Jung et al. IUCN habitat classifications paper
https://www.nature.com/articles/s41597-020-00599-8.pdf

```{r}
urban<-raster(here("projected_data/Population/Fiji_urban.tif"))
urban<-projectRaster(urban, crs = t_crs)
#urban[urban>0]<-1
```


```{r}
urban<-resample(urban, pop_ras_proj)
urban_pts<-rasterToPoints(urban)
urban_df<-urban_pts %>% 
  as.data.frame() 
```

```{r}
non_stp<-rasterToPoints(unconnected_ras) %>% 
  as.data.frame() %>% 
  rename(non_stp = FJI_Pop_Grid_proj )

pop_urban<-full_join(pop_df, urban_df, by = c("x", "y")) %>% 
  full_join(., non_stp, by = c("x", "y")) 

pop_urban<- pop_urban %>% 
  mutate(id = 1:nrow(pop_urban))
```

# Septic

```{r}
pop_target<-(fiji_pop_df-conn_pop)/2

pop_target/fiji_pop_df #Should be ~40%

unconnected<-pop_urban %>% 
  filter(!is.na(non_stp) == T,
         is.na(FJI_Pop_Grid_proj) == F) %>% 
  mutate(urban_bin = ifelse(Fiji_urban>0,1,0)) %>% 
  dplyr::arrange(desc(Fiji_urban),
                desc(non_stp)) %>% 
  mutate(cumpop = cumsum(FJI_Pop_Grid_proj)) 

septic<-unconnected %>% 
  filter(cumpop<=pop_target) 

septic2<-septic%>% 
  dplyr::select(x,y,FJI_Pop_Grid_proj)

septic_sp<-st_as_sf(septic2, coords = c("x", "y"), crs = t_crs)

septic_ras<-rasterize(septic_sp, pop_ras_proj, crs = t_crs)

septic_ras_pop<-septic_ras[[2]]

septic_pop<-cellStats(septic_ras_pop, "sum")

writeRaster(septic_ras_pop,here("output_data/Population/Septic_population.tif"), overwrite = T)
```


# Direct

```{r}
direct<-unconnected %>% 
  filter(cumpop>pop_target) %>% 
  dplyr::select(x,y,FJI_Pop_Grid_proj)

direct_sp<-st_as_sf(direct, coords = c("x", "y"), crs = t_crs)

direct_ras<-rasterize(direct_sp, pop_ras_proj, crs = t_crs)

direct_ras_pop<-direct_ras[[2]]

direct_pop<-cellStats(direct_ras_pop, "sum")

writeRaster(direct_ras_pop,here("output_data/Population/Direct_population.tif"),overwrite = T)
```

# Check population

```{r}
conn_pop + septic_pop + direct_pop
```


```{r}
(conn_pop + septic_pop + direct_pop)/fiji_pop_df
```


