---
title: "Fiji_STP_watersheds"
author: "Caitie"
date: "09/09/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)
library(sf)
#library(startR)
library(here)
library(raster)
library(gdalUtils)
library(tabularaster)
library(units)
library(rgdal)
library(lwgeom)

t_crs<-"+proj=aea +lat_1=-9 +lat_2=-26 +lat_0=-17 +lon_0=180 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs"
```

# Fiji

Source- https://data.humdata.org/dataset/fiji-administrative-boundaries/resource/d949f7a8-7ac3-41eb-8aec-0e29af5042f6

```{r}
fiji_tik<-st_read(here("raw_data/Tikina/fji_polbnda_adm3_tikina.shp")) %>% 
  rename(TIKINA = ADM3_NAME,
         PROVINCE = ADM2_NAME,
         TID = FBOS_TID,
         PID = FBOS_PID) %>% 
  summarise()

fiji_proj<-st_transform(fiji_tik, t_crs)

fiji_proj<-st_zm(fiji_proj)

st_write(fiji_proj, here("projected_data/Tikina/fji_proj.shp"), append = F)
```

# Population density

Source: 
https://data.humdata.org/dataset/fiji-high-resolution-population-density-maps-demographic-estimates

30 m (people/30m2) spatial resolution: https://blogs.worldbank.org/opendata/first-look-facebook-s-high-resolution-population-maps

This takes quite a long time - once created load in projected raster only


```{r}
pop_ras_proj<-raster(here("projected_data/Population/population_fji_albers.tif"))

#gdalwarp(srcfile = file.path(here("projected_data/Population/population_fji_proj.tif")), dstfile = #file.path(here("projected_data/Population/population_fji_albers.tif")), t_srs = "+proj=aea +lat_1=-9 +lat_2=-26 +lat_0=-17 +lon_0=180 +x_0=0 +y_0=0 #+ellps=WGS84 +datum=WGS84 +units=m +no_defs", overwrite = T)
```


# Connected populations

STP Watershed boundaries

Source - Water Authority Fiji

```{r}
stp<-st_read(here("raw_data/Sewage_plants/Fiji Waste Water Catchment.shp")) %>% 
  st_transform(., crs = t_crs) %>% 
  mutate(STP = ifelse(TREATMENT_ == "NATABUA WWTP", "Natabua WWTP",
                      ifelse(TREATMENT_ == "Navakai PS", "Navakai WWTP", as.character(TREATMENT_)))) %>% 
  mutate(area = st_area(.)) %>% 
  group_by(STP) %>% 
  summarise(area = sum(area, na.rm = T)) %>% 
  filter(!is.na(STP) == T,
         !STP %in% c("ACS WWTP", "Naboro WWTP", "Wailada WWTP"))
  
stp<-stp %>% 
  mutate(stp_pop = extract(pop_ras_proj, ., fun = sum, na.rm = T),
         ID = 1:nrow(stp))
```

# Summarise population within each STP watershed

```{r}
#fiji_pop_df<-extract(pop_ras_proj, fiji_proj, fun = sum, na.rm = T)

fiji_pop_df<-cellStats(pop_ras_proj, "sum")

pop_df<-rasterToPoints(pop_ras_proj) %>% 
  as.data.frame()

 # Population is 1175078
```

# Prop of population connected

```{r}
conn_pop<-sum(stp$stp_pop)

prop_pop<-conn_pop/fiji_pop_df

conn_pop
fiji_pop_df
prop_pop

#~16% of population is connected based on these estimates with Felipe's population density layer
#~18.9% of population is connected based on the Facebook population density layer

#1198468
```


# Crop STP from population data

```{r}
stp_pop<-crop(pop_ras_proj, stp, snap = "near")
```


# Rasterize STP shapefile

```{r}
stp<-st_cast(stp, "POLYGON")
stp_ras<-fasterize::fasterize(stp, pop_ras_proj, field = "ID")
writeRaster(stp_ras, here("output_data/Sewage_plants/stp_raster_residential.tif"), overwrite = T)
stp_ras<-raster(here("output_data/Sewage_plants/stp_raster_residential.tif"))
```

# Compare our results to reported results

Source - Table 1 from Fiji national liquid waste management strategy and action plan 2007

```{r}
reported_conn<-read.csv(here("raw_data/Sewage_plants/STP_pop_connected.csv")) %>% 
  mutate(ID = ifelse(STP_name == "Adi_Cakobau School", NA,
                     ifelse(STP_name == "Pacific_Harbour", 1,
                            ifelse(STP_name == "Suva_Kinoya", 2,
                                   ifelse(STP_name == "Naboro Prison", NA,
                                          ifelse(STP_name == "Nausori", 3,
                                                 ifelse(STP_name ==  "Labasa", 4,
                                                        ifelse(STP_name == "Lautoka", 5,
                                                               ifelse(STP_name ==  "Nadi", 6,
                                                                      ifelse(STP_name == "Sigatoka", 7,
                                                                             ifelse(STP_name == "Ba", 8,
                                                                                    ifelse(STP_name == "Wailada", NA, NA))))))))))))

```

Join to estimates

```{r}
pop_check<- stp %>% 
  as.data.frame() %>% 
  dplyr::select(-geometry) %>% 
  full_join(., reported_conn, by = "ID") %>% 
  dplyr::select(STP, STP_name, stp_pop, Pop_connected) %>% 
  rename(estimated = stp_pop,
         reported = Pop_connected)

write.csv(here("output_data/Sewage_plants/STP_population_check.csv"))
```

# Septic population

Source: Fiji liquid waste management strategy and action plan 2007

40% of the population uses septic systems

```{r}
urban<-raster(here("projected_data/Population/Fiji_urban.tif"))
urban<-projectRaster(urban, crs = t_crs)
urban[urban>0]<-1
```

```{r}
stp_pop<-stp_ras
stp_pop[stp_pop>0]<-1

stp_df<-rasterToPoints(stp_pop) %>% 
  as.data.frame() %>% 
  rename(stp = layer)

```

```{r}
urban<-resample(urban, pop_ras_proj)
urban_df<-rasterToPoints(urban) %>% 
  as.data.frame() 

#unconn_urban<-urban * non_stp #These are the urban areas NOT covered by STPs
#unconn_urban<-resample(unconn_urban, pop_ras_proj)
```

```{r}
test<-full_join(pop_df, urban_df, by = c("x", "y")) %>% 
  full_join(., stp_df, by = c("x", "y")) 

test<-test %>% 
  mutate(id = 1:nrow(test))
```

```{r}
stp_test<-test %>% 
  filter(!is.na(stp) == T) %>% 
  dplyr::select(x,y,population_fji_albers)

stp_ras_pop<-rasterFromXYZ(stp_test, pop_ras_proj)
crs(stp_ras_pop)<-crs(pop_ras_proj)
#writeRaster(stp_ras_pop,here("output_data/Population/Connected_population.tif"), overwrite = T)
```

stp population is 227461.9
Total population is 1198468

# Septic

```{r}
pop_target<-(fiji_pop_df-sum(stp_test$population_fji_albers,na.rm = T))/2

septic<-test %>% 
  filter(is.na(stp) == T) %>% 
  dplyr::arrange(desc(population_fji_albers),
                 desc(Fiji_urban)) %>% 
  mutate(cumpop = cumsum(population_fji_albers)) %>% 
  filter(cumpop<=pop_target) 

septic2<-septic%>% 
  dplyr::select(x,y,population_fji_albers)

septic_ras<-rasterFromXYZ(septic2, pop_ras_proj)
crs(septic_ras)<-crs(pop_ras_proj)
writeRaster(septic_ras,here("output_data/Population/Septic_population.tif"), overwrite = T)
```
# Direct

```{r}
direct<-test %>% 
  filter(is.na(stp) == T,
         !id %in% septic$id) %>% 
  dplyr::select(x,y, population_fji_albers)

direct_ras<-rasterFromXYZ(direct, pop_ras_proj)
crs(direct_ras)<-crs(pop_ras_proj)
writeRaster(direct_ras,here("output_data/Population/Direct_population.tif"),overwrite = T)
```


