---
title: "Fiji_STP_watersheds"
author: "Caitie"
date: "09/09/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)
library(sf)
#library(startR)
library(here)
library(raster)
library(gdalUtils)
library(tabularaster)
library(units)
library(rgdal)
library(lwgeom)
library(fasterize)

t_crs<-"+proj=aea +lat_1=-9 +lat_2=-26 +lat_0=-17 +lon_0=180 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs"
```

# Fiji

Source- https://data.humdata.org/dataset/fiji-administrative-boundaries/resource/d949f7a8-7ac3-41eb-8aec-0e29af5042f6

```{r}
#fiji_tik<-st_read(here("raw_data/Tikina/fji_polbnda_adm3_tikina.shp")) %>% 
#  rename(TIKINA = ADM3_NAME,
#         PROVINCE = ADM2_NAME,
#         TID = FBOS_TID,
#         PID = FBOS_PID) %>% 
#  summarise()

#fiji_proj<-st_transform(fiji_tik, t_crs)

#fiji_proj<-st_zm(fiji_proj)

#st_write(fiji_proj, here("projected_data/Tikina/fji_proj.shp"), append = F)
```

# Population density

Source: 
https://data.humdata.org/dataset/fiji-high-resolution-population-density-maps-demographic-estimates

30 m (people/30m2) spatial resolution: https://blogs.worldbank.org/opendata/first-look-facebook-s-high-resolution-population-maps

This takes quite a long time - once created load in projected raster only

```{r}
pop_ras_proj<-raster(here("projected_data/Population/population_fji_albers.tif"))

#gdalwarp(srcfile = file.path(here("projected_data/Population/population_fji_proj.tif")), dstfile = #file.path(here("projected_data/Population/population_fji_albers.tif")), t_srs = "+proj=aea +lat_1=-9 +lat_2=-26 +lat_0=-17 +lon_0=180 +x_0=0 +y_0=0 #+ellps=WGS84 +datum=WGS84 +units=m +no_defs", overwrite = T)
```


# Connected populations

STP Watershed boundaries

Source - Water Authority Fiji

```{r}
stp<-st_read(here("raw_data/Sewage_plants/Fiji Waste Water Catchment.shp")) %>% 
  st_transform(., crs = t_crs) %>% 
  mutate(STP = ifelse(TREATMENT_ == "NATABUA WWTP", "Natabua WWTP",
                      ifelse(TREATMENT_ == "Navakai PS", "Navakai WWTP", as.character(TREATMENT_)))) %>% 
  mutate(area = st_area(.)) %>% 
  group_by(STP) %>% 
  summarise(area = sum(area, na.rm = T)) %>% 
  filter(!is.na(STP) == T,
         !STP %in% c("ACS WWTP", "Naboro WWTP", "Wailada WWTP"))
  
stp<-stp %>% 
  mutate(stp_pop = extract(pop_ras_proj, ., fun = sum, na.rm = T),
         ID = 1:nrow(stp))

#test<-extract(pop_ras_proj, stp, cellnumbers = T, weights = T)

#test2<-do.call(rbind.data.frame, test)
#test2<-test2 %>% 
#  filter(!is.na(value) == T,
#         !weight<0.5)
```

```{r}
#stp<-st_cast(stp, "POLYGON")

#stp_ras<-fasterize(stp, pop_ras_proj)

#stp_ras<-rasterize(stp, pop_ras_proj, getCover = T)

#sub_stp<-stp[1:2,]

#test<-rasterize(sub_stp, pop_ras_proj, getCover = T)

#test<-stack(pop_ras_proj, stp_ras)

#stp_df<-as_tibble(stp_ras, cell = T, value = T) %>% 
#  mutate(stp = cellvalue)
#pop_df<-as_tibble(pop_ras_proj, cell = T, value = T) %>% 
#  mutate(pop = cellvalue)

#stp_pop<-full_join(pop_df, stp_df, by = "cellindex")

#test<-stp_pop %>% 
#  filter(!is.na(pop) == T | !is.na(stp) == T) %>% 
#  mutate(stp_pop = ifelse(stp == 999, pop, NA))

#overlay(, r2, fun = function(x, y) {x[x == 999 & y == 1] <- 1; x})

#stp_ras[stp_ras == 1]<-999
```


# Summarise population within each STP watershed

```{r}
#fiji_pop_df<-extract(pop_ras_proj, fiji_proj, fun = sum, na.rm = T)

fiji_pop_df<-cellStats(pop_ras_proj, "sum")

pop_df<-rasterToPoints(pop_ras_proj) %>% 
  as.data.frame()

 # Population is 1175078
```

# Prop of population connected

```{r}
conn_pop<-sum(stp$stp_pop)

prop_pop<-conn_pop/fiji_pop_df

conn_pop
fiji_pop_df
prop_pop

#~16% of population is connected based on these estimates with Felipe's population density layer
#~18.9% of population is connected based on the Facebook population density layer

#1198468
```


# Crop STP from population data

```{r}

#stp_ras <- rasterize(stp, pop_ras_proj, getCover=TRUE)
#writeRaster(stp_ras, here("output_data/Sewage_plants/STP_ras.tif"))

stp_ras<-raster(here("output_data/Sewage_plants/STP_ras.tif"))


stp_ras2<-stp_ras
stp_ras2[stp_ras2<0.5] <- NA

stack_test<-stack(stp_ras2, pop_ras_proj)

res1 <- overlay(stack_test, fun =   
  function(x,y) { 
        ifelse(!is.na(x) == T, y = NA, y) 
  } )
```


# Rasterize STP shapefile

```{r}
stp<-st_cast(stp, "POLYGON")
stp_ras3<-fasterize::fasterize(stp, pop_ras_proj, field = "ID")
writeRaster(stp_ras3, here("output_data/Sewage_plants/stp_raster_residential.tif"), overwrite = T)
stp_ras<-raster(here("output_data/Sewage_plants/stp_raster_residential.tif"))
```

# Compare our results to reported results

Source - Table 1 from Fiji national liquid waste management strategy and action plan 2007

```{r}
reported_conn<-read.csv(here("raw_data/Sewage_plants/STP_pop_connected.csv")) %>% 
  mutate(ID = ifelse(STP_name == "Adi_Cakobau School", NA,
                     ifelse(STP_name == "Pacific_Harbour", 1,
                            ifelse(STP_name == "Suva_Kinoya", 2,
                                   ifelse(STP_name == "Naboro Prison", NA,
                                          ifelse(STP_name == "Nausori", 3,
                                                 ifelse(STP_name ==  "Labasa", 4,
                                                        ifelse(STP_name == "Lautoka", 5,
                                                               ifelse(STP_name ==  "Nadi", 6,
                                                                      ifelse(STP_name == "Sigatoka", 7,
                                                                             ifelse(STP_name == "Ba", 8,
                                                                                    ifelse(STP_name == "Wailada", NA, NA))))))))))))

```

Join to estimates

```{r}
pop_check<- stp %>% 
  as.data.frame() %>% 
  dplyr::select(-geometry) %>% 
  full_join(., reported_conn, by = "ID") %>% 
  dplyr::select(STP, STP_name, stp_pop, Pop_connected) %>% 
  rename(estimated = stp_pop,
         reported = Pop_connected) %>% 
  mutate(diff = reported - estimated)

write.csv(pop_check,here("output_data/Sewage_plants/STP_population_check.csv"))
```


# Septic population

Source: Fiji liquid waste management strategy and action plan 2007

40% of the population uses septic systems

From Jung et al. IUCN habitat classifications paper
https://www.nature.com/articles/s41597-020-00599-8.pdf
```{r}
urban<-raster(here("projected_data/Population/Fiji_urban.tif"))
urban<-projectRaster(urban, crs = t_crs)
#urban[urban>0]<-1
```

```{r}
#stp_pop<-stp_ras
#stp_pop[stp_pop>0]<-1

stp_df<-rasterToPoints(stp_ras) %>% 
  as.data.frame() %>% 
  rename(stp = stp_raster_residential)

```

```{r}
urban<-resample(urban, pop_ras_proj)
urban_pts<-rasterToPoints(urban)
urban_df<-urban_pts %>% 
  as.data.frame() 
```

```{r}
non_stp<-rasterToPoints(res1) %>% 
  as.data.frame() %>% 
  rename(non_stp = layer)

pop_urban<-full_join(pop_df, urban_df, by = c("x", "y")) %>% 
  full_join(., non_stp, by = c("x", "y")) 

pop_urban<- pop_urban %>% 
  mutate(id = 1:nrow(pop_urban))
```


stp population is 227461.9
Total population is 1198468

# Septic


```{r}
pop_target<-(fiji_pop_df-conn_pop)/2

pop_target/fiji_pop_df #Should be ~40%

septic<-pop_urban %>% 
  filter(!is.na(non_stp) == T,
         is.na(population_fji_albers) == F) %>% 
  mutate(urban_bin = ifelse(Fiji_urban>0,1,0)) %>% 
  dplyr::arrange(desc(Fiji_urban),
                desc(non_stp)) %>% 
  mutate(cumpop = cumsum(population_fji_albers)) %>% 
  filter(cumpop<=pop_target) 

septic2<-septic%>% 
  dplyr::select(x,y,population_fji_albers, )

septic_sp<-st_as_sf(septic2, coords = c("x", "y"), crs = t_crs)

septic_ras<-rasterize(septic_sp, pop_ras_proj, crs = t_crs)

writeRaster(septic_ras,here("output_data/Population/Septic_population.tif"), overwrite = T)
```

```{r}
#tmap_mode("view")
## tmap mode set to plotting
#tm_shape(septic_ras) +
#    tm_raster("population_fji_albers", palette = terrain.colors(10)) +
#  tm_shape(fiji_basins12) +
#    tm_borders("white", lwd = .5)
```

# Direct

```{r}
direct<-pop_urban %>% 
  filter(!is.na(non_stp) == T,
         !id %in% septic$id) %>% 
  dplyr::select(x,y, population_fji_albers)

direct_sp<-st_as_sf(direct, coords = c("x", "y"), crs = t_crs)

direct_ras<-rasterize(direct_sp, pop_ras_proj, crs = t_crs)

#direct_ras<-rasterFromXYZ(direct, pop_ras_proj, crs = t_crs)

writeRaster(direct_ras,here("output_data/Population/Direct_population.tif"),overwrite = T)
```


