---
title: "Untitled"
author: "Caitie"
date: "29/09/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(raster)
library(here)

t_crs<-"+proj=aea +lat_1=-9 +lat_2=-26 +lat_0=-17 +lon_0=180 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs"
```

# Population stats

```{r}
pop_ras_proj<-raster(here("projected_data/Population/population_fji_albers.tif"))
fiji_pop_df<-cellStats(pop_ras_proj, "sum")


stp_ras<-raster(here("output_data/Sewage_plants/stp_raster_residential.tif"))

stp<-st_read(here("raw_data/Sewage_plants/Fiji Waste Water Catchment.shp")) %>% 
  st_transform(., crs = t_crs) %>% 
  mutate(STP = ifelse(TREATMENT_ == "NATABUA WWTP", "Natabua WWTP",
                      ifelse(TREATMENT_ == "Navakai PS", "Navakai WWTP", as.character(TREATMENT_)))) %>% 
  mutate(area = st_area(.)) %>% 
  group_by(STP) %>% 
  summarise(area = sum(area, na.rm = T)) %>% 
  filter(!is.na(STP) == T,
         !STP %in% c("ACS WWTP", "Naboro WWTP", "Wailada WWTP"))
  
stp<-stp %>% 
  mutate(stp_pop = extract(pop_ras_proj, ., fun = sum, na.rm = T),
         ID = 1:nrow(stp))
```

```{r}
conn_pop<-sum(stp$stp_pop)

prop_pop<-conn_pop/fiji_pop_df
```


```{r}
pop_check<-read_csv(here("output_data/Sewage_plants/STP_population_check.csv")) %>% 
  filter(!is.na(estimated) == T) %>% 
  mutate(perc_diff = (estimated - reported)/estimated)
```

```{r}
cor.test(pop_check$reported, pop_check$estimated, method = "pearson")
```

```{r}
septic<-raster(here("output_data/Population/Septic_population.tif"))
```

```{r}
septic_pop<-cellStats(septic, stat = "sum", na.rm = T)

septic_pop/fiji_pop_df
```

```{r}
direct<-raster(here("output_data/Population/Direct_population.tif"))
```

```{r}
direct_pop<-cellStats(direct, stat = "sum", na.rm = T)

direct_pop/fiji_pop_df
```

```{r}
(conn_pop + septic_pop + direct_pop)/fiji_pop_df
```
# Nutrients by treatment types

Nutrients without treatment

```{r}
n_fiji<-raster(here("output_data/Nutrients/Fiji_N_per_cell.tif"))
p_fiji<-raster(here("output_data/Nutrients/Fiji_P_per_cell.tif"))
```

```{r}
fiji_n<-cellStats(n_fiji, sum, na.rm = T) * 0.001
fiji_p<-cellStats(p_fiji, sum , na.rm = T) * 0.001

fiji_n
fiji_p
```


## Connected

```{r}
nutri_connected<-st_read(here("output_data/Sewage_plants/Nutrients_at_STP.shp"))
```

The below values are in kg/year
```{r}

# Total N and P human emissions
connected_n<-sum(nutri_connected$N) * 0.001
connected_p<-sum(nutri_connected$P) * 0.001

connected_n
connected_p

# N and P after WWTP treatment
connected_n_treat<-sum(nutri_connected$N_final) * 0.001
connected_p_treat<-sum(nutri_connected$P_final) * 0.001

connected_n_treat
connected_p_treat

# Percent of N and P emissions released into environment
sum(nutri_connected$N_final)/sum(nutri_connected$N)
sum(nutri_connected$P_final)/sum(nutri_connected$P)


sum(nutri_connected$P_final)/sum(nutri_connected$N_final)
```

Correlation between Fiji Water Authoriy estimates and our estimates

```{r}
nutri_removal<-read.csv(here("raw_data/Sewage_plants/Nutrient_removal_STP.csv")) %>% 
  mutate(ID = ifelse(STP == "ACS", NA,
                     ifelse(STP == "Deuba", 1,
                            ifelse(STP == "Kinoya", 2,
                                   ifelse(STP == "Naboro", NA,
                                          ifelse(STP == "Nadali", 3,
                                                 ifelse(STP ==  "Namara", 4,
                                                        ifelse(STP == "Lautoka", 5,
                                                               ifelse(STP ==  "Navakai", 6,
                                                                      ifelse(STP == "Olosara", 7,
                                                                             ifelse(STP == "Ba", 8,
                                                                                    ifelse(STP == "Wailada", NA, NA))))))))))),
         nutri_left = (1-rm_eff)) %>% 
  filter(!STP == "ACS",
         !STP == "Naboro") 

N_removal<-nutri_removal %>% 
  filter(type == "N",
        !is.na(ID) == T) %>% 
  rename(N_left = nutri_left) %>% 
  dplyr::select(STP, ID, Raw, Final)%>% 
  rename(N_raw = Raw,
         N_eff_actual = Final)

P_removal<-nutri_removal %>% 
  filter(type == "P",
         !is.na(ID) == T) %>% 
  rename(P_left = nutri_left) %>% 
  dplyr::select(STP, ID, Raw, Final) %>% 
  rename(P_raw = Raw,
         P_eff_actual = Final)
  
```

```{r}
wwtp_compare<-full_join(nutri_connected, N_removal, by = c("ID", "STP")) %>% 
  full_join(., P_removal)
```

```{r}
cor.test(wwtp_compare$N_final, wwtp_compare$N_eff_actual, method = "pearson")
cor.test(wwtp_compare$P_final, wwtp_compare$P_eff_actual, method = "pearson")
```

## Septic

```{r}
N_cell_septic<-raster(here("output_data/Nutrients/Septic_N.tif"))

P_cell_septic<-raster(here("output_data/Nutrients/Septic_P.tif"))

```

This is the amount of N/P through septic systems assuming 10% nutrient removal in tonnes/year

```{r}
septic_n<-cellStats(N_cell_septic, sum, na.rm = T) * 0.001
septic_p<-cellStats(P_cell_septic, sum , na.rm = T) * 0.001

```

This is the amount that makes it into surface waters considering a 50 m lateral travel distance

```{r}
nutri_septic<-read.csv(here("output_data/Nutrients/buffers/N_P_septic_per_basin_50_buff.csv"))

septic_n_surface<-sum(nutri_septic$N,na.rm = T) * 0.1 * 0.001
septic_p_surface<-sum(nutri_septic$P,na.rm = T) * 0.1 * 0.001

septic_n_surface
septic_p_surface

(sum(nutri_septic$N,na.rm = T) * 0.1 * 0.001)/(cellStats(N_cell_septic, sum, na.rm = T) * 0.001)
(sum(nutri_septic$P,na.rm = T) * 0.1 * 0.001)/(cellStats(P_cell_septic, sum , na.rm = T) * 0.001)

```

## Direct

```{r}
N_cell_direct<-raster(here("output_data/Nutrients/Direct_N.tif"))

P_cell_direct<-raster(here("output_data/Nutrients/Direct_P.tif"))
```


```{r}
cellStats(N_cell_direct, sum, na.rm = T) * 0.001
cellStats(P_cell_direct, sum , na.rm = T) * 0.001
```

```{r}
nutri_direct<-read.csv(here("output_data/Nutrients/buffers/N_P_direct_per_basin_50_buff.csv"))

direct_n_surface<-sum(nutri_direct$N,na.rm = T) * 0.1 * 0.001
direct_p_surface<-sum(nutri_direct$P,na.rm = T) * 0.1 * 0.001

direct_n_surface
direct_p_surface

(sum(nutri_direct$N,na.rm = T) * 0.1 * 0.001)/(cellStats(N_cell_direct, sum, na.rm = T) * 0.001)
(sum(nutri_direct$P,na.rm = T) * 0.1 * 0.001)/(cellStats(P_cell_direct, sum , na.rm = T) * 0.001)
```

# Domestic nutrients

Total domestic nutrients at pourpoints

```{r}
total_n_surface<-connected_n_treat+septic_n_surface+direct_n_surface

total_p_surface<-connected_p_treat+septic_p_surface+direct_p_surface

total_n_surface
total_p_surface
```

```{r}
connected_n_treat/total_n_surface
connected_p_treat/total_p_surface
```

## Tourism

```{r}
tik_hotels<-st_read(here("output_data/Tourism/Final_hotel_room_map.shp"))
#tik_hotels<-st_read(here("output_data/Tourism/All_hotels_by_tikina.csv"))

#total number of hotels 
nrow(tik_hotels)

tik_hotels_treatment<-read.csv(here("output_data/Tourism/Hotels_treatment_type.csv"))

nrow(tik_hotels_treatment)
nrow(tik_hotels_treatment)/nrow(tik_hotels)

length(which(tik_hotels_treatment$treatment_level == "Primary"))
length(which(tik_hotels_treatment$treatment_level == "Secondary"))
length(which(tik_hotels_treatment$treatment_level == "Septic"))

```

```{r}
# Relationship between # visitors and # hotels in a Tikina

prop_occupancy_tik<-read.csv(here("tables/Hotels_rooms_visitors_Fiji.csv"))

cor.test(prop_occupancy_tik$Tik_visitors, prop_occupancy_tik$Num_hotels, method = "pearson")
cor.test(prop_occupancy_tik$Prop_visitors, prop_occupancy_tik$Prop_hotels, method = "pearson")

```

```{r}
tik_tourist_nutrients<-read.csv(here("output_data/Tourism/Tourist_nutrients_by_Tikina.csv"))

tourist_n<-sum(tik_tourist_nutrients$Tourist_N, na.rm = T)* 0.001
tourist_p<-sum(tik_tourist_nutrients$Tourist_P, na.rm = T)* 0.001

tourist_n
tourist_p

```
```{r}
# Nutrients after treatment
tourist_treated<-read.csv(here("output_data/Tourism/Treated_tourist_nutrients.csv"))

tourist_n_treat<-sum(tourist_treated$Treated_N, na.rm = T)/1000
tourist_p_treat<-sum(tourist_treated$Treated_P, na.rm = T)/1000
```

```{r}
# Total nutrient removal rate (Raw-Final)/Raw
(tourist_n - tourist_n_treat)/tourist_n # N removal
(tourist_p- tourist_p_treat)/tourist_p # P removal

```

```{r}
# Percentage of total nutrients that Tourism makes up
tourist_n_treat/(total_n_surface + tourist_n_treat)

tourist_p_treat/(total_p_surface + tourist_p_treat)
```

```{r}
area_tourist_nutrients<-tourist_treated %>% 
  group_by(Area) %>% 
  summarise(tourist_N = sum(Tourist_N, na.rm = T),
            tourist_P = sum(Tourist_P, na.rm = T),
            treat_N = sum(Treated_N, na.rm = T),
            treat_P = sum(Treated_P, na.rm = T)) %>% 
  mutate(All_nutrients = treat_N + treat_P)


area_tourist_nutrients
```


```{r}
38202.468/sum(area_tourist_nutrients$treat_N, na.rm = T)
```

# Leach/buffer sensitivity

```{r}
sens<-read.csv(here("output_data/Sensitivity/Leaching_buffer_sensitivity.csv"))

septic_max<-sens %>% 
  filter(type == "septic",
         leach_rate == 1,
         buffer == 500)

direct_max<-sens %>% 
  filter(type == "direct",
         leach_rate == 1,
         buffer == 500)

septic_max
direct_max
```
 
# Total N and P from wasterwater into surface water in Fiji

```{r}
# Total excreted N and P
cellStats(N_cell_septic, sum, na.rm = T) * 0.001 + cellStats(N_cell_direct, sum , na.rm = T) * 0.001 + sum(nutri_connected$N_final, na.rm = T) * 0.001

cellStats(P_cell_septic, sum, na.rm = T) * 0.001 + cellStats(P_cell_direct, sum , na.rm = T) * 0.001 + sum(nutri_connected$P_final, na.rm = T) * 0.001

# Total N and P reaching surface waters
(sum(nutri_direct$N,na.rm = T) * 0.1 * 0.001) + (sum(nutri_septic$N,na.rm = T) * 0.1 * 0.001) + (sum(nutri_connected$N_final) * 0.001)

(sum(nutri_direct$P,na.rm = T) * 0.1 * 0.001) + (sum(nutri_septic$P,na.rm = T) * 0.1 * 0.001) + (sum(nutri_connected$P_final) * 0.001)

#Proportion of connected N and P from total
(sum(nutri_connected$N_final) * 0.001)/((sum(nutri_direct$N,na.rm = T) * 0.1 * 0.001) + (sum(nutri_septic$N,na.rm = T) * 0.1 * 0.001) + (sum(nutri_connected$N_final) * 0.001))

(sum(nutri_connected$P_final) * 0.001)/((sum(nutri_direct$P,na.rm = T) * 0.1 * 0.001) + (sum(nutri_septic$P,na.rm = T) * 0.1 * 0.001) + (sum(nutri_connected$P_final) * 0.001))
```

```{r}
N_cell<-raster(here("output_data/Nutrients/Fiji_N_per_cell.tif"))
P_cell<-raster(here("output_data/Nutrients/Fiji_P_per_cell.tif"))

cellStats(N_cell, sum, na.rm = T) * 0.001
cellStats(P_cell, sum, na.rm = T) * 0.001
```


```{r}
((sum(nutri_direct$N,na.rm = T) * 0.1 * 0.001) + (sum(nutri_septic$N,na.rm = T) * 0.1 * 0.001) + (sum(nutri_connected$N_final) * 0.001))/cellStats(N_cell, sum, na.rm = T) * 0.001

((sum(nutri_direct$P,na.rm = T) * 0.1 * 0.001) + (sum(nutri_septic$P,na.rm = T) * 0.1 * 0.001) + (sum(nutri_connected$P_final) * 0.001))/cellStats(P_cell, sum, na.rm = T) * 0.001
```

# Nutrients at pourpoints

## Connected
```{r}
connected<-st_read(here("output_data/Sewage_plants/Nutrients_at_STP.shp")) %>% 
  as.data.frame() %>% 
  dplyr::select(-geometry)

cor.test(connected$stp_pop, connected$N_final, method = "pearson")
```

```{r}
septic_pp<-read.csv(here("output_data/Nutrients/Fiji_septic_nutrients_at_pourpoints.csv"))

direct_pp<-read.csv(here("output_data/Nutrients/Fiji_direct_nutrients_at_pourpoints.csv"))
```



# Nutrients at corals


# Bar plot of nutrient source