---
title: "Untitled"
author: "Caitie"
date: "29/09/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(raster)
library(here)

t_crs<-"+proj=aea +lat_1=-9 +lat_2=-26 +lat_0=-17 +lon_0=180 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs"
```

# Population stats

```{r}
pop_ras_proj<-raster(here("projected_data/Population/population_fji_albers.tif"))
fiji_pop_df<-cellStats(pop_ras_proj, "sum")


stp_ras<-raster(here("output_data/Sewage_plants/stp_raster_residential.tif"))

stp<-st_read(here("raw_data/Sewage_plants/Fiji Waste Water Catchment.shp")) %>% 
  st_transform(., crs = t_crs) %>% 
  mutate(STP = ifelse(TREATMENT_ == "NATABUA WWTP", "Natabua WWTP",
                      ifelse(TREATMENT_ == "Navakai PS", "Navakai WWTP", as.character(TREATMENT_)))) %>% 
  mutate(area = st_area(.)) %>% 
  group_by(STP) %>% 
  summarise(area = sum(area, na.rm = T)) %>% 
  filter(!is.na(STP) == T,
         !STP %in% c("ACS WWTP", "Naboro WWTP", "Wailada WWTP"))
  
stp<-stp %>% 
  mutate(stp_pop = extract(pop_ras_proj, ., fun = sum, na.rm = T),
         ID = 1:nrow(stp))
```

```{r}
conn_pop<-sum(stp$stp_pop)

prop_pop<-conn_pop/fiji_pop_df
```


```{r}
pop_check<-read_csv(here("output_data/Sewage_plants/STP_population_check.csv")) %>% 
  filter(!is.na(estimated) == T) %>% 
  mutate(perc_diff = (estimated - reported)/estimated)
```

```{r}
cor.test(pop_check$reported, pop_check$estimated, method = "pearson")
```

```{r}
septic<-raster(here("output_data/Population/Septic_population.tif"))
```

```{r}
septic_pop<-cellStats(septic, stat = "sum", na.rm = T)

septic_pop/fiji_pop_df
```

```{r}
direct<-raster(here("output_data/Population/Direct_population.tif"))
```

```{r}
direct_pop<-cellStats(direct, stat = "sum", na.rm = T)

direct_pop/fiji_pop_df
```

```{r}
(conn_pop + septic_pop + direct_pop)/fiji_pop_df
```
# Nutrients by treatment types

## Connected

```{r}
nutri_connected<-st_read(here("output_data/Sewage_plants/Nutrients_at_STP.shp"))
```

The below values are in kg/year
```{r}

# Total N and P human emissions
sum(nutri_connected$N)
sum(nutri_connected$P)

# N and P after WWTP treatment
sum(nutri_connected$N_final) * 0.001
sum(nutri_connected$P_final) * 0.001

# Percent of N and P emissions released into environment
sum(nutri_connected$N_final)/sum(nutri_connected$N)
sum(nutri_connected$P_final)/sum(nutri_connected$P)


sum(nutri_connected$P_final)/sum(nutri_connected$N_final)
```


## Septic

```{r}
N_cell_septic<-raster(here("output_data/Nutrients/Septic_N.tif"))

P_cell_septic<-raster(here("output_data/Nutrients/Septic_P.tif"))

```

This is the amount of N/P through septic systems assuming 10% nutrient removal in tonnes/year

```{r}
cellStats(N_cell_septic, sum, na.rm = T) * 0.001
cellStats(P_cell_septic, sum , na.rm = T) * 0.001
```

This is the amount that makes it into surface waters considering a 50 m lateral travel distance

```{r}
nutri_septic<-read.csv(here("output_data/Nutrients/buffers/N_P_septic_per_basin_50_buff.csv"))

sum(nutri_septic$N,na.rm = T) * 0.1 * 0.001
sum(nutri_septic$P,na.rm = T) * 0.1 * 0.001

(sum(nutri_septic$N,na.rm = T) * 0.1 * 0.001)/(cellStats(N_cell_septic, sum, na.rm = T) * 0.001)
(sum(nutri_septic$P,na.rm = T) * 0.1 * 0.001)/(cellStats(P_cell_septic, sum , na.rm = T) * 0.001)

```

## Direct

```{r}
N_cell_direct<-raster(here("output_data/Nutrients/Direct_N.tif"))

P_cell_direct<-raster(here("output_data/Nutrients/Direct_P.tif"))
```


```{r}
cellStats(N_cell_direct, sum, na.rm = T) * 0.001
cellStats(P_cell_direct, sum , na.rm = T) * 0.001
```

```{r}
nutri_direct<-read.csv(here("output_data/Nutrients/buffers/N_P_direct_per_basin_50_buff.csv"))

sum(nutri_direct$N,na.rm = T) * 0.1 * 0.001
sum(nutri_direct$P,na.rm = T) * 0.1 * 0.001

(sum(nutri_direct$N,na.rm = T) * 0.1 * 0.001)/(cellStats(N_cell_direct, sum, na.rm = T) * 0.001)
(sum(nutri_direct$P,na.rm = T) * 0.1 * 0.001)/(cellStats(P_cell_direct, sum , na.rm = T) * 0.001)
```

# Leach/buffer sensitivity

```{r}
sens<-read.csv(here("output_data/Sensitivity/Leaching_buffer_sensitivity.csv"))

septic_max<-sens %>% 
  filter(type == "septic",
         leach_rate == 1,
         buffer == 500)

direct_max<-sens %>% 
  filter(type == "direct",
         leach_rate == 1,
         buffer == 500)

septic_max
direct_max
```
 
# Total N and P from wasterwater into surface water in Fiji

```{r}
(sum(nutri_direct$N,na.rm = T) * 0.1 * 0.001) + (sum(nutri_septic$N,na.rm = T) * 0.1 * 0.001) + (sum(nutri_connected$N_final) * 0.001)

(sum(nutri_direct$P,na.rm = T) * 0.1 * 0.001) + (sum(nutri_septic$P,na.rm = T) * 0.1 * 0.001) + (sum(nutri_connected$P_final) * 0.001)


(sum(nutri_connected$N_final) * 0.001)/((sum(nutri_direct$N,na.rm = T) * 0.1 * 0.001) + (sum(nutri_septic$N,na.rm = T) * 0.1 * 0.001) + (sum(nutri_connected$N_final) * 0.001))

(sum(nutri_connected$P_final) * 0.001)/((sum(nutri_direct$P,na.rm = T) * 0.1 * 0.001) + (sum(nutri_septic$P,na.rm = T) * 0.1 * 0.001) + (sum(nutri_connected$P_final) * 0.001))
```

```{r}
N_cell<-raster(here("output_data/Nutrients/Fiji_N_per_cell.tif"))
P_cell<-raster(here("output_data/Nutrients/Fiji_P_per_cell.tif"))

cellStats(N_cell, sum, na.rm = T) * 0.001
cellStats(P_cell, sum, na.rm = T) * 0.001
```


```{r}
((sum(nutri_direct$N,na.rm = T) * 0.1 * 0.001) + (sum(nutri_septic$N,na.rm = T) * 0.1 * 0.001) + (sum(nutri_connected$N_final) * 0.001))/cellStats(N_cell, sum, na.rm = T) * 0.001

((sum(nutri_direct$P,na.rm = T) * 0.1 * 0.001) + (sum(nutri_septic$P,na.rm = T) * 0.1 * 0.001) + (sum(nutri_connected$P_final) * 0.001))/cellStats(P_cell, sum, na.rm = T) * 0.001
```

# Nutrients at pourpoints

```{r}
connected<-st_read(here("output_data/Sewage_plants/Nutrients_at_STP.shp")) %>% 
  as.data.frame() %>% 
  dplyr::select(-geometry)
unconnected<-read.csv(here("output_data/Nutrients/N_P_unconnected_per_basin.csv"))
tourist<-read.csv(here("output_data/Sewage_plants/Connected_tourist_nutrients.csv"))
```

```{r}
conn_N<-sum(connected$N, na.rm = T)
unconn_N<-sum(unconnected$N, na.rm = T)
conn_P<-sum(connected$P, na.rm = T)
unconn_P<-sum(unconnected$P, na.rm = T)
tourist_N<-sum(tourist$Total_N, na.rm = T)
tourist_P<-sum(tourist$Total_P, na.rm = T)

df<-data.frame(type = c("Connected", "Unconnected", "Connected", "Unconnected", "Connected_tourism", "Connected_tourism"),
               nutrient = c("N", "N", "P", "P", "N", "P"),
               value = c(conn_N, unconn_N, conn_P, unconn_P, tourist_N, tourist_P))



sum(df$value) * 0.001
```

```{r}
prop<-df %>% 
  group_by(type) %>% 
  summarise(all = sum(value, na.rm = T))

prop<-prop %>% 
  mutate(prop = all/sum(prop$all))
```


# Nutrients at corals

```{r}
coral_export<-st_read(here("output_data/Nutrients/Fiji_corals_nutrient_export.shp")) 

coral_export<- coral_export %>% 
  as.data.frame() %>% 
  dplyr::select(-geometry) %>% 
  pivot_longer(., cols =c("conn_N" ,"conn_P" , "uncnn_N" , "uncnn_P" , "torst_N" , "torst_P" , "Total_N" , "Total_P" , "Ttl_ntr"), names_to = "type", values_to = "value") %>% 
  group_by(type) %>% 
  summarise(totals = sum(value, na.rm = T)) %>% 
  mutate(totals_tonnes<-totals * 0.001)

coral_export
```
# Bar plot of nutrient source