---
title: "Fiji_STP_watersheds"
author: "Caitie"
date: "09/09/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)
library(sf)
#library(startR)
library(here)
library(raster)
library(gdalUtils)
library(tabularaster)
library(units)
library(rgdal)
library(lwgeom)
```

# Fiji

Source - 

```{r}
fiji_tik<-st_read(here("raw_data/Tikina/fji_polbnda_adm3_tikina.shp")) %>% 
  rename(TIKINA = ADM3_NAME,
         PROVINCE = ADM2_NAME,
         TID = FBOS_TID,
         PID = FBOS_PID) %>% 
  summarise()

fiji_proj<-st_transform(fiji_tik, "+proj=tmerc +lat_0=-17 +lon_0=178.75 +k=0.9998548 +x_0=2000000 +y_0=4000000 +ellps=WGS72
+towgs84=35.1728,-136.5713,36.9643,-1.371019,0.841969,4.718006,1.5370023600525 +units=m +no_defs ")

fiji_proj<-st_zm(fiji_proj)

st_write(fiji_proj, here("projected_data/Tikina/fji_proj.shp"), overwrite = T)
```

# Population density

Source: 
https://data.humdata.org/dataset/fiji-high-resolution-population-density-maps-demographic-estimates

30 m (people/30m2) spatial resolution: https://blogs.worldbank.org/opendata/first-look-facebook-s-high-resolution-population-maps

This takes quite a long time - once created load in projected raster only

```{r}
#pop_ras<-raster(here("raw_data/Population/population_fji_2018-10-01.tif"))

#pop_ras_proj<-projectRaster(pop_ras, crs = "+proj=tmerc +lat_0=-17 +lon_0=178.75 +k=0.9998548 +x_0=2000000 +y_0=4000000 +ellps=WGS72+towgs84=35.1728,-136.5713,36.9643,-1.371019,0.841969,4.718006,1.5370023600525 +units=m +no_defs")

#writeRaster(pop_ras_proj, here("projected_data/Population/population_fji_proj.tif"), overwrite = T)
```

```{r}
pop_ras_proj<-raster(here("projected_data/Population/population_fji_proj.tif"))
```


# STP Watershed boundaries

Source - Water Authority Fiji

```{r}
stp<-st_read(here("raw_data/Sewage_plants/Fiji Waste Water Catchment.shp")) %>% 
  mutate(STP = ifelse(TREATMENT_ == "NATABUA WWTP", "Natabua WWTP",
                      ifelse(TREATMENT_ == "Navakai PS", "Navakai WWTP", as.character(TREATMENT_)))) %>% 
  mutate(area = st_area(.)) %>% 
  group_by(STP) %>% 
  summarise(area = sum(area, na.rm = T)) %>% 
  filter(!is.na(STP) == T) 
  
stp<-stp %>% 
  mutate(stp_pop = extract(pop_ras_proj, ., fun = sum, na.rm = T),
         ID = 1:nrow(stp))
```
# Summarise population within each STP watershed

```{r}
fiji_pop_df<-extract(pop_ras_proj, fiji_proj, fun = sum, na.rm = T)

# Population is 1175078
```
# Prop of population connected

```{r}
conn_pop<-sum(stp$stp_pop)

prop_pop<-conn_pop/fiji_pop_df

conn_pop
fiji_pop_df
prop_pop

#~16% of population is connected based on these estimates with Felipe's population density layer
#~19.3% of population is connected based on the Facebook population density layer
```


# Crop STP from population data

```{r}
stp_pop<-crop(pop_ras_proj, stp, snap = "near")
```

# Rasterize STP shapefile

This takes a long time - avoid if possible

```{r}
#stp_ras<-rasterize(stp, pop_ras_proj, field = "ID")
#writeRaster(stp_ras, here("output_data/Sewage_plants/stp_raster.tif"), overwrite = T)
```

# Compare our results to reported results

Source - Table 1 from Fiji national liquid waste management strategy and action plan 2007

```{r}
reported_conn<-read.csv(here("raw_data/Sewage_plants/STP_pop_connected.csv")) %>% 
  mutate(ID = ifelse(STP_name == "Adi_Cakobau School", 1,
                     ifelse(STP_name == "Pacific_Harbour", 2,
                            ifelse(STP_name == "Suva_Kinoya", 3,
                                   ifelse(STP_name == "Naboro Prison", 4,
                                          ifelse(STP_name == "Nausori", 5,
                                                 ifelse(STP_name ==  "Labasa", 6,
                                                        ifelse(STP_name == "Lautoka", 7,
                                                               ifelse(STP_name ==  "Nadi", 8,
                                                                      ifelse(STP_name == "Sigatoka", 9,
                                                                             ifelse(STP_name == "Ba", 10,
                                                                                    ifelse(STP_name == "Wailada", 11, NA))))))))))))
```

Join to estimates

```{r}
pop_check<- stp %>% 
  as.data.frame() %>% 
  dplyr::select(-geometry) %>% 
  full_join(., reported_conn, by = "ID") %>% 
  dplyr::select(STP, STP_name, stp_pop, Pop_connected) %>% 
  rename(estimated = stp_pop,
         reported = Pop_connected)

write.csv(here("output_data/Sewage_plants/STP_population_check.csv"))
```

