---
title: "Supplementary_figures"
author: "Caitie"
date: "23/06/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(raster)
library(here)
library(ggplot2)
library(devtools)
library(patchwork)
library(viridis)
library(ggrepel)

t_crs<-"+proj=aea +lat_1=-9 +lat_2=-26 +lat_0=-17 +lon_0=180 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs"
```

# Population estimates vs. reported plot

```{r}
pop_check<-read_csv(here("output_data/Sewage_plants/STP_population_check.csv")) %>% 
  filter(!is.na(estimated) == T) %>% 
  mutate(label = ifelse(STP == "Deuba WWTP", "Pacific Harbor",
                        ifelse(STP == "Kinoya WWTP", "Kinoya",
                               ifelse(STP == "Nadali WWTP", "Rewa",
                                      ifelse(STP == "Namara TP", "Labasa",
                                             ifelse(STP == "Natabua WWTP", "Natabua",
                                                    ifelse(STP == "Navakai WWTP", "Nadi",
                                                           ifelse(STP == "Olosara", "Sigatoka",
                                                                  ifelse(STP == "Votua WWTP", "Ba", NA)))))))))
```

```{r}
ggplot(pop_check, aes(x = reported/1000, y = estimated/1000, col = label)) +
  geom_point(size = 2) +
  ylab("Estimated population (thousands)") +
  xlab("Reported population (thousands)") +
  stat_smooth(method = "lm", col = "black", linetype = "dashed") +
  theme_bw() +
  labs(colour="Wastewater\ntreatment plant")
```
```{r}
ggsave(here("figures/Supp_reported_estimated_WWTP_population.png"), dpi =300, width = 8, height = 5,)
```

# Estimated WWTP nutrients vs reported

```{r}
wwtp_compare<-read.csv(here("output_data/Sensitivity/WWTP_compare_nutrients.csv"))
```

```{r}
actual<-wwtp_compare %>% 
  dplyr::select(STP.x,N_eff_actual, P_eff_actual) %>% 
  pivot_longer(., cols = c("N_eff_actual", "P_eff_actual"), names_to = "type", values_to = "Actual") %>% 
  mutate(type2 = ifelse(type == "N_eff_actual", "N", "P")) %>% 
  dplyr::select(-type) %>% 
  rename(type = type2)

estimated<-wwtp_compare %>% 
  dplyr::select(STP.x, N_final, P_final) %>% 
  pivot_longer(., cols = c("N_final", "P_final"), names_to = "type", values_to = "Estimated") %>% 
  mutate(type2 = ifelse(type == "N_final", "N", "P"),
         Estimated = Estimated*0.001) %>% 
  dplyr::select(-type) %>% 
  rename(type = type2) 


wwtp_compare2<-full_join(actual, estimated)
```



```{r}
ggplot(wwtp_compare2, aes(x = Estimated, y = Actual, col = STP.x)) +
  geom_point(size = 2) +
  facet_wrap(~type, scales = "free") +
  ylab("Estimated effluent (tonnes)") +
  xlab("Reported effluent (tonnes)") +
  stat_smooth(method = "lm", col = "black", linetype = "dashed") +
  theme_bw() +
  labs(colour="Wastewater\ntreatment plant")
```
```{r}
ggsave(here("figures/Supp_reported_estimated_WWTP_effluent.png"), dpi =300, width = 8, height = 5,)
```


# Treatment/leaching rate/distance from rivers sensitivity plot

```{r}
n_septic_sens<-read.csv(here("output_data/Sensitivity/Septic_treatment_leach_buffer_analysis.csv"))

n_direct_sens<-read.csv(here("output_data/Sensitivity/Direct_treatment_leach_buffer_analysis.csv"))
  
```

Make heat map of different treatment and leaching rates considering a 50 m buffer

Treatment rate of 0.1 means that 10% of nutrients is removed through treatment

Leach rate of 0.1 means that 10% of nutrients leaches (90% lost), a value of 90% would be 10% of nutrients is lost through leaching

leach2 of 0.1 means that 90% of nutrients leaches (10% lost)

```{r}
septic_treat_leach<-n_septic_sens %>% 
  filter(buffer == 50) %>% 
   mutate(leach2 = 1-leach_rate,
     z = ifelse(treatment_rate == 0.2 & leach2 == 0.1, TRUE, FALSE))
```

```{r}
n_septic_heatmap <- ggplot(data = septic_treat_leach, mapping = aes(x = as.factor(treatment_rate),
                                                       y = leach2)) +
  geom_tile(aes(fill = N_leach*0.001)) +
  geom_text(aes(label = round(N_leach*0.001, 2), color=as.factor(z))) +
  scale_color_manual(guide = "none", values = c(`TRUE` = "red", `FALSE` = "black")) +
  xlab(label = "") + 
  ylab(label = "Leaching\n(% nutrient loss)") + 
  theme_bw() + 
  labs(fill="Nitrogen", title = "Septic") + 
  scale_fill_viridis(discrete=FALSE, direction=-1) +
  theme(plot.title = element_text(hjust = 0.5))
  

n_septic_heatmap
```


```{r}
p_septic_heatmap <- ggplot(data = septic_treat_leach, mapping = aes(x = as.factor(treatment_rate),
                                                       y = leach2)) +
  geom_tile(aes(fill = P_leach*0.001)) +
  geom_text(aes(label = round(P_leach*0.001, 2), color=as.factor(z))) +
  scale_color_manual(guide = "none", values = c(`TRUE` = "red", `FALSE` = "black")) +
  xlab(label = "Treatment\n(%nutrient loss)") + 
  ylab(label = "Leaching\n(% nutrient loss)") + 
  theme_bw() + 
  labs(fill="Phosphorus", title = "Septic") + 
  scale_fill_viridis(discrete=FALSE, direction=-1) +
  theme(plot.title = element_text(hjust = 0.5))
  

p_septic_heatmap
```

```{r}
direct_treat_leach<-n_direct_sens %>% 
  filter(buffer == 50) %>% 
   mutate(leach2 = 1-leach_rate,
     z = ifelse(treatment_rate == 0 & leach2 == 0.1, TRUE, FALSE))
```

```{r}
n_direct_heatmap <- ggplot(data = direct_treat_leach, mapping = aes(x = as.factor(treatment_rate),y = leach2)) +
  geom_tile(aes(fill = N_leach*0.001)) +
  geom_text(aes(label = round(N_leach*0.001, 2), color=as.factor(z))) +
  scale_color_manual(guide = "none", values = c(`TRUE` = "red", `FALSE` = "black")) +
  xlab(label = "") + 
  ylab(label = "Leaching\n(% nutrient loss)") + 
  theme_bw() + 
  labs(fill="Nitrogen", title = "Direct") + 
  scale_fill_viridis(discrete=FALSE, direction=-1) +
  theme(plot.title = element_text(hjust = 0.5))
  

n_direct_heatmap
```


```{r}
p_direct_heatmap <- ggplot(data = direct_treat_leach, mapping = aes(x = as.factor(treatment_rate),y = leach2)) +
  geom_tile(aes(fill = P_leach*0.001)) +
  geom_text(aes(label = round(P_leach*0.001, 2), color=as.factor(z))) +
  scale_color_manual(guide = "none", values = c(`TRUE` = "red", `FALSE` = "black")) +
  xlab(label = "Treatment\n(%nutrient loss)") + 
  ylab(label = "Leaching\n(% nutrient loss)") + 
  theme_bw() + 
  labs(fill="Phosphorus", title = "Direct") + 
  scale_fill_viridis(discrete=FALSE, direction=-1) +
  theme(plot.title = element_text(hjust = 0.5))
  

p_direct_heatmap
```

```{r}
(n_septic_heatmap + n_direct_heatmap)/(p_septic_heatmap + p_direct_heatmap) + plot_annotation(tag_levels = 'A')
```

```{r}
ggsave(here("figures/Supp_treat_leach_sensitivity_heatmap.png"), dpi =300, width = 14, height = 8,)
```

# Change in N/P with increasing distance

```{r}
septic_buffer_dat<-n_septic_sens %>% 
  filter(treatment_rate == 0.2) %>% 
  dplyr::select(buffer, leach_rate, N_leach, P_leach) %>% 
  mutate(leach2 = 1-leach_rate) %>% 
  distinct(.) %>% 
  pivot_longer(., col = c("N_leach", "P_leach"), names_to = "Nutrients") %>% 
  mutate(value = value * 0.001,
         type = "Septic") %>% 
  filter(leach_rate == 0.1) %>% 
  mutate(Nutrients = ifelse(Nutrients == "N_leach", "N", "P"))

direct_buffer_dat<-n_direct_sens %>% 
  filter(treatment_rate == 0) %>% 
  dplyr::select(buffer, leach_rate, N_leach, P_leach) %>% 
  mutate(leach2 = 1-leach_rate) %>% 
  distinct(.) %>% 
  pivot_longer(., col = c("N_leach", "P_leach"), names_to = "Nutrients") %>% 
  mutate(value = value * 0.001,
         type = "Direct") %>% 
  filter(leach_rate == 0.1) %>% 
  mutate(Nutrients = ifelse(Nutrients == "N_leach", "N", "P"))

buffer_dat<-rbind(septic_buffer_dat, direct_buffer_dat)
```


```{r}
buffer_sens<-ggplot(buffer_dat, aes(x = buffer, y = value, col = Nutrients)) +
  geom_point() +
  facet_wrap(~type) +
  theme_bw() +
  xlab("Buffer distance (meters)") +
  ylab("Nutrients (tonnes)")

buffer_sens
```


# Change in N/P with increasing leaching rate

```{r}
septic_leach_dat<-n_septic_sens %>% 
  filter(treatment_rate == 0.2) %>% 
  dplyr::select(buffer, leach_rate, N_leach, P_leach) %>% 
  mutate(leach2 = 1-leach_rate) %>% 
  distinct(.) %>% 
  pivot_longer(., col = c("N_leach", "P_leach"), names_to = "Nutrients") %>% 
  mutate(value = value * 0.001,
         type = "Septic") %>% 
  filter(buffer == 50) %>% 
  mutate(Nutrients = ifelse(Nutrients == "N_leach", "N", "P"))

direct_leach_dat<-n_direct_sens %>% 
  filter(treatment_rate == 0) %>% 
  dplyr::select(buffer, leach_rate, N_leach, P_leach) %>% 
  mutate(leach2 = 1-leach_rate) %>% 
  distinct(.) %>% 
  pivot_longer(., col = c("N_leach", "P_leach"), names_to = "Nutrients") %>% 
  mutate(value = value * 0.001,
         type = "Direct") %>% 
  filter(buffer == 50) %>% 
  mutate(Nutrients = ifelse(Nutrients == "N_leach", "N", "P"))

leach_dat<-rbind(septic_leach_dat, direct_leach_dat)
```



```{r}
leach_sens<-ggplot(leach_dat, aes(x = leach2, y = value, col = Nutrients)) +
  geom_point() +
  facet_wrap(~type) +
  theme_bw() +
  xlab("Leaching rate (%)") +
  ylab("Nutrients (tonnes)") 

leach_sens
```

# Change in N/P with increasing treatment

```{r}
septic_treat_dat<-n_septic_sens %>% 
  filter(leach_rate == 0.9) %>% 
    mutate(leach2 = 1-leach_rate) %>% 
  dplyr::select(buffer, treatment_rate, N_leach, P_leach) %>% 
  distinct(.) %>% 
  pivot_longer(., col = c("N_leach", "P_leach"), names_to = "Nutrients") %>% 
  mutate(value = value * 0.001,
         type = "Septic") %>% 
  filter(buffer == 50) %>% 
  mutate(Nutrients = ifelse(Nutrients == "N_leach", "N", "P"))

direct_treat_dat<-n_direct_sens %>% 
  filter(leach_rate == 0.9) %>% 
  mutate(leach2 = 1-leach_rate) %>% 
  dplyr::select(buffer, treatment_rate, N_leach, P_leach) %>% 
  distinct(.) %>% 
  pivot_longer(., col = c("N_leach", "P_leach"), names_to = "Nutrients") %>% 
  mutate(value = value * 0.001,
         type = "Direct") %>% 
  filter(buffer == 50) %>% 
  mutate(Nutrients = ifelse(Nutrients == "N_leach", "N", "P"))

treat_dat<-rbind(septic_treat_dat, direct_treat_dat)
```



```{r}
treat_sens<-ggplot(treat_dat, aes(x = treatment_rate, y = value, col = Nutrients)) +
  geom_point() +
  facet_wrap(~type) +
  theme_bw() +
  xlab("Treatment rate (%)") +
  ylab("Nutrients (tonnes)") 

treat_sens
```

```{r}
buffer_sens/leach_sens/treat_sens + plot_annotation(tag_levels = 'A')
```

```{r}
ggsave(here("figures/Supp_leach_buffer_treat_sensitivity_line_graph.png"), dpi =300, width = 10, height = 15)
```


# Relationship between the proportion of hotels and proporiton of visitors in each Tikina

```{r}
hotel_prop<-read.csv(here("tables/Hotels_rooms_visitors_Fiji.csv"))

cor.test(hotel_prop$Prop_visitors, hotel_prop$Prop_hotels, method = "pearson") # highly positively correlated
```

```{r}
ggplot(hotel_prop, aes(x = Prop_visitors, y = Prop_hotels, label = TIKINA)) +
  geom_point(size = 2) +
  geom_text_repel() +
  ylab("Proportion of hotels") +
  xlab("Proportion of visitors") +
  stat_smooth(method = "lm", col = "black", linetype = "dashed") +
  theme_bw() #+
  #labs(colour="Tikina")
```
```{r}
ggsave(here("figures/Supp_prop_hotels_visitors.png"), dpi =300, width = 8, height = 5,)
```