---
title: "Untitled"
author: "Caitie"
date: "15/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(rgdal)
library(sf)
library(tidyverse)
library(countrycode)
library(here)

t_crs<-"+proj=aea +lat_1=-9 +lat_2=-26 +lat_0=-17 +lon_0=180 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs"

options(scipen = 999)
```



# Calculate Nutrients from tourists

In this code we estimate the contribution of tourists to sewage pollution in Fiji.

# Visitor Arrivals by country 2018

Data is from Fiji's Bureau of Statistics: https://www.statsfiji.gov.fj/index.php/statistics/tourism-and-migration-statistics/visitor-arrivals-statistics

Potentially use a different year?

```{r}
visit_arrivals<-read_csv(here("raw_data/Tourism/Fiji_Visitor_Arrivals_by_Country.csv")) %>% 
  dplyr::select(-X5, -X6, -X7, -X8, -X9, -X10, -X11) %>% 
  filter(!Country == "Total") %>% 
  group_by(Country) %>% 
  summarise(Total_vistors = sum(Visitor_arrivals, na.rm = T)) %>% 
  mutate(Country = ifelse(Country == "Korea", "South Korea", as.character(Country)))

sum(visit_arrivals$Total_vistors)
```

# Visitors from each country by region

Table 8 from https://fhta.com.fj/wp-content/uploads/2019/01/Qtr.-3-2018.pdf
Findings from Qtr 3 2018 hotel survey

```{r}
visitors_region<-read_csv(here("raw_data/Tourism/Fiji_tourists_by_region.csv"))

prop_visitors_region<- visitors_region %>% 
  group_by(Country) %>% 
  summarise(Total_visitors = sum(Num_visitors, na.rm = T)) %>% 
  left_join(., visitors_region, by = "Country") %>% 
  mutate(prop_visitors = Num_visitors/Total_visitors)

#test<-prop_visitors_region %>% 
#  filter(Country == "Australia")
```

# Rooms and beds occupied in each region

Data source: https://fhta.com.fj/wp-content/uploads/2019/01/Qtr.-3-2018.pdf

```{r}
beds_sold<-read_csv(here("raw_data/Tourism/Fiji_room_bed_sold_by_region.csv")) %>% 
  group_by(Area) %>% 
  summarise(Total_beds_sold = sum(Beds_sold, na.rm = T),
            Total_rooms_sold = sum(Rooms_sold, na.rm = T)) %>% 
  mutate(Prop_beds_sold = Total_beds_sold/sum(Total_beds_sold, na.rm = T),
         Prop_rooms_sold= Total_rooms_sold/sum(Total_rooms_sold, na.rm = T))
```

# Protein supply by country

```{r}
protein_supply<-read_csv(here("raw_data/Protein_supply/protein-supply-by-region.csv")) %>% 
  filter(Year == 2013) %>% 
  rename(Protein_g_capita_day = `Food Balance Sheets: Grand Total - Protein supply quantity (g/capita/day) (FAO (2017)) (g/capita/day)`)
```

```{r}
plant_protein_supply<-read_csv(here("raw_data/Protein_supply/FAOSTAT_vegetable_protein_consumption.csv")) %>% 
  filter(Year == 2013,
         Item == "Vegetal Products") %>% 
  dplyr::select(Country, Year, Item, Value) %>% #unit is g/capita/day
  mutate(Code = countrycode(Country, "country.name", "iso3c")) %>%
  rename(plant_protein = Value)
```

```{r}
protein_supply<-full_join(protein_supply, plant_protein_supply, by = c("Code", "Year"))
```

# Join Visitors and protein supply

Visitor data has groups of countries-for this we take the mean protein for the group of countries

```{r}
# Countries by continent

continent<-read_csv(here("raw_data/Tourism/Countries_by_continent.csv"))

# Taiwan included in rest of Asia

# Countries in "Rest_of_Asia" = 
# Countries in "Continental Europe" = 
# Countries in "Pacific Islands" =
# Countries in "Others" = 

#> unique(visit_arrivals$Country)
# [1] "Australia"       "Canada"          "China"           "Europe"          "Hong Kong"       "India"           "Japan"           "South Korea"    
# [9] "New Zealand"     "Others"          "Pacific_Islands" "Rest_of_Asia"    "United Kingdom"  "United States"  

rest_of_asia<-continent %>% 
  filter(Continent == "Asia",
         !ISO3 %in% c("CHN", "HKG", "IND", "JPN", "KOR"))

cont_europe<-continent %>% 
  filter(Continent == "Europe",
         !ISO3 %in% c("ALA", "ISL", "IRL", "GGY", "IMN", "MLT", "GBR", "FRO", "SJM", "HRV", "GIB", "JEY"),
         !is.na(ISO3) == T)
  
pi<-continent %>% 
  filter(Continent == "Oceania",
         !ISO3 %in% c("NZL", "AUS", "FJI"),
         !Region1 == "Australia and New Zealand")

  
# For now we do not include Others with accounts for 4974 or 0.5% of visitors
```


```{r}
rest_of_asia_protein<-left_join(rest_of_asia, protein_supply, by = c("ISO3" = "Code")) %>% 
  summarise(Protein_g_capita_day = mean(Protein_g_capita_day, na.rm = T),
            Plant_protein = mean(plant_protein, na.rm = T))

cont_europe_protein<-left_join(cont_europe, protein_supply, by = c("ISO3" = "Code")) %>% 
  summarise(Protein_g_capita_day = mean(Protein_g_capita_day, na.rm = T),
            Plant_protein = mean(plant_protein, na.rm = T))

pi_protein<-left_join(pi, protein_supply, by = c("ISO3" = "Code")) %>% 
  summarise(Protein_g_capita_day = mean(Protein_g_capita_day, na.rm = T),
            Plant_protein = mean(plant_protein, na.rm = T))


```


# Calculate Nutrients from visitors

```{r}
avg_stay = 11.4 #days - reference is from https://pic.or.jp/ja/wp-content/uploads/2019/07/2018-Annual-Visitor-Arrivals-ReportF.pdf


visitor_nutrients<-visit_arrivals %>% 
  filter(!Country == "Others") %>% 
  left_join(., protein_supply, by = c("Country" = "Entity")) %>% 
  mutate(Protein_g_capita_day = as.numeric(Protein_g_capita_day),
         Protein_g_capita_day = ifelse(Country == "Rest_of_Asia", as.numeric(round(rest_of_asia_protein$Protein_g_capita_day,2)),
                                       ifelse(Country == "Europe", as.numeric(round(cont_europe_protein$Protein_g_capita_day,2)),
                                              ifelse(Country == "Pacific_Islands", as.numeric(round(pi_protein$Protein_g_capita_day,2)),
                                                     ifelse(Country == "Hong Kong", 129.18, as.numeric(Protein_g_capita_day))))),
         Plant_protein = as.numeric(plant_protein),
         Plant_protein= ifelse(Country == "Rest_of_Asia", as.numeric(round(rest_of_asia_protein$Plant_protein,2)),
                                       ifelse(Country == "Europe", as.numeric(round(cont_europe_protein$Plant_protein,2)),
                                              ifelse(Country == "Pacific_Islands", as.numeric(round(pi_protein$Plant_protein,2)),
                                                     ifelse(Country == "Hong Kong", 34.77, as.numeric(Plant_protein))))),
         Protein_N_intake = Protein_g_capita_day * 0.13,
         #Protein_P_intake = Protein_g_capita_day *(1/6),
         #N_excretion_human = Protein_N_intake * (0.8+0.17),
         P_excretion_human = 0.011 * (Protein_g_capita_day + Plant_protein), 
         N_emissions_human = Protein_N_intake * avg_stay/1000, #kg/person/year
         P_emissions_human = P_excretion_human* avg_stay/1000,#kg/person/year
         N_emissions_visitors = N_emissions_human * Total_vistors, #kg/country tourists total/year
         P_emissions_visitors = P_emissions_human * Total_vistors) 

```


# Join to visitor by region data

```{r}
visitor_nutrients_region<-visitor_nutrients %>% 
  mutate(Country2 = ifelse(Country == "Europe", "Cont. Europe",
                           ifelse(Country == "United States", "USA",
                           ifelse(Country %in% c("Hong Kong", "India", "Japan", "South Korea", "Rest_of_Asia", "Pacific_Islands", "United Kingdom", "China"), "Others", as.character(Country))))) %>% 
  left_join(., prop_visitors_region, by = c("Country2" = "Country")) %>% 
  mutate(N_visitors_region = N_emissions_visitors * prop_visitors,
         P_visitors_region = P_emissions_visitors * prop_visitors) 

test<-visitor_nutrients_region %>% 
  filter(Country == "Australia")

test<-visitor_nutrients_region %>% 
  filter(Area == "Coral Coast")


visitor_nutrients_region2<-visitor_nutrients_region %>% 
  group_by(Area) %>% 
  summarise(Total_N = sum(N_visitors_region,na.rm = T),
            Total_P = sum(P_visitors_region, na.rm = T))
```

# Spatialize region data

Coral Coast - check
Lautoka - Vuda
Mamanuca - Malolo
Nadi - Tikina == "Nadi"
Northern Division - ADM1_NAME == "Northern Division"
Others
Suva - Tikina == "Suva"

```{r}
fiji_tik<-st_read(here("projected_data/Tikina/Fiji_tikina.shp")) %>% 
  st_transform(., crs = t_crs) %>% 
  mutate(area = as.numeric(st_area(.))) %>% 
  group_by(TIKINA, ADM1_NAME) %>%
  summarise(area = sum(area, na.rm = T)) %>% 
  mutate(Area = case_when(TIKINA == "Suva" ~ "Suva",
                          TIKINA == "Nadi" ~ "Nadi",
                          ADM1_NAME == "Northern  Division" ~ "Northern Division",
                          TIKINA == "Baravi" ~ "Coral Coast",
                          TIKINA == "Nasigatoka" ~ "Coral Coast",
                          TIKINA == "Cuvu" ~ "Coral Coast",
                          TIKINA == "Malomalo" ~ "Coral Coast",
                          TIKINA == "Vuda" ~ "Lautoka",
                          TIKINA == "Malolo" ~ "Mamanuca"),
         Area = ifelse(is.na(Area) == T, "Others", as.character(Area)))
```


```{r}
fiji_tik_nutrients<-full_join(fiji_tik, visitor_nutrients_region2, by ="Area")
```


# Join hotel location with hotel room numbers

This layer was produced by manually looking up hotel names in google earth

```{r}
hotel_loc<-readOGR("/home/kuempel/Fiji_sewage/raw_data/Tourism/Fiji_Hotels_Rooms.kml")

hotel_loc<-hotel_loc %>% 
  st_as_sf() %>% 
  st_transform(., crs = t_crs) %>% 
  mutate(ID = as.numeric(description),
         ID = ifelse(Name == "Mana Lagoon", 88,
                     ifelse(Name == "Beachcomber Island Resort, Tai Is; Vuda", 70, as.numeric(ID)))) %>% 
  dplyr::select(Name, ID, geometry)
```



I have a list of licensed hotels in Fiji in 2020. It was sent to me via e-mail from Mereoni W. Kalokalaodrau. For now I use the 2016 data as most of our data is from 2018.
```{r}
#hotel_2020<-read_csv("/home/kuempel/Fiji_sewage/raw_data/Tourism/Hotel_list_2020.csv") %>% 
#  dplyr::select(-"#")
```

This is a list of licensed hotels in Fiji in 2016. I think this more accurately matches the other data but discuss with group. The data was given to me via e-mail from Helen Sykes

```{r}
hotel_rooms<-read.csv("/home/kuempel/Fiji_sewage/raw_data/Tourism/Hotel_num_rooms_Fiji.csv") 

hotel_rooms$Num_persons <- as.numeric(gsub(",","",hotel_rooms$Num_persons))

hotel_rooms<-hotel_rooms %>% 
  mutate(Bures = replace_na(Bures, 0),
         Rooms = replace_na(Rooms, 0),
         Dorms = replace_na(Dorms, 0),
         Cabins = replace_na(Cabins, 0),
         Villas = replace_na(Villas, 0),
         Lodges = replace_na(Lodges, 0),
         Ensuite = replace_na(Ensuite, 0),
         Bungalows = replace_na(Bungalows, 0),
         Tents = replace_na(Tents, 0),
         Suites = replace_na(Suites, 0),
         Cottages = replace_na(Cottages, 0)) %>% 
  mutate(Total_rooms = Bures + Rooms + Dorms + Cabins + Villas + Lodges + Ensuite + Bungalows + Tents + Suites + Cottages) %>% 
  dplyr::select(Area, Hotel_Name, Total_rooms, Num_persons, ID)
```

There are quite a few more hotels listed in 2020 than in 2016 - discuss with Stacy what she suggests to do?
```{r}
#test<-full_join(hotel_2020, hotel_rooms, by = "Hotel_Name")
```



Explore original hotel layer

```{r}
orig_hotels<-readOGR("/home/kuempel/Fiji_sewage/raw_data/Tourism/Fiji_Hotels.kmz") %>% 
  st_as_sf() %>% 
  st_transform(., crs = t_crs) %>% 
  mutate(ID = NA) %>% 
  dplyr::select(Name, ID, geometry)
```

```{r}
all_hotels<-rbind(hotel_loc, orig_hotels) %>% 
  filter(!duplicated(geometry))
```


```{r}
hotel_rooms_loc<-full_join(all_hotels, hotel_rooms, by = "ID") %>% 
  filter(!is.na(Name) == T)
```

```{r}
cor.test(hotel_rooms_loc$Num_persons, hotel_rooms_loc$Total_rooms, method = "pearson")
```


# Hotels per tikina/basin

```{r}
fiji_basins<-st_read(here("projected_data/Basins/Fiji_Basins12_albers.shp"))

fiji_basins<-fiji_basins %>% 
  dplyr::select(MAIN_BAS) %>% 
  mutate(basin_area_m2 = as.numeric(st_area(.))) %>% 
  group_by(MAIN_BAS) %>% 
  summarise(basin_area_m2 = sum(basin_area_m2, na.rm = T))
```


```{r}
tikina_basin<-st_intersection(fiji_tik, fiji_basins) %>% 
  mutate(area_tik_bas = as.numeric(st_area(.)),
         prop_area = area_tik_bas/basin_area_m2) 

tikina_bas_hotels<-st_intersection(hotel_rooms_loc, tikina_basin)

tikina_bas_hotels_df<-tikina_bas_hotels %>% 
  as.data.frame() %>% 
  dplyr::select(-geometry)

write.csv(tikina_bas_hotels_df, here("output_data/Tourism/All_hotels_by_tikina.csv"))

tikina_bas_hotels_rooms<-tikina_bas_hotels %>% 
  filter(!is.na(Total_rooms) == T)

tikina_bas_hotels_add<-tikina_bas_hotels %>% 
  filter(is.na(Total_rooms == T)) %>% 
  dplyr::select(-area)

```

# Add in hotel rooms

Here I separated out hotels that did not have room numbers then searched google to find room numbers. Now I add that data back in.

I also want to remove any potential duplicate hotels

Remove "The projects collective"

```{r}
room_search<-read.csv(here("raw_data/Tourism/Fiji_additional_rooms.csv")) %>% 
  dplyr::select(-Notes, -X.1, -X) 

tikina_add2<-tikina_bas_hotels_add %>% 
  filter(!Name == "The Projects Collective") %>% 
  full_join(., room_search, by = c("Name", "ID", "Area", "Num_persons", "Area.1", "Hotel_Name", "TIKINA", "ADM1_NAME")) %>% 
  mutate(Total_rooms = ifelse(is.na(Total_rooms.x) == T, Total_rooms.y, Total_rooms.x)) %>% 
  dplyr::select(-Total_rooms.x, -Total_rooms.y) 

```

Join together and remove any potential duplicates

DONE Remove duplicate Tubakula Baech Bungalows
DONE Remove duplicate Dreamview Villas
DONE Remove duplicate Fiji Palms Resort
DONE Remove duplicate Funky Fish Beach
DONE Remove duplicate Gold Coast Inn
DONE Remove duplicate Koro Sun
DONE Remove duplicate Musket Cove
DONE Remove Ocean Studio Fiji
DONE Remove Basilico Italian Restaurant at Radisson Blu Resort, Fiji
DONE Remove Swimming Pool
DONE Remove duplicates of The Terrace Apartments
DONE Remove duplicate Tokoriki



Check 	

LEFT IN BUT NOT 100% SURE: Hibisucus duplicates???
LEFT IN: Novotel Nadi vs Novotel Suva Lami Bay
REMOVED ONE: Rendezvous Beach Resort, Uciwai, Nadi vs.Rendezvous Surf Camp Fiji
REMOVED ONE: Sheraton Denarau Villas, Denarau Island, Nadi vs Sheraton Fiji Resort 
LEFT IN: Victoria Hotel Fiji vs. Victoria Palms Hotel
REMOVED ONE:Yadua Bay Resort vs. Yadua Bay Resort & Villas

REMOVED ONE: Club Fiji Limited, Wailoaloa Beach, Nadi Bay AND Club Fiji Limited = are these the same??

```{r}
tikina_hotels <- rbind(tikina_bas_hotels_rooms, tikina_add2) %>% 
  filter(!Name == "Tubakula Beach Bungalows",
         !Name == "Basilico Italian Restaurant at Radisson Blu Resort, Fiji",
         !Name == "Ocean Studio Fiji",
         !Name == "Dreamview Villas",
         !Name == "Fiji Palms, Resort",
         !Name == "Gold Coast Inn Fiji",
         !Name == "Koro sun resort",
         !Name == "Musket Cove Island Resort & Marina",
       #  !Name == "The Terrace Apartments" & is.na(Total_rooms) == T,
         !Name == "Tokoriki",
         !Name == "Funky Fish Beach Resort",
         !Name == "Rendezvous Surf Camp Fiji",
         !Name == "Sheraton Fiji Resort",
         !Name == "Yadua Bay Resort",
         !Name == "Club Fiji",
         !duplicated(geometry))

# Manually remove duplicate Terrace Apartments

terrace<-tikina_hotels %>% 
  filter(Name == "The Terrace Apartments")

terrace<-terrace[1,]

tikina_hotels<-tikina_hotels %>% 
  filter(!Name == "The Terrace Apartments")

tikina_hotels<-rbind(tikina_hotels, terrace)

st_write(tikina_hotels, here("output_data/Tourism/Final_hotel_room_map.shp"), append = F)

```

# Hotels per area

********Double check********
```{r}
hotels_per_area<-tikina_hotels %>% 
  group_by(Area.1) %>% 
  summarise(Total_hotels = length(unique(Name))) %>% 
  as.data.frame() %>% 
  dplyr::select(-geometry)

hotels_per_basin<-tikina_hotels %>% 
  group_by(MAIN_BAS) %>% 
  summarise(Total_hotels = length(unique(Name))) %>% 
  as.data.frame() %>% 
  dplyr::select(-geometry)

hotels_per_tikina<-tikina_hotels %>% 
  group_by(TIKINA) %>% 
  summarise(Total_hotels = length(unique(Name))) %>% 
  as.data.frame() %>% 
  dplyr::select(-geometry)

hotels_per_tikina_basin<-tikina_hotels %>% 
  group_by(TIKINA, MAIN_BAS) %>% 
  summarise(Total_hotels = length(unique(Name))) %>% 
  as.data.frame() %>% 
  dplyr::select(-geometry)

hotels_per_all<-tikina_hotels %>% 
  group_by(TIKINA, MAIN_BAS, Area.1) %>% 
  summarise(Total_hotels = length(unique(Name))) %>% 
  as.data.frame() %>% 
  dplyr::select(-geometry)

```

```{r}
prop_hotels_tik<-tikina_hotels %>% 
  group_by(TIKINA, Area.1, MAIN_BAS) %>% 
  summarise(Num_hotels = length(unique(Name))) %>% 
  left_join(., hotels_per_area, by = "Area.1") %>% 
  mutate(Prop_hotels = Num_hotels/Total_hotels) %>% 
  as.data.frame() %>% 
  dplyr::select(-geometry) 

test<-prop_hotels_tik %>% 
  filter(Area.1 == "Others")
```

# Rooms per area - don't use this anymore, distribute on hotels
```{r}
#rooms_area<-tikina_hotels %>% 
#  filter(!is.na(Total_rooms)) %>% 
#  group_by(Area.1) %>% 
#  summarise(Total_rooms = sum(Total_rooms, na.rm = T)) %>% 
#  as.data.frame() %>% 
#  dplyr::select(-geometry)

#rooms_basin<-tikina_hotels %>% 
#  filter(!is.na(Total_rooms)) %>% 
#  group_by(MAIN_BAS) %>% 
#  summarise(Total_rooms = sum(Total_rooms, na.rm = T)) %>% 
#  as.data.frame() %>% 
#  dplyr::select(-geometry)

#rooms_tikina<-tikina_hotels %>% 
#  group_by(TIKINA) %>% 
#  summarise(Total_rooms = sum(Total_rooms, na.rm = T)) %>% 
#  as.data.frame() %>% 
#  dplyr::select(-geometry)

#persons_area<-tikina_hotels %>% 
#  filter(!is.na(Num_persons)) %>% 
#  group_by(Area.1) %>% 
#  summarise(Total_persons = sum(Num_persons, na.rm = T)) %>% 
#  as.data.frame() %>% 
#  dplyr::select(-geometry)

#persons_basins<-tikina_hotels %>% 
#  filter(!is.na(Num_persons)) %>% 
#  group_by(MAIN_BAS) %>% 
#  summarise(Total_persons = sum(Num_persons, na.rm = T)) %>% 
#  as.data.frame() %>% 
#  dplyr::select(-geometry)

#persons_tikina<-tikina_hotels %>% 
#  filter(!is.na(Num_persons)) %>% 
#  group_by(TIKINA) %>% 
#  summarise(Total_persons = sum(Num_persons, na.rm = T)) %>% 
#  as.data.frame() %>% 
#  dplyr::select(-geometry)

```

NB: Some hotels do not have room/person information which creates a discrepency in proportions between hotels/rooms/people.

```{r}
#prop_occupancy_tik<- tikina_hotels %>% 
#  group_by(TIKINA, Area.1, MAIN_BAS) %>% 
#  summarise(Tik_rooms = sum(Total_rooms, na.rm = T),
  #          Tik_visitors = sum(Num_persons, na.rm = T)) %>% 
  #left_join(., rooms_area, by = "Area.1") %>% 
  #left_join(., persons_area, by = "Area.1") %>% 
#  mutate(Prop_rooms = Tik_rooms/Total_rooms,
#            Prop_visitors = Tik_visitors/Total_persons) %>% 
#  left_join(., prop_hotels_tik, by = c("TIKINA", "MAIN_BAS", #"Area.1")) %>% 
#  as.data.frame() %>% 
#  dplyr::select(-geometry) 

#write.csv(prop_occupancy_tik, #here("tables/Hotels_rooms_visitors_Fiji.csv"))

```

Test correlations
```{r}
#cor.test(prop_occupancy_tik$Prop_rooms, prop_occupancy_tik$Prop_visitors, method = "pearson") # highly positively correlated
#cor.test(prop_occupancy_tik$Prop_rooms, prop_occupancy_tik$Prop_hotels, method = "pearson") # highly positively correlated
#cor.test(prop_occupancy_tik$Prop_visitors, prop_occupancy_tik$Prop_hotels, method = "pearson") # highly positively correlated
```
# Distribute nutrients based on number of hotels within each Tikina/Watershed/Tourist Area

```{r}
tik_tourist_nutrients<-full_join(fiji_tik_nutrients, prop_hotels_tik, by = c("TIKINA", "Area" = "Area.1")) %>%
  mutate(Tourist_N = Total_N * Prop_hotels,
         Tourist_P = Total_P * Prop_hotels) 


test<-tik_tourist_nutrients %>% 
  filter(Area == "Coral Coast") 

#plot(tik_tourist_nutrients["Tourist_N"])
#plot(tik_tourist_nutrients["Tourist_P"])

tik_tourist_nutrients_df<-tik_tourist_nutrients %>% 
  as.data.frame() %>% 
  dplyr::select(-geometry)

write.csv(tik_tourist_nutrients_df, here("output_data/Tourism/Tourist_nutrients_by_Tikina.csv"))

round(sum(visitor_nutrients_region2$Total_N, na.rm = T),1) == round(sum(tik_tourist_nutrients$Tourist_N, na.rm = T), 1)
round(sum(visitor_nutrients_region2$Total_P, na.rm = T),1) == round(sum(tik_tourist_nutrients$Tourist_P, na.rm = T),1)
```
# Treatment levels

From Fiji National Watewater Report 2007

"Most large hotels (>100 rooms) have sewage treatment plants which provide primary or secondary treatment"

~15 large hotels
~25 medium-sized resorts (30-100 rooms)

Smaller resorts (~65) and backpackers accomodations (1-30 rooms) usually have septic tanks 

To be conservative we assign large hotels secondary treatment, medium-sized resorts primary treatment and smaller resorts septic tank treatment for N and P

Primary treatment = 20% removal for both N and P
Secondary treatment = 40% for N and 45% for P 
Septic system = 20% (same as primary treatment)


```{r}

# If rooms are missing for a Tikina/basin we gap fill them

rooms_na<-tikina_hotels %>% 
  filter(is.na(Total_rooms) == T)

avg_rooms<-tikina_hotels %>% 
  group_by(TIKINA) %>% 
  summarise(avg_rooms = round(mean(Total_rooms, na.rm = T), 0)) %>% 
  dplyr::select(-geometry) %>% 
  as.data.frame()

tikina_hotels2<-tikina_hotels %>% 
  full_join(., avg_rooms, by = "TIKINA") %>% 
  mutate(Total_rooms2 = ifelse(is.na(Total_rooms) == T, avg_rooms, Total_rooms))

test<-tikina_hotels2 %>% 
  filter(is.na(Total_rooms2) == T)

hotel_treatment<-tikina_hotels2 %>%
  filter(!is.na(Total_rooms2) == T) %>% 
  mutate(treatment_level = case_when(Total_rooms2>100 ~ "Secondary",
                                     Total_rooms2<=100 & Total_rooms2>=30 ~ "Primary",
                                     Total_rooms2<30 ~ "Septic"))

test<-hotel_treatment %>% 
  filter(is.na(treatment_level) == T)

hotel_treatment_df<-hotel_treatment %>% 
  as.data.frame() %>% 
  dplyr::select(-geometry.x, -geometry.y)

write.csv(hotel_treatment_df, here("output_data/Tourism/Hotels_treatment_type.csv"))


```


# Determine treatment levels within each Tikina/watershed

```{r}
tikina_bas_treat <- hotel_treatment %>%
  dplyr::select(-geometry.x, -geometry.y) %>% 
  as.data.frame() %>% 
  count(TIKINA, MAIN_BAS, Area.1, treatment_level, sort = TRUE) %>% 
  rename(tik_bas_n = n) %>% 
  filter(!is.na(MAIN_BAS) == T) # There is one hotel that is not within a basin

all_treat <- hotel_treatment %>% 
  dplyr::select(-geometry.x, -geometry.y) %>% 
  as.data.frame() %>% 
  count(Area.1, sort = TRUE) %>% 
  rename(total_n = n)

prop_treatment<-full_join(tikina_bas_treat, all_treat) %>% 
  mutate(prop_treat = tik_bas_n/total_n)


test<-prop_treatment %>% 
  filter(Area.1 == "Coral Coast")

```


```{r}
tourist_treated<-tik_tourist_nutrients %>% 
  rename(Area.1 = Area) %>% 
  full_join(., prop_treatment, by = c("TIKINA", "MAIN_BAS", "Area.1")) %>% 
  dplyr::select(TIKINA, Area.1, MAIN_BAS, Total_N, Total_P, Tourist_N, Tourist_P, treatment_level, prop_treat) %>% 
  mutate(Type_N = Total_N * prop_treat, 
         Type_P = Total_P * prop_treat)

```

Check to make sure all is working correctly

```{r}
test_nutrients <- tik_tourist_nutrients_df %>% 
  filter(Area == "Coral Coast")

sum(test_nutrients$Tourist_N, na.rm = T)

test_treat<- tourist_treated %>% 
  filter(Area.1 == "Coral Coast")

sum(test_treat$Type_N, na.rm = T)
```


```{r}

tourist_treated_final<-tourist_treated %>% 
  mutate(Treated_N = ifelse(treatment_level == "Primary", Type_N * prop_treat * 0.8,
                          ifelse(treatment_level == "Secondary", Type_N * prop_treat * 0.6,
                              ifelse(treatment_level == "Septic", Type_N * prop_treat * 0.8, NA))),
       Treated_P = ifelse(treatment_level == "Primary", Type_P * prop_treat * 0.8,
                          ifelse(treatment_level == "Secondary", Type_P * prop_treat * 0.55,
                              ifelse(treatment_level == "Septic", Type_P * prop_treat * 0.8, NA)))) %>% 
  dplyr::select(TIKINA, MAIN_BAS, Area.1, treatment_level, prop_treat, Tourist_N, Tourist_P, Type_N, Type_P, Treated_N, Treated_P) 

test<-tourist_treated_final %>% 
  filter(Area.1 == "Coral Coast") 

tourist_treated_df<-tourist_treated_final %>% 
  as.data.frame() %>% 
  dplyr::select(-geometry)

write.csv(tourist_treated_df, here("output_data/Tourism/Treated_tourist_nutrients.csv"))
```


CHECK AND MAKE SURE IT'S OK THAT THESE ARE EXCLUDED
```{r}
test_final<-tourist_treated_final %>% 
  filter(is.na(Treated_N) == T)
```




