---
title: "Untitled"
author: "Caitie"
date: "17/09/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)
library(sf)
library(here)
library(raster)
library(ggplot2)
library(rgdal)
library(gdistance)
library(reshape2)
library(rgrass7)
library(parallel)
library(tmap)
#remotes::install_github("SEEG-Oxford/seegSDM")
library(seegSDM)
library(tabularaster)
library(units)
library(lwgeom)
library(here)

t_crs<-"+proj=aea +lat_1=-9 +lat_2=-26 +lat_0=-17 +lon_0=180 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs"
```


# Basins

```{r}
# Read in data and calculate area
fiji_basins12<-st_read(here("projected_data/Basins/Fiji_basins12.shp")) %>% 
  dplyr::select(HYBAS_ID, MAIN_BAS) %>% 
  st_transform(.,t_crs)
```

# Rivers

```{r}
rivers<-st_read(here("raw_data/Rivers/RiverATLAS_v10_shp/RiverATLAS_v10_australia.shp"))

rivers_proj<-st_transform(rivers, t_crs)

e<-extent(fiji_basins12)

crop_rivers<-st_crop(rivers_proj, e) %>% 
  dplyr::select(HYRIV_ID, MAIN_RIV, NEXT_DOWN, dis_m3_pyr)

data_per_river<-st_join(crop_rivers,fiji_basins12)

na_rivers<-data_per_river %>% 
  filter(is.na(MAIN_BAS) == T)

sub_rivers<-data_per_river %>% 
  filter(MAIN_RIV %in% na_rivers$MAIN_RIV,
         NEXT_DOWN == MAIN_RIV) %>% 
  as.data.frame() %>% 
  dplyr::select(-geometry) %>% 
  distinct(MAIN_RIV, MAIN_BAS) %>% 
  filter(!is.na(MAIN_BAS) == T) %>% 
  rename(MIS_BAS = MAIN_BAS,
         MIS_RIV = MAIN_RIV)

basin_rivers<-data_per_river %>% 
  full_join(., sub_rivers, c("MAIN_RIV" = "MIS_RIV")) %>% 
  mutate(MAIN_BAS = ifelse(is.na(MAIN_BAS) == T, as.numeric(MIS_BAS), as.numeric(MAIN_BAS))) %>% 
  dplyr::select(HYRIV_ID, MAIN_RIV, NEXT_DOWN, dis_m3_pyr, HYBAS_ID, MAIN_BAS)
```


# Pourpoints
Method from here: https://stackoverflow.com/questions/55106950/r-sf-intersect-lines-with-the-borders-of-multipolygons-extract-coordinates-of

Here is the new method I should use: https://gis.stackexchange.com/questions/251101/return-end-vertices-of-an-sf-linestring

```{r}
# Read in data
#sub_fiji_rivers<- rivers_proj %>% 
#  filter(NEXT_DOWN == 0) %>% 
#  st_cast(., "LINESTRING") %>% 
#  filter(!duplicated(HYRIV_ID))


#If you only want the endpoints, then st_line_sample is what you are looking for:

pnts<-st_endpoint(basin_rivers) 

pnts_xy<-st_coordinates(pnts) 

data_per_river2<-cbind(basin_rivers, pnts_xy) %>% 
  rename(pp_x = X,
         pp_y = Y) %>% 
  dplyr::select(HYRIV_ID, NEXT_DOWN, MAIN_RIV, HYBAS_ID, MAIN_BAS,dis_m3_pyr, pp_x, pp_y) %>% 
  rename(riv_dis = dis_m3_pyr)
```



# Nutrients per basin

Now we assume only nutrients within 50 meters of rivers gets into surface waters

Read in data
```{r}
septic_basins_nutri<-read.csv(here("output_data/Nutrients/buffers/N_P_septic_per_basin_50_buff.csv")) %>% 
  dplyr::select(-X)
  
direct_basins_nutri<-read.csv(here("output_data/Nutrients/buffers/N_P_direct_per_basin_50_buff.csv")) %>% 
  dplyr::select(-X)
```

# Distribute

We distributed the sediment export across all points weighted by the mean annual discharge of each river

```{r}
septic_basins_nutri_all<-left_join(data_per_river2, septic_basins_nutri, by = c("MAIN_BAS")) %>% 
  as.data.frame() %>% 
  dplyr::select(-geometry, MAIN_BAS, riv_dis, pp_x, pp_y)

direct_basins_nutri_all<-left_join(data_per_river2, direct_basins_nutri, by = c("MAIN_BAS")) %>% 
  as.data.frame() %>% 
  dplyr::select(-geometry, MAIN_BAS, riv_dis, pp_x, pp_y)

septic_basins_nutri_dist<-septic_basins_nutri_all %>% 
  group_by(MAIN_BAS) %>% 
  summarise(Total_discharge = sum(riv_dis)) %>% 
  left_join(., septic_basins_nutri_all, by = "MAIN_BAS") %>% 
  mutate(prop_dis = riv_dis/Total_discharge,
         N_pourpoint = prop_dis * N,
         P_pourpoint = prop_dis * P,
         N_pourpoint_leach = N_pourpoint * 0.1,
         P_pourpoint_leach = P_pourpoint * 0.1) # Leaching rate is from Jacks et al. 1999 (1-50% of nitrates leached to groundwater)

direct_basins_nutri_dist<-direct_basins_nutri_all %>% 
  group_by(MAIN_BAS) %>% 
  summarise(Total_discharge = sum(riv_dis)) %>% 
  left_join(., direct_basins_nutri_all, by = "MAIN_BAS") %>% 
  mutate(prop_dis = riv_dis/Total_discharge,
         N_pourpoint = prop_dis * N,
         P_pourpoint = prop_dis * P,
         N_pourpoint_leach = N_pourpoint * 0.1,
         P_pourpoint_leach = P_pourpoint * 0.1) # Leaching rate is from Jacks et al. 1999 Try to find values specifically for phosphorous?

```

# Data check

```{r}
sum(septic_basins_nutri$N, na.rm = T) == sum(septic_basins_nutri_dist$N_pourpoint, na.rm = T)
sum(direct_basins_nutri$N, na.rm = T) == sum(direct_basins_nutri_dist$N_pourpoint, na.rm = T)
```

# Write files
```{r}
write_csv(septic_basins_nutri_dist, here("output_data/Nutrients/Fiji_septic_nutrients_at_pourpoints.csv"))

write_csv(direct_basins_nutri_dist, here("output_data/Nutrients/Fiji_direct_nutrients_at_pourpoints.csv"))
```

# Nutrient export at each pourpoint (spatial)

```{r}
pour_points<-septic_basins_nutri_dist
coordinates(pour_points) <- ~pp_x+pp_y
pour_points<-st_as_sf(pour_points)
pour_points<-pour_points %>% 
  dplyr::select(HYRIV_ID, MAIN_BAS, N_pourpoint, P_pourpoint, N_pourpoint_leach, P_pourpoint_leach) %>% 
  rename(N = N_pourpoint,
         P = P_pourpoint,
         N_leach = N_pourpoint_leach,
         P_leach = P_pourpoint_leach) %>% 
  filter(!is.na(N) == T)

st_crs(pour_points)<-t_crs

st_write(pour_points, here("output_data/Nutrients_at_pourpoints/Fiji_septic_pourpoints.shp"), delete_layer = T)
```


```{r}
pour_points_direct<-direct_basins_nutri_dist
coordinates(pour_points_direct) <- ~pp_x+pp_y
pour_points_direct<-st_as_sf(pour_points_direct)
pour_points_direct<-pour_points_direct %>% 
  dplyr::select(HYRIV_ID, MAIN_BAS, N_pourpoint, P_pourpoint, N_pourpoint_leach, P_pourpoint_leach) %>% 
  rename(N = N_pourpoint,
         P = P_pourpoint,
         N_leach = N_pourpoint_leach,
         P_leach = P_pourpoint_leach) %>% 
  filter(!is.na(N) == T)

st_crs(pour_points_direct)<-t_crs

st_write(pour_points_direct, here("output_data/Nutrients_at_pourpoints/Fiji_direct_pourpoints.shp"), delete_layer = T)
```