---
title: "Untitled"
author: "Caitie"
date: "17/09/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(sf)
#library(startR)
library(here)
library(raster)
library(gdalUtils)
library(tabularaster)
library(units)
library(rgdal)
library(lwgeom)
```

# STP watersheds


```{r}
stp<-st_read(here("raw_data/Sewage_plants/Fiji Waste Water Catchment.shp")) %>% 
  mutate(STP = ifelse(TREATMENT_ == "NATABUA WWTP", "Natabua WWTP",
                      ifelse(TREATMENT_ == "Navakai PS", "Navakai WWTP", as.character(TREATMENT_)))) %>% 
  mutate(area = st_area(.)) %>% 
  group_by(STP) %>% 
  summarise(area = sum(area, na.rm = T)) %>% 
  filter(!is.na(STP) == T) 

```


# River data

```{r}
rivers<-st_read(here("raw_data/Rivers/Fiji_RiverATLAS.shp"))

rivers_proj<-st_transform(rivers, st_crs(stp)) %>% st_zm()

st_write(rivers_proj, here("projected_data/Rivers/Fiji_rivers.shp"), append = F)
```


# Buffer river

For now I do 500 m each side - determine a more defensible value?

Could also buffer coastline?

Could also do something like Steph Borelle's paper on plastics:

https://science.sciencemag.org/content/suppl/2020/09/16/369.6510.1515.DC1

```{r}
buffer_rivers<-st_buffer(rivers_proj, dist = 500) %>% 
  mutate(ID = 1)
```

# Remove STP area

```{r}
diff_buffer<-st_difference(buffer_rivers, st_union(stp))

st_write(diff_buffer, here("output_data/Rivers/River_buffer_stprm.shp"), append = F)
```


# N and P pollution

```{r}
N_cell<-raster(here("output_data/Nutrients/Fiji_N_per_cell.tif"))
P_cell<-raster(here("output_data/Nutrients/Fiji_P_per_cell.tif"))
```

# Septic population
```{r}
septic<-raster(here("output_data/Population/Septic_population.tif"))

septic[septic>0]<-1
```


# Direct population

```{r}
direct<-raster(here("output_data/Population/Direct_population.tif"))

direct[direct>0]<-1
```


```{r}
septic_N<-N_cell * septic
septic_P<-P_cell * septic

septic_N<-septic_N * 0.9 # Assume 10% removal efficiency from Wang et al. primary treatment
septic_P<-septic_N * 0.9 # Assume 10% removal efficiency from Wang et al. primary treatment

direct_N<-N_cell * direct
direct_P<-P_cell * direct
```

# Rasterize buffer

This takes awhile - avoid if possible
```{r}
#buffer_ras<-rasterize(diff_buffer, N_cell, field = "ID")

#writeRaster(buffer_ras, here("output_data/Nutrients/buffer_rivers.tif"),overwrite = T)

buffer_ras<-raster(here("output_data/Rivers/buffer_rivers.tif"))
```


# Change Buffer area to N and P pollution values

```{r}
direct_N_buff<-direct_N * buffer_ras
direct_P_buff<-direct_P * buffer_ras

septic_N_buff<- septic_N * buffer_ras
septic_P_buff<- septic_P * buffer_ras
```


```{r}
cellStats(direct_N, stat = sum, na.rm = T) #1695542 kg/year
cellStats(direct_N_buff, stat = sum, na.rm = T) #738091.8 kg/year

cellStats(septic_N, stat = sum, na.rm = T) #1525970 kg/year
cellStats(septic_N_buff, stat = sum, na.rm = T) #649384.4 kg/year
```

# Nutrients within watersheds

Wateshed boundaries

Level 12 basins

Look to see if any of the basins are endorrheic - they are not (column ENDO)
```{r}
# Read in data and calculate area
fiji_basins12<-st_read(here("projected_data/Basins/Fiji_basins12.shp")) %>% 
  group_by(MAIN_BAS) %>% 
  summarise(area_km2 = sum(area_km2, na.rm = T))

fiji_basins12<-fiji_basins12 %>% 
  mutate(ID = seq(from = 1, to =nrow(fiji_basins12), 1))

#fiji_basins_df<-fiji_basins12 %>% 
#  as.data.frame() %>% 
#  dplyr::select(HYBAS_ID, NEXT_DOWN,area_km2, ID, dis_m3_pyr)

```


Sum cells within watersheds

```{r}
septic_basin_N<-raster::extract(septic_N_buff, fiji_basins12, fun=sum, na.rm=TRUE, df=TRUE)
septic_basin_P<-raster::extract(septic_P_buff, fiji_basins12, fun=sum, na.rm=TRUE, df=TRUE)

direct_basin_N<-raster::extract(direct_N_buff, fiji_basins12, fun=sum, na.rm=TRUE, df=TRUE)
direct_basin_P<-raster::extract(direct_P_buff, fiji_basins12, fun=sum, na.rm=TRUE, df=TRUE)
```

```{r}
septic_basins_nutri_df<-full_join(septic_basin_N, fiji_basins12, by = "ID") %>% 
  full_join(., septic_basin_P, by = "ID") %>% 
  rename(N = layer.x,
         P = layer.y) %>% 
  dplyr::select(ID, N, P, MAIN_BAS)

direct_basins_nutri_df<-full_join(direct_basin_N, fiji_basins12, by = "ID") %>% 
  full_join(., direct_basin_P, by = "ID") %>% 
  rename(N = layer.x,
         P = layer.y) %>% 
  dplyr::select(ID, N, P, MAIN_BAS)

```

```{r}
write.csv(septic_basins_nutri_df, here("output_data/Nutrients/N_P_septic_per_basin.csv"))
write.csv(direct_basins_nutri_df, here("output_data/Nutrients/N_P_direct_per_basin.csv"))
```

